---
title: "Results_prelim"
author: "Marion Boisseaux"
date: "04/05/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# (PART) Part three : Results {-}

The data

```{r echo=FALSE, message=FALSE, warning=FALSE}
Metradica <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica")
```

# Hypotheses : 

Part I (Habitat preference - type) : *specialists* species should have a more adequate set of trait to a given habitat than the generalists in the same habitat. Generalists would express a wider range of traits.

PArt II (Precipitation gradient) : 



# Data exploration 

How to visualize the data and show the links between the variables and identify the same responses of the individuals? 


## General PCA 

### Contribution of individuals and variables : 1-2 dimensions

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(FactoMineR)
library(Factoshiny)


#resultPCA <- Factoshiny(Metradica[,c(8:13,20)])

#dim 1-2

#Contribution
res.PCA<-PCA(Metradica[,c(8:13,20)],graph=FALSE)

a1<- plot.PCA(res.PCA,choix='var',habillage = 'contrib',title="Graphe des variables de l'ACP")

a2<-plot.PCA(res.PCA,invisible=c('quali'),habillage='contrib',title="Graphe des individus de l'ACP",cex=2,cex.main=2,cex.axis=2,col.quali='#9AE019',label =c('ind.sup'))

a1
a2
```

### Contribution of individuals and variables : 1-2 dimensions

```{r echo=FALSE, message=FALSE, warning=FALSE}
#dim 3-4
res.PCA<-PCA(Metradica[,c(8:13,20)],graph=FALSE)

b1<-plot.PCA(res.PCA,axes=c(3,4),choix='var',title="Graphe des variables de l'ACP")

b2<-plot.PCA(res.PCA,axes=c(3,4),invisible=c('ind.sup'),title="Graphe des individus de l'ACP",cex=2,cex.main=2,cex.axis=2,col.quali='#9AE019', label = c('quali'))

b1
b2

```

### Habitat collected


```{r echo=FALSE, message=FALSE, warning=FALSE}

#Habitat collected

res.PCA<-PCA(Metradica[, c(6, 8:13, 20)],quali.sup=c(1),graph=FALSE)

c1<- plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="",cex=2.25,cex.main=2.25,cex.axis=2.25,col.quali='#FFC400',label =c('quali'))

c2<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=1.9,cex.main=1.9,cex.axis=1.9,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(c2,c1), ncol = 2)


```


### Habitat preference -type

```{r echo=FALSE, message=FALSE, warning=FALSE}

res.PCA<-PCA(Metradica[,c(7, 8:13, 20)],quali.sup=c(1),graph=FALSE)

d2<- plot.PCA(res.PCA,invisible=c('ind.sup'),title="Graphe des individus de l'ACP",cex=1.8,cex.main=1.8,cex.axis=1.8,col.quali='#FF6600',label =c('quali'))


d1<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title ="" ,cex=1.9,cex.main=1.7,cex.axis=1.7,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(d2,d1), ncol = 2)

```

### Forest sites 
```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[,c(5, 8:13, 20)],quali.sup=c(1),graph=FALSE)

e2<-plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=2.1,cex.main=2.1,cex.axis=2.1,col.quali='#3622E6',label =c('quali'))

e1<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=1.9,cex.main=1.9,cex.axis=1.9,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(e2,e1), ncol = 2)

```


### Dawkins of tree

```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[c(8:13, 24)],quali.sup=c(7),graph=FALSE)

plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",col.quali='#FFC400',label =c('quali'))
```

### Species

```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[c(4,8:13)],quali.sup=c(1),graph=FALSE)

g2<- plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=0.9,cex.main=1.6,cex.axis=1.6,col.quali='#2BF0D2',label =c('quali'))


g2
```


## Distribution of major traits 

A focus on the frequency distribution of traits of individuals within communities allows scaling up from organism to ecosystem level and assessing how ecological communities and ecosystems respond to climate drivers (Garnier et al 2016; Liu et al 2020).

The shape of trait distribution could have the potential to reveal the ecological significance of trends and tradeoffs in traits at the species level. A focus on the *mean * and the *variance* of the community trait distribution is rooted in the 
concept of phenotype-environment matching and environmental optimality, where species’ relative abundance is mediated by their traits, that is, “community assembly by trait selection”. To understand how community trait composition is affected by ecological processes. 



* use of community-weighted trait metrics CWM
* variance
* mean
* skewness (symmetry)
* kurtosis (measure of tailness with heavy tail referring to outliers)


*after log tranform*

### leaf minimal conductance


```{r}
library(ggplot2)

ggplot(Metradica) +
 aes(x = log10(Gmin)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

### Turgor loss point
```{r}

ggplot(Metradica) +
 aes(x = Ptlp) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

The πtlp values in our data set were on average less negative than those previously reported in the literature (for moist tropical forests (Fig. 1) (Maréchaux 2015). There are several possible explanations for such a pattern, one of them being that as they conducted their measurements at the peak of the dry season, we also measured πtlp at the peak of the dry season, but 2020-2021 dry seasons were "wetter" than usual. Plants often acclimate πtlp during drought periods, through the accumulation of cell solutes, or osmotic adjustment. Such an adjustment results in a lowering of πtlp and can contribute to drought tolerance in vegetation world-wide (Wright et al. 1992; Abrams & Kubiske 1994; Cao 2000; Merchant et al. 2007; Zhu & Cao 2009; Bartlett, Scoffoni & Sack 2012b; Bartlett et al. 2014).


### Leaf area

```{r}
ggplot(Metradica) +
 aes(x = log10(LA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()

```

### Specifig leaf area
```{r}

ggplot(Metradica) +
 aes(x = log10(SLA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

### leaf saturated water content
```{r}
ggplot(Metradica) +
 aes(x = log10(LSWC)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```


### Major vein density
```{r}
ggplot(Metradica) +
 aes(x = log10(MajVLA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()

```

## Summary of main variables
```{r}
 plot(Metradica[,8:13])
```


