---
title: "Results_prelim"
author: "Marion Boisseaux"
date: "04/05/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---

# (PART) Part three : Results {-}

The data

```{r echo=FALSE, message=FALSE, warning=FALSE}
Metradica <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica")
```

# Hypotheses : 

Part I (Habitat preference - type) : *specialists* species should have a more adequate set of trait to a given habitat than the generalists in the same habitat. Generalists would express a wider range of traits.

PArt II (Precipitation gradient) : 



# Data exploration 

How to visualize the data and show the links between the variables and identify the same responses of the individuals? 


## General PCA 

### Contribution of individuals and variables : 1-2 dimensions

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(FactoMineR)
library(Factoshiny)


#resultPCA <- Factoshiny(Metradica[,c(8:13,20,21)])

#dim 1-2

#Contribution
res.PCA<-PCA(Metradica[,c(8:13,20)],graph=FALSE)

a1<- plot.PCA(res.PCA,choix='var',habillage = 'contrib',title="Graphe des variables de l'ACP")

a2<-plot.PCA(res.PCA,invisible=c('quali'),habillage='contrib',title="Graphe des individus de l'ACP",cex=2,cex.main=2,cex.axis=2,col.quali='#9AE019',label =c('ind.sup'))

a1
a2
```

### Contribution of individuals and variables : 1-2 dimensions

```{r echo=FALSE, message=FALSE, warning=FALSE}
#dim 3-4
res.PCA<-PCA(Metradica[,c(8:13,20)],graph=FALSE)

b1<-plot.PCA(res.PCA,axes=c(3,4),choix='var',title="Graphe des variables de l'ACP")

b2<-plot.PCA(res.PCA,axes=c(3,4),invisible=c('ind.sup'),title="Graphe des individus de l'ACP",cex=2,cex.main=2,cex.axis=2,col.quali='#9AE019', label = c('quali'))

b1
b2

```

### Habitat collected


```{r echo=FALSE, message=FALSE, warning=FALSE}

#Habitat collected

res.PCA<-PCA(Metradica[, c(6, 8:13, 20)],quali.sup=c(1),graph=FALSE)

c1<- plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="",cex=2.25,cex.main=2.25,cex.axis=2.25,col.quali='#FFC400',label =c('quali'))

c2<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=1.9,cex.main=1.9,cex.axis=1.9,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(c2,c1), ncol = 2)


```


### Habitat preference -type

```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[,c(7, 8:13, 20)],quali.sup=c(1),graph=FALSE)

d2<- plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=1.8,cex.main=1.8,cex.axis=1.8,col.quali='#FF6600',label =c('quali'))


d1<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title ="" ,cex=1.9,cex.main=1.7,cex.axis=1.7,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(d2,d1), ncol = 2)

```

### Forest sites 
```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[,c(5, 8:13, 20)],quali.sup=c(1),graph=FALSE)

e2<-plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=2.1,cex.main=2.1,cex.axis=2.1,col.quali='#3622E6',label =c('quali'))

e1<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=1.9,cex.main=1.9,cex.axis=1.9,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(e2,e1), ncol = 2)

```


### Dawkins of tree

```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[c(8:13, 24)],quali.sup=c(7),graph=FALSE)

plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",col.quali='#FFC400',label =c('quali'))
```

### Species

```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[c(4,8:13)],quali.sup=c(1),graph=FALSE)

g2<- plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=0.9,cex.main=1.6,cex.axis=1.6,col.quali='#2BF0D2',label =c('quali'))


g2
```


## Distribution of major traits 

A focus on the frequency distribution of traits of individuals within communities allows scaling up from organism to ecosystem level and assessing how ecological communities and ecosystems respond to climate drivers (Garnier et al 2016; Liu et al 2020).

The shape of trait distribution could have the potential to reveal the ecological significance of trends and tradeoffs in traits at the species level. A focus on the *mean * and the *variance* of the community trait distribution is rooted in the 
concept of phenotype-environment matching and environmental optimality, where species’ relative abundance is mediated by their traits, that is, “community assembly by trait selection”. To understand how community trait composition is affected by ecological processes. 



* use of community-weighted trait metrics CWM
* variance
* mean
* skewness (symmetry)
* kurtosis (measure of tailness with heavy tail referring to outliers)


*after log tranform*

### leaf minimal conductance


```{r}
library(ggplot2)

ggplot(Metradica) +
 aes(x = log10(Gmin)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

### Turgor loss point
```{r}

ggplot(Metradica) +
 aes(x = log10(abs(Ptlp))) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

### Leaf area

```{r}
ggplot(Metradica) +
 aes(x = log10(LA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()

```

### Specifig leaf area
```{r}

ggplot(Metradica) +
 aes(x = log10(SLA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

### leaf saturated water content
```{r}
ggplot(Metradica) +
 aes(x = log10(LSWC)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```


### Major vein density
```{r}
ggplot(Metradica) +
 aes(x = log10(MajVLA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()

```

## Summary of main variables
```{r}
 plot(Metradica[,8:13])
```


## Gmin - exploration

The capacity to retain water will become increasingly important for survival of tropical trees. Along with other plant hydraulic traits, cuticle conductance may strongly affect survival during droughts (Cochard, 2020).

ANOVA reports a p-value far below 0.05, indicating there are differences in the means in the forest sites and habitat collect. Tukey post-hoc test shows groups a Bafog and b for Paracou and Kaw. It also shows groups TF a and BF b.  

Model_gmin <- lm(log10(Gmin) ~ Forest + Habitat,  data = Metradica)

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
Metradica %>% group_by(Forest) %>% summarise_at(vars(Gmin), funs(mean(Gmin, na.rm=TRUE))) 

# Global test
library(ggpubr)
library(ggfortify)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_gmin<-lm(log10(Gmin) ~ Forest + Habitat,  data = Metradica)
#autoplot(Model_gmin)
#summary(Model_gmin)
anova(Model_gmin) # ANOVA reports a p-value far below 0.05, indicating there are differences in the means in the forest sites and habitat and varies across species.
#tukey_gmin <- TukeyHSD(aov(Model_gmin))
library(agricolae)
#tukey2 <- HSD.test(aov(Model_gmin), trt = 'Forest') #show groups a Bafog and b for Paracou and Kaw
#tukey3 <- HSD.test(aov(Model_gmin), trt = 'Habitat') #show groups TF a and BF b 
```


```{r echo=FALSE, message=FALSE, warning=FALSE}
library(ggplot2)
library(plotly)
library(ggplot2)
library(cowplot)

#gmin with all species- interactive graph
plot_ly(Metradica, y = ~Gmin, color = ~Name, type = "box")


#forest
options(digits = 10)
means <- aggregate(Gmin ~Forest, Metradica, mean)


A<-  ggplot(Metradica) +
  aes(x = Forest, y = log10(Gmin), fill = Forest, group = Forest) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(Bafog = "#ED9210", Kaw = "#0C8FCD", Paracou = "#10C65B")) +
  labs(
    x = "",
    y = "Minimal conductance (mmol.m-2.s-1)"
  ) +
  stat_summary(fun.y="mean", colour = "red", geom="point") +
 theme_minimal() +
  stat_compare_means(method = "anova", label = "p.signif")


B <- ggplot(Metradica) +
 aes(x = Forest, y = Gmin, colour = Name) +
 geom_boxplot(shape = "circle", fill = "#112446") +
  labs(
    x = "Forest sites",
    y = ""
  ) +
 scale_color_hue(direction = 1) +
 theme_minimal() +
  theme(legend.position="bottom")


ggarrange(ncol = 1, plotlist = list(A, B), nrow = 2)


```


The adjusted mean arises when statistical averages must be corrected to compensate for data imbalances and large variances. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
#moyenne ajustée pour reequilibre mon design : meme nbr d'espece dans chque site
library(emmeans)
m_ajust_forest_gmin <- emmeans(object = Model_gmin, specs = "Forest")
#pairs(m_ajust_forest_gmin) 
a <- plot(m_ajust_forest_gmin)

m_ajust_habitat_gmin <- emmeans(object = Model_gmin, specs = "Habitat")
#pairs(m_ajust_habitat_gmin) 
b <- plot(m_ajust_habitat_gmin)

library(ggplot2)
library(cowplot)

plot_grid(a,b, labels = c('A', 'B'), label_size = 12)
```

*interpretation* Across all species and all sites, gmin averaged 4.02 mmol.m-2.s-1. Gmin varied significantly among species (F-statistic: 18.10326,  p-value: < 2.2204e-16). Across sites, gmin ranged from 3.08 mmol m–2 s–1 in Paracou to 3.60 mmol m–2 s–1 in Kaw to 5.47 mmol.m-2.m-1 i Bafog and site differences were significant (F-statistic:  50.0139,  p-value: < 2.2204e-16). 

It is unclear whether a higher gmin in the Bafog site is assigned to stomatal opening or a higher permeability of the cuticle. We may need to consider soil water access as an additional factor to understand the pattern.

*literature* Slot et al 2021 found across 24 tropical species an average gmin of 4.0 mmol m–2 s–1. Large differences among species in cuticular water loss have the potential to contribute to differential mortality during drought, phenomena that are increasingly common in the tropics (Rifai et al 2019)

* **Test the phylogenetic signal.**
* **compare with stomatal density** 
* **see if more trichomes for bafog site that could explain why these species can afford to have a higher gmin?**

```{r}

library(ggplot2)

ggplot(Metradica) +
 aes(x = LT, y = MajVLA, fill = Name) +
 geom_point(shape = "circle", size = 1.5, colour = "#112446") +
 scale_fill_hue(direction = 1) +
 theme_minimal()

ggplot(Metradica) +
 aes(x = DBH, y = MajVLA, colour = Name) +
 geom_point(shape = "circle", size = 1.5) +
 scale_color_hue(direction = 1) +
 theme_minimal()



ggplot(Metradica) +
 aes(x = Forest, y = Ptlp, colour = Name) +
 geom_boxplot(shape = "circle", fill = "#112446") +
 scale_color_hue(direction = 1) +
 theme_minimal()

```

