---
title: "Results_prelim2"
author: "Marion Boisseaux"
date: "07/05/2022"
output: html_document
---

## Gmin - exploration

The capacity to retain water will become increasingly important for survival of tropical trees. Along with other plant hydraulic traits, cuticle conductance may strongly affect survival during droughts (Cochard, 2020).

ANOVA reports a p-value far below 0.05, indicating there are differences in the means in the forest sites and habitat collect. Tukey post-hoc test shows groups a Bafog and b for Paracou and Kaw. It also shows groups TF a and BF b.  

Model_gmin <- lm(log10(Gmin) ~ Forest + Habitat,  data = Metradica)

The data

```{r Data import for traits, echo=FALSE, message=FALSE, warning=FALSE}
Metradica <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica")
```

```{r gmin-anova, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
Metradica %>% group_by(Forest) %>% summarise_at(vars(Gmin), funs(mean(Gmin, na.rm=TRUE))) 

# Global test
library(ggpubr)
library(ggfortify)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_gmin<-lm(log10(Gmin) ~ Forest+Habitat,  data = Metradica)
#autoplot(Model_gmin)
summary(Model_gmin)
anova(Model_gmin) # ANOVA reports a p-value far below 0.05, indicating there are differences in the means in the forest sites and habitat and varies across species.
#tukey_gmin <- TukeyHSD(aov(Model_gmin))
library(agricolae)
tukey2 <- HSD.test(aov(Model_gmin), trt = 'Forest') #show groups a Bafog and b for Paracou and Kaw
tukey3 <- HSD.test(aov(Model_gmin), trt = 'Habitat') #show groups TF a and BF b 
```

### Plots 
```{r Gmin pref habitat}

gmin <- Metradica %>%
 filter(!is.na(Type)) %>%
 ggplot() +
  aes(x = Type, y = log10(Gmin), fill = Type) +
  geom_boxplot(shape = "circle") +
  labs(
    x = "",
    y = "Minimal conductance (mmol.m-2.s-1)"
  ) +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#FFD361"
    )
  ) +
  theme_minimal() +
  stat_compare_means(method = "anova", label.y = 2, size = 3)+ theme(axis.title = element_text(size = 10)) +  stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 1.5, size = 7)
                                                                       


```


```{r gmin-plot, message=FALSE, warning=FALSE}
library(ggplot2)
library(plotly)
library(ggplot2)
library(cowplot)

#gmin with all species- interactive graph
plot_ly(Metradica, y = ~Gmin, color = ~Name, type = "box", showlegend = FALSE) %>% layout(yaxis = list(title ='Minimal conductance (mmol.m-2.s-1)'))


#forest
options(digits = 10)
means <- aggregate(Gmin ~Forest, Metradica, mean)


A<-  ggplot(Metradica) +
  aes(x = Forest, y = log10(Gmin), fill = Forest, group = Forest) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(Bafog = "#ED9210", Kaw = "#0C8FCD", Paracou = "#10C65B")) +
  labs(
    x = "",
    y = "Minimal conductance (mmol.m-2.s-1)"
  ) +
  stat_summary(fun.y="mean", colour = "red", geom="point") +
 theme_minimal() +
  stat_compare_means(method = "anova", label = "p.signif")


B <- ggplot(Metradica) +
 aes(x = Forest, y = Gmin, colour = Name) +
 geom_boxplot(shape = "circle", fill = "#112446") +
  labs(
    x = "Forest sites",
    y = ""
  ) +
 scale_color_hue(direction = 1) +
 theme_minimal() +
  theme(legend.position="bottom")


ggarrange(ncol = 1, plotlist = list(A, B), nrow = 2)


```


The adjusted mean arises when statistical averages must be corrected to compensate for data imbalances and large variances. 

```{r gmin-ajustmeans, echo=FALSE, message=FALSE, warning=FALSE}
#moyenne ajustée pour reequilibre mon design : meme nbr d'espece dans chque site
Model_gmin<-lm(log10(Gmin) ~ Forest+Habitat,  data = Metradica)

library(emmeans)
m_ajust_forest_gmin <- emmeans(object = Model_gmin, specs = "Forest")
#pairs(m_ajust_forest_gmin) 
a <- plot(m_ajust_forest_gmin)

m_ajust_habitat_gmin <- emmeans(object = Model_gmin, specs = "Habitat")
#pairs(m_ajust_habitat_gmin) 
b <- plot(m_ajust_habitat_gmin)

library(ggplot2)
library(cowplot)

plot_grid(a,b, labels = c('A', 'B'), label_size = 12)
```

### Gmin and other variables? 

Yes : MajVLA and SLA.
$quanti
          correlation       p.value
MajVLA  0.09328913682 0.01618976310
FvFm    0.06178897606 0.10874004687
LSWC   -0.04404830581 0.25416539130
Ptlp   -0.05363521589 0.17134527454
LA     -0.08838865629 0.02213220611
SLA    -0.09932187546 0.01009827694


```{r gmin-MajVLA and SLA}
M_gmin <- lm(Gmin ~ MajVLA + SLA, data = Metradica)
library(ggplot2)


library(ggpubr)
ggplot(Metradica,aes(x = Gmin, y = MajVLA)) + 
  geom_point() + 
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.y = 30, aes(label = ..eq.label..)) +
  stat_regline_equation(label.y = 25, aes(label = ..rr.label..))


ggplot(Metradica,aes(x = SLA, y = Gmin)) + 
  geom_point() + 
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.y = 30, aes(label = ..eq.label..)) +
  stat_regline_equation(label.y = 25, aes(label = ..rr.label..))


```


*interpretation* Across all species and all sites, gmin averaged 4.02 mmol.m-2.s-1. Gmin varied significantly among species (F-statistic: 18.10326,  p-value: < 2.2204e-16). Across sites, gmin ranged from 3.08 mmol m–2 s–1 in Paracou to 3.60 mmol m–2 s–1 in Kaw to 5.47 mmol.m-2.m-1 i Bafog and site differences were significant (F-statistic:  50.0139,  p-value: < 2.2204e-16). 

It is unclear whether a higher gmin in the Bafog site is assigned to stomatal opening or a higher permeability of the cuticle. We may need to consider soil water access as an additional factor to understand the pattern.

*literature* Slot et al 2021 found across 24 tropical species an average gmin of 4.0 mmol m–2 s–1. Large differences among species in cuticular water loss have the potential to contribute to differential mortality during drought, phenomena that are increasingly common in the tropics (Rifai et al 2019)

* **Test the phylogenetic signal.**
* **compare with stomatal density** 
* **see if more trichomes for bafog site that could explain why these species can afford to have a higher gmin?**


## Ptlp - exploration

Leaf turgor loss point (πtlp) indicates the capacity of a plant to maintain cell turgor pressure during dehydration, which has been proven to be strongly predictive of the plant response to drought. 

```{r Ptlp-plot}
library(ggplot2)
library(plotly)
library(ggplot2)
library(cowplot)

#ptlp with all species- interactive graph
plot_ly(Metradica, y = ~Ptlp, color = ~Name, type = "box")
```

### Paracou data set


Several outliers are either marked as "herbivory", are "young", or have Run = 4 and trace of fungi (659).

```{r Ptlp-Paracou, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)

ParacouPtlp <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1sLs02kNSBbNmDsepvAU38YdwKZPpcZwiAFM_TRw0y04/edit#gid=922870345", range = "ptlp")

plot_ly(ParacouPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Code)
plot_ly(ParacouPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Comment)
plot_ly(ParacouPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Run)
plot_ly(ParacouPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~LeafPhenoStatus)
plot_ly(ParacouPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~LeafHealthStatus)

```

 

### Bafog data set

```{r Ptlp-Bafog, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)

BafogPtlp <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/14E9RjSB4dq8epcDBqMtRi1HOGddbhLOWA8g6TF1bDWM/edit#gid=1237961205", range = "ptlp")

plot_ly(BafogPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Code)
plot_ly(BafogPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Comment)
plot_ly(BafogPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Run)
plot_ly(BafogPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~LeafPhenoStatus)
plot_ly(BafogPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~LeafHealthStatus)

```

Several outliers are either marked as "Erreur bota", "pas de stabilisation", and two leaves are Run 4 and 3.

### Kaw data set

```{r Ptlp-Kaw, message=FALSE, warning=FALSE}
library(plotly)
library(ggplot2)

KawPtlp <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1ywbd6_6DWfqCguahhEvs0qt0d3jAtsbt94xydm-maqI/edit#gid=922870345", range = "ptlp")

plot_ly(KawPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Code)
plot_ly(KawPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Comment)
plot_ly(KawPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~Run)
plot_ly(KawPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~LeafPhenoStatus)
plot_ly(KawPtlp, x=~SpCode, y=~Ptlp, type = "box",text=~LeafHealthStatus)

```

Several outliers are either marked as "Epiphytes", "herbivory", One run is 4. 



* The variability in πtlp among species indicates the potential for a 
range of species responses to drought within Amazonian forest communities. 

* For *Symphonia globulifera* we couldn't exclude first- and second-order veins (that may have resulted in apoplastic dilution that would lead to less negative osmometer values (Kikuta & Richter 1992)). Eventhough it does not appear to be an outlier, we still have too keep in mind that the overall values would be more negative. 

* We found lower TLP values (less negative) for 7 species (above - 1.6 MPa):
  - *Dicorynia guianensis* (as Maréchaux et al 2015)
  - *Eschweleira coriacea *  (as Maréchaux et al 2015)
  - *Hymenopus heteromorphus*
  - *Iryanthera sagotiana*
  - *Iryanthera hostmannii*
  - *Jacaranda copaia subsp. copaia*
  - *Pterocarpus officinalis*

* We found higher TLP values (more negative) for 10 species (below - 1.87 MPa) including *Voucapoua americana* and both *Protium* species like Maréchaux et al 2015. Protium species have been found in more seasonally dry forests across the Amazonia (Ter Steege et al 2006). 

Correlation with other variable : LSWC and SLA 

```{r Ptlp-LSWC and SLA, echo=FALSE, message=FALSE, warning=FALSE}
M_ptlp <- lm(Ptlp ~ LSWC + SLA, data = Metradica)


library(ggpubr)
ggplot(Metradica,aes(x = LSWC, y = Ptlp)) + 
  geom_point() + 
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.y = 0.5, aes(label = ..eq.label..)) +
  stat_regline_equation(label.y = 0.3, aes(label = ..rr.label..))


ggplot(Metradica,aes(x = SLA, y = Ptlp)) + 
  geom_point() + 
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.y = 0.5, aes(label = ..eq.label..)) +
  stat_regline_equation(label.y = 0.3, aes(label = ..rr.label..))
```

####  Anova and plots
```{r Ptlp-anova, message=FALSE, warning=FALSE}
# Global test
library(ggpubr)
library(ggfortify)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_Ptlp<-lm(Ptlp ~ Forest+Habitat,  data = Metradica)
#autoplot(Model_Ptlp)
summary(Model_Ptlp)
anova(Model_Ptlp) # ANOVA reports a p-value far below 0.05, indicating there are differences in the means in the forest sites and habitat and varies across species.
#tukey_Ptlp <- TukeyHSD(aov(Model_Ptlp))
library(agricolae)
#tukey2 <- HSD.test(aov(Model_Ptlp), trt = 'Forest') #show groups a Bafog and b for Paracou and c for Kaw
#tukey3 <- HSD.test(aov(Model_Ptlp), trt = 'Habitat') #show groups TF a and BF b

library(rstatix)
stat.test <- aov(Ptlp ~ Forest,  data = Metradica) %>%
  tukey_hsd()

ggboxplot(Metradica, x = "Forest", y = "Ptlp") +
  stat_pvalue_manual(
    stat.test, label = "p.adj", 
    y.position = c(0, 0.7, -0.5)
      )


library(dplyr)
library(ggplot2)
# BF vs TF per site

Metradica %>%
 filter(!is.na(Habitat)) %>%
 ggplot() +
 aes(x = Habitat, y = Ptlp, fill = Habitat) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(
 BF = "#4097F2", TF = "#EEC810")) +
 labs(x = "Habitat", y = "Turgor loss point (MPa)", fill = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 18L), plot.caption = element_text(size = 17L), 
 axis.title.y = element_text(size = 16L), axis.title.x = element_text(size = 13L)) +
 facet_wrap(vars(Forest)) + stat_compare_means()

# BF vs TF all sites blended
Metradica %>%
 filter(!is.na(Habitat)) %>%
 ggplot() +
 aes(x = Habitat, y = Ptlp, fill = Habitat) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(
 BF = "#4097F2", TF = "#EEC810")) +
 labs(x = "Habitat", y = "Turgor loss point (MPa)", fill = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 18L), plot.caption = element_text(size = 17L), 
 axis.title.y = element_text(size = 16L), axis.title.x = element_text(size = 13L)) + stat_compare_means()

#habitat preference
tlp <- Metradica %>%
 filter(!is.na(Type)) %>%
 ggplot() +
 aes(x = Type, y = log10(abs(Ptlp)), fill = Type) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#FFD361")) +
 labs(x = " ", y = "Turgor loss point (MPa)", 
 fill = "Habitat preference") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + stat_compare_means(method = "anova", label.y = 0.6, size = 3)+ theme(axis.title = element_text(size = 10)) +  stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 0.5, size = 7)

### 3 sites
 ggplot(Metradica) +
  aes(x = Forest, y = log10(abs(Ptlp)), fill = Forest) +
  geom_boxplot(shape = "circle") + labs(
    x = "",
    y = "Turgor loss point (MPa)"
  ) +
   scale_fill_manual(
    values = list(
      Bafog = "#F4C71C",
      Kaw = "#0051C1",
      Paracou = "#66FF61"
    )
  ) +
  theme_minimal() + theme(axis.title = element_text(size = 10)) +
  theme(
    plot.caption = element_text(size = 16L),
    axis.title.x = element_text(size = 21L), 
    axis.title.y = element_text(size = 15)
  ) +  stat_compare_means(method = "anova", label.y = 0.5, size = 4)+   stat_compare_means(aes(label = ..p.signif..), method = "anova",  size = 7)

```


*Litterature* 
* The paper by Zhu et al. (2018) in this issue of Tree Physiology provides a meta-analysis of TLP and its relationship to a range of hydraulic traits linked to drought tolerance, as well as to leaf economic traits, across an impressive 389 species (of which, data for 240 are published for the first time) from nine major forest types in China. 

*adjustments in leaf structure in response to seasonal water deficit (Niinemets 2001, Mitchell et al. 2008) and altered nutrient concentrations (Villagra et al. 2013) drive changes in leaf water relations traits, including TLP. Blackman 2018

*This plant functional trait represents the leaf water potential that induces wilting. Leaves with a more negative πtlp (measured in MPa) remain turgid at more negative water potentials and tend to maintain critical processes, such as leaf hydraulic conductance, stomatal conductance and photosynthetic gas exchange, under drier conditions (Cheung, Tyree & Dainty 1975; Abrams, Kubiske & Steiner 1990; Brodribb et al. 2003; Bartlett, Scoffoni & Sack 2012b; Guyot, Scoffoni & Sack 2012). Thus, a more negative value for πtlp contributes to greater leaf-level drought tolerance and therefore also plant-level drought tolerance. 


## LSWC - exploration 

One of the direct results of the regulation of stomatal movement is the reduction of water loss through transpiration by adjusting the leaf stomatal conductance, to achieve a high water-use efficiency and prevent embolism, which is called isohydric behavior. In contrast, the leaf stomatal conductance is kept at a relatively high level to maintain efficiently photosynthesis, which is known as anisohydric behavior (Roman et al., 2015). Therefore, LSWC reflect the plant's response to drought. (Zhou et al 2021)

```{r lswc-anova calcul, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
Metradica %>% group_by(Type) %>% summarise_at(vars(LSWC), funs(mean(LSWC, na.rm=TRUE))) 

# Global test
library(ggpubr)
library(ggfortify)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_LSWC<-lm(log10(LSWC) ~ Type,  data = Metradica)
#autoplot(Model_LSWC)
summary(Model_LSWC)
anova(Model_LSWC) # ANOVA reports a p-value far below 0.05, indicating there are differences in the means in the forest sites and habitat and varies across species.
tukey_LSWC <- TukeyHSD(aov(Model_LSWC))
library(agricolae)
tukey2 <- HSD.test(aov(Model_LSWC), trt = 'Type') 
#tukey3 <- HSD.test(aov(Model_LSWC), trt = 'Habitat')  
```

### Plots 

```{r HabitatPref_LSWC, warning=FALSE}

lswc <- Metradica %>%
 filter(!is.na(Type)) %>%
 ggplot() +
  aes(x = Type, y = log10(LSWC), fill = Type) +
  geom_boxplot(shape = "circle") +
  labs(
    x = "",
    y = "Leaf saturated water content (g.g)", fill ="Habitat preference"
  ) +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#FFD361"
    )
  ) +
  theme_minimal() +
  stat_compare_means(method = "anova", label.y = 0.75, size = 3)+ theme(axis.title = element_text(size = 10)) +  stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 0.5, size = 7)
lswc
``` 


### MajVLA - exploration

```{r lswc-anova, echo=FALSE, message=FALSE, warning=FALSE}
library(tidyr)
library(dplyr)
Metradica %>% group_by(Type) %>% summarise_at(vars(MajVLA), funs(mean(MajVLA, na.rm=TRUE))) 

# Global test
library(ggpubr)
library(ggfortify)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_MajVLA<-lm(log10(MajVLA) ~ Type,  data = Metradica)
#autoplot(Model_MajVLA)
summary(Model_MajVLA)
anova(Model_MajVLA) # ANOVA reports a p-value far below 0.05, indicating there are differences in the means in the forest sites and habitat and varies across species.
tukey_MajVLA <- TukeyHSD(aov(Model_MajVLA))
library(agricolae)
tukey2 <- HSD.test(aov(Model_MajVLA), trt = 'Type') 
#tukey3 <- HSD.test(aov(Model_MajVLA), trt = 'Habitat')  
```

### Plots

```{r HabitatPref_MajVLA}

vein <- Metradica %>%
 filter(!is.na(Type)) %>%
 ggplot() +
  aes(x = Type, y = log10(MajVLA), fill = Type) +
  geom_boxplot(shape = "circle") +
  labs(
    x = "",
    y = "Major vein density (mm.mm-2)", fill ="Habitat preference"
  ) +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#FFD361"
    )
  ) +
  theme_minimal() +
  stat_compare_means(method = "anova", label.y = 1.5, size = 3)+ theme(axis.title = element_text(size = 10)) +  stat_compare_means(aes(label = ..p.signif..),
                  method = "anova", label.y = 1.25, size = 7)
plot(vein)
``` 

## Summary Anova - 4 major traits: Ptlp, Gmin, LSWC, MajVLA

```{r}
library(ggpubr)

ggarrange(tlp, gmin, lswc, vein, ncol=2, nrow=2, common.legend = TRUE, legend="bottom", labels = c('A', 'B', 'C', 'D'))
```

