---
title: "Venation results"
author: "Marion Boisseaux"
date: "28/03/2022"
output: html_document
---
# Vein traits

The leaf is a critical component in the plant water transport system, accounting for 30% or more of whole-plant hydraulic resistance (Sack and Holbrook, 2006). Leaf venation architecture has numerous common functions across plant species—see Sack & Scoffoni, 2013 for review. Briefly, the leaf venation serves for mechanical support (Niklas, 1999), sugar and hormone transport in the phloem (Kehr & Buhtz, 2008), and, via the xylem, the replacement of water lost to transpiration when the stomata open for photosynthesis (Sack & Holbrook, 2006). However, venation architecture is highly diverse across species (Uhl & Mosbrugger, 1999; Roth-Nebelsick et al., 2001; Sack & Frole, 2006; Ellis et al., 2009; Brodribb et al., 2010). In dicotyledons, the leaf venation system typically consists of three orders of major veins and up to five higher orders of minor veins embedded in the mesophyll, with the vein orders arranged in a hierarchy; lower order veins are larger in diameter, with greater xylem conduit numbers and sizes, whereas higher order veins have greater length per leaf area (VLA; Sack & Holbrook, 2006; McKown et al., 2010). Total leaf VLA has been shown to correlate with maximum hydraulic conductance and photosynthetic rate per area across species (Sack & Frole, 2006; Brodribb et al., 2007) and tends to be higher for species growing in high light. Major VLA has been found to play a role in determining the damage tolerance of the vein system, and in leaf drought tolerance (Sack et al., 2008; Scoffoni et al., 2011). 


## Hypothesis

- Smaller leaves tend to have a higher major VLA. For SFF specialists, the replacement of water lost to transpiration during photosynthesis would be no problem during the wet season, since water is not a limiting factor. We collected the leaves during the dry season, therefore, SFF specialists would either have an adapted mechanisms to overcome water scarcity or not. 
- Leaves from the driest habitat, *Terra firme* are smaller and have a higher major VLA than the leaves from seasonally flooded habitats. 
- Leaves from Bafog (lower precipitation regime) are smaller with a higher major VLA than leaves in Kaw (higher precipitation regime). Paracou leaves major VLA values would range in the middle. 

Litterature :

*Smaller leaves tend to have higher major VLA intrinsically as a result of their development. The drought tolerance and protection conferred by higher major VLA in smaller leaves provides an explanation for the greater abundance of smaller leaves in drier and more exposed habitats (Scoffoni et al., 2011).*

*Drought impacts less leaves with higher major vein density because they can provide more numerous water flow pathways around the damaged vein. (Scoffoni et al 2011)*

*Smaller leaves, which generally have higher major vein density, would thus have lower hydraulic vulnerability. Tests using simulations with a spatially explicit model confirmed that smaller leaves with higher major vein density were more tolerant of major vein embolism.(Scoffoni et al 2011)*

From Scoffoni *et al* 2011:

* Smaller leaves more frequent in dry habitats
* Smaller leaves have thinner boundary layer: more rapid convective cooling  
* Direct hydraulic benefit of small leaves, if their greater major vein redundancy protects K  leaf from decline and thus contributes to drought tolerance.

## Materials and Method

Leaf area (LA, mm2 ) 
Major vein density (Major VLA, mm/mm2) : vein length per unit area 
Sum of vein densities for 1°, 2° and 3° veins (mm mm-2)
Double sided lamp flatbed scanner
ImageJ


*Why a higher VLA? To confer redundancy and drought tolerance*

Measurements from Scoffoni's Lab. These measures were calculated by a student group project from January - March 2022.

## Statistical analysis

* ANOVAs for the differences between SFF and TF habitat 
* ANOVAs for the differences between the three sites
* ANOVAs for the differences between habitat specialists and generalists
Species nested within those categories

Additional data to confront VLA with :

* Ptlp 
    + hypotheses : Species of TF habitat would exhibit greater expression of leaf drought tolerance traits than species from SFF habitat i.e. small leaves with high VLA associated with more negative values for osmotic potential at at turgor loss point.
- gmin (same VLA leaf)
    + Species of TF habitat would exhibit greater expression of leaf drought tolerance traits than species from SFF habitat i.e. small leaves with high VLA associated with lower minimal cuticular conductance. 
- LSWC 
    + Species of TF habitat would exhibit greater expression of leaf drought tolerance traits than species from SFF habitat i.e. small leaves with high VLA associated with higher LSWC more water per unit dry weight, that would provide a larger buffering capacity when water supply becomes limiting (higher water storage)
- Stomatal density *waiting for data*
- leaf chemistry *waiting for data*

Paracou data: 
```{r}
library(readr)
Paracou <- read_csv("Clean_data/Paracou.csv")
```
FTH data :
```{r}
FTH <- read_csv("Clean_data/FTH.csv")
```

Both FTH and Paracou data combined:

```{r}
Paracou_FTH<- read_csv("Clean_data/Paracou_FTH.csv")
```

Bafog data: 


Kaw data: 

## Results

```{r Import dataset veins, include=FALSE}
library(readxl)
library(forcats)
library(dplyr)
library(tidyverse)


veindata <- read_excel("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/Divers/Scoffoni/results/summarize_spp_avg.xlsx",     sheet = "for R")

veindata <- veindata %>%
    mutate(Species = recode(Species, 'Protium_picramnioides' = 'Protium_stevensonii')) %>%
    mutate(Species = recode(Species, 'Jacaranda_copaia' = 'Jacaranda_copaia subsp. Copaia'))


veindata$Species <- as.factor(veindata$Species)
fct_reorder(veindata$Species, veindata$LA, min)

veindata$MajVLA <- as.numeric(veindata$MajVLA)

```

### Across species from all habitats

```{r echo=FALSE}
library(ggplot2)
library(forcats)
library(dplyr)
library(tidyverse)


ggplot(veindata) +
 aes(x = fct_reorder(Species, LA), y = LA, fill = Species) +
 geom_boxplot(shape = "circle") +
 theme_minimal() + 
 facet_grid(vars(Site), vars()) + 
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


ggplot(veindata) +
 aes(x = fct_reorder(Species, MajVLA), y = MajVLA, fill = Species) +
 geom_boxplot(shape = "circle") +
 theme_minimal() + 
 facet_grid(vars(Site), vars()) + 
theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))


```




### SFF vs TF habitats

```{r echo=FALSE}

library(ggplot2)

ggplot(veindata) +
 aes(x = Habitat, y = LA, fill = Habitat) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(
 BF = "#6DB9F8", TF = "#FFA961")) +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15L), 
 plot.caption = element_text(size = 14L), axis.title.y = element_text(size = 14L), axis.title.x = element_text(size = 18L)) +
 facet_wrap(vars(Site))


ggplot(veindata) +
 aes(x = Habitat, y = MajVLA, fill = Habitat) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(
 BF = "#6DB9F8", TF = "#FFA961")) +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15L), 
 plot.caption = element_text(size = 14L), axis.title.y = element_text(size = 14L), axis.title.x = element_text(size = 18L)) +
 facet_wrap(vars(Site))

```



### Specialists SFF vs Specialists TF vs Generalists


```{r echo=FALSE}

library(ggplot2)
ggplot(veindata) +
 aes(x = Pref_Habitat, y = LA, fill = Pref_Habitat) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(BF = "#495BE3", Generalist = "#AED3CC", TF = "#F0C323")) +
 theme_minimal() +
 facet_wrap(vars(Site))

ggplot(veindata) +
 aes(x = Pref_Habitat, y = MajVLA, fill = Pref_Habitat) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(BF = "#495BE3", Generalist = "#AED3CC", TF = "#F0C323")) +
 theme_minimal() +
 facet_wrap(vars(Site))


```


### Bafog vs Kaw
```{r echo=FALSE}
library(ggplot2)

ggplot(veindata) +
 aes(x = Site, y = LA, fill = Site) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(
 Bafog = "#E5B922", KAW = "#0040C1", PARACOU = "#E5D1DD")) +
 theme_minimal()

ggplot(veindata) +
 aes(x = Site, y = MajVLA, fill = Site) +
 geom_boxplot(shape = "circle") +
 scale_fill_manual(values = list(
 Bafog = "#E5B922", KAW = "#0040C1", PARACOU = "#E5D1DD")) +
 theme_minimal()

```



