---
title: "Results_prelim"
author: "Marion Boisseaux"
date: "04/05/2022"
output: html_document
editor_options: 
  chunk_output_type: console
---


The data

```{r echo=FALSE, message=FALSE, warning=FALSE}
Metradica <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica")
```

# Data exploration 

How to visualize the data and show the links between the variables and identify the same responses of the individuals? 


## General PCA 

### Contribution of individuals and variables : 1-2 dimensions

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(FactoMineR)
library(Factoshiny)


#resultPCA <- Factoshiny(Metradica[,c(5:13,20)])

#dim 1-2

#Contribution
res.PCA<-PCA(Metradica[,c(8:13,20)],graph=FALSE)

a1<- plot.PCA(res.PCA,choix='var',habillage = 'contrib',title="Graphe des variables de l'ACP")

a2<-plot.PCA(res.PCA,invisible=c('quali'),habillage='contrib',title="Graphe des individus de l'ACP",cex=2,cex.main=2,cex.axis=2,col.quali='#9AE019',label =c('ind.sup'))

a1
a2
```

### Contribution of individuals and variables : 1-2 dimensions

```{r echo=FALSE, message=FALSE, warning=FALSE}
#dim 3-4
res.PCA<-PCA(Metradica[,c(8:13,20)],graph=FALSE)

b1<-plot.PCA(res.PCA,axes=c(3,4),choix='var',title="Graphe des variables de l'ACP")

b2<-plot.PCA(res.PCA,axes=c(3,4),invisible=c('ind.sup'),title="Graphe des individus de l'ACP",cex=2,cex.main=2,cex.axis=2,col.quali='#9AE019', label = c('quali'))

b1
b2

```

### Habitat collected


```{r echo=FALSE, message=FALSE, warning=FALSE}

#Habitat collected

res.PCA<-PCA(Metradica[, c(6, 8:13, 20)],quali.sup=c(1),graph=FALSE)

c1<- plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="",cex=2.25,cex.main=2.25,cex.axis=2.25,col.quali='#FFC400',label =c('quali'))

c2<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=1.9,cex.main=1.9,cex.axis=1.9,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(c2,c1), ncol = 2)


```


### Habitat preference -type

```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[,c(7, 8:13, 20)],quali.sup=c(1),graph=FALSE)

d2<- plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=1.8,cex.main=1.8,cex.axis=1.8,col.quali='#FF6600',label =c('quali'))


d1<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title ="" ,cex=1.9,cex.main=1.7,cex.axis=1.7,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(d2,d1), ncol = 2)

```

### Forest sites 
```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[,c(5, 8:13, 20)],quali.sup=c(1),graph=FALSE)

e2<-plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=2.1,cex.main=2.1,cex.axis=2.1,col.quali='#3622E6',label =c('quali'))

e1<-plotellipses(res.PCA, keepvar=1,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=1.9,cex.main=1.9,cex.axis=1.9,col.quali='#7A067A',label =c('quali'))

ggpubr::ggarrange(nrow = 1, plotlist = list(e2,e1), ncol = 2)

```


### Dawkins of tree

```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[c(8:13, 24)],quali.sup=c(7),graph=FALSE)

plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",col.quali='#FFC400',label =c('quali'))
```

### Species

```{r echo=FALSE, message=FALSE, warning=FALSE}
res.PCA<-PCA(Metradica[c(4,8:13)],quali.sup=c(1),graph=FALSE)

g2<- plot.PCA(res.PCA,invisible=c('ind','ind.sup'),title="Graphe des individus de l'ACP",cex=0.9,cex.main=1.6,cex.axis=1.6,col.quali='#2BF0D2',label =c('quali'))


g2
```


## Distribution of major traits 

*after log tranform*

### leaf minimal conductance


```{r}
library(ggplot2)

ggplot(Metradica) +
 aes(x = log10(Gmin)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

### Turgor loss point
```{r}

ggplot(Metradica) +
 aes(x = log10(abs(Ptlp))) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

### Leaf area

```{r}
ggplot(Metradica) +
 aes(x = log10(LA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()

```

### Specifig leaf area
```{r}

ggplot(Metradica) +
 aes(x = log10(SLA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```

### leaf saturated water content
```{r}
ggplot(Metradica) +
 aes(x = log10(LSWC)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()
```


### Major vein density
```{r}
ggplot(Metradica) +
 aes(x = log10(MajVLA)) +
 geom_histogram(bins = 30L, fill = "#112446") +
 theme_minimal()

```




```{r}

library(ggplot2)

ggplot(Metradica) +
 aes(x = LT, y = MajVLA, fill = Name) +
 geom_point(shape = "circle", size = 1.5, colour = "#112446") +
 scale_fill_hue(direction = 1) +
 theme_minimal()

ggplot(Metradica) +
 aes(x = DBH, y = MajVLA, colour = Name) +
 geom_point(shape = "circle", size = 1.5) +
 scale_color_hue(direction = 1) +
 theme_minimal()

ggplot(Metradica) +
 aes(x = Forest, y = Gmin, colour = Name) +
 geom_boxplot(shape = "circle", fill = "#112446") +
 scale_color_hue(direction = 1) +
 theme_minimal()

ggplot(Metradica) +
 aes(x = Forest, y = Ptlp, colour = Name) +
 geom_boxplot(shape = "circle", fill = "#112446") +
 scale_color_hue(direction = 1) +
 theme_minimal()

```

