---
title: "ReunionMEtradica"
author: "Marion Boisseaux"
date: "16/06/2022"
output: html_document
---

# Libraries

```{r}
library(tidyverse)
library(dplyr)
library(factoextra)
library(FactoMineR)
library(Factoshiny)
library(corrplot) 
library(ggpubr)
library(ggfortify)
library(agricolae)
library(rstatix)
```

# Data

```{r message=FALSE, warning=FALSE}

Metradica <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica") %>% 
  select(Code, Genus, Species, Name, Habitat, Forest, Type, HabitatType, Gmin, TLP, LA, SLA, LSWC, MajVLA, MidribWidth, SecundaryWidth, TreeHeight, TreeDawkins, TWI_JC) %>% 
  mutate(TreeHeight = as.numeric(TreeHeight)) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth", "TreeHeight"), abs) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth", "TreeHeight"), log) %>% 
  mutate(TLP = -TLP) %>% 
  na.omit() 

#levels(Habitat) <- list(SF  = "BF")
#Phylo <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1KBppmJ2SBLMao0qeRwb0xBOvv5mYJrHunbAQCpdz5qU/edit#gid=0", range = "summary") %>% select(Order, Family, Genus)


#Metradica <- left_join(Metradica_log, Phylo, by = 'Genus') %>% relocate(Order, Family, .after = Code)

#Metradica_log <- Metradica_log %>% subset( Code != "674")



```

# PCA

To characterize the functional trait space in each habitat, we performed a Principal Component Analysis (PCA) with trait values at the individual level (i.e. each score in the PCA refers to an individual tree),  to analyze trait covariation and to reveal the relationships between traits. 

Using the among PCA, a “classic” PCA, we aim to evaluate trait syndroms characterizing species strategies. For the within PCA, all the gravity centers are placed back at the origin and the individuals are being represented with a maximal variance. We eliminate the species effect to study the individual strategies. The among-PCA searches the axes at the center of gravity and emphasizes on the differences between groups (here, species) whereas the within-PCA searches for the shared-axes in each group.

```{r}

res.PCA<-PCA(Metradica[, c(1:18)][,-c(1,2,3,4,5,7,8,18)],quali.sup=c(1),graph=FALSE)

# Visualize eigenvalues/variances
fviz_screeplot(res.PCA, addlabels = TRUE, ylim = c(0, 50)) # 70 % de notre jeu de données est expliqué avec les 4

# dim 1-2 

## variables
fviz_pca_var(res.PCA, axes = c(3,4), col.var='contrib', gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))+
 theme_classic() 

## Biplot 1,2
fviz_pca_biplot(res.PCA,axes = c(1,2),  col.var='contrib', gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), label="var",  repel = TRUE # Avoid text overlapping
                )  + ylim(-4,4) + theme_classic()
## dim 3,4
fviz_pca_biplot(res.PCA,axes = c(3,4),  col.var='contrib', gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), label="var",  repel = TRUE # Avoid text overlapping
                )  + ylim(-4,4) + theme_classic()


## Forest
res.PCA<-PCA(Metradica[, c(1:18)][,-c(1,2,3,4,5,7,8,18)],quali.sup=c(1),graph=FALSE)
fviz_pca_biplot(res.PCA, label="var", habillage = c(1),  repel = TRUE # Avoid text overlapping)
                ,addEllipses=TRUE, ellipse.level=0.95) + scale_color_brewer(palette="Set1")   #ylim(-0.2,0.2)+ xlim(-0.2,0.2)
  + theme_classic() 

fviz_pca_biplot(res.PCA, axes = c(1,2), label="var", habillage = c(1),  repel = TRUE # Avoid text overlapping)
                ,addEllipses=TRUE, ellipse.level=0.95) + scale_color_brewer(palette="Set2")  + ylim(-0.4,0.4)+ xlim(-0.4,0.4) + theme_classic() 

## HabitatType
res.PCA<-PCA(Metradica[, c(1:18)][,-c(1,2,3,4,5,6,7,18)],quali.sup=c(1),graph=FALSE)
fviz_pca_biplot(res.PCA, label="var", habillage = c(1),  repel = TRUE # Avoid text overlapping)
                ,addEllipses=TRUE, ellipse.level=0.95) + scale_color_brewer(palette="Set2")   #ylim(-0.2,0.2)+ xlim(-0.2,0.2)
  + theme_classic() 

## Habitat de collecte
res.PCA<-PCA(Metradica[, c(1:18)][,-c(1,2,3,4,6,7,8,18)],quali.sup=c(1),graph=FALSE)
fviz_pca_biplot(res.PCA, label="var", habillage = c(1),  repel = TRUE # Avoid text overlapping)
                ,addEllipses=TRUE, ellipse.level=0.95) + scale_color_brewer(palette="Set2") + ylim(-0.2,0.2)+ xlim(-0.2,0.2)
  + theme_classic() 
fviz_pca_biplot(res.PCA, axes = c(3,4), label="var", habillage = c(1),  repel = TRUE # Avoid text overlapping)
                ,addEllipses=TRUE, ellipse.level=0.95) + scale_color_brewer(palette="Set2")   #ylim(-0.2,0.2)+ xlim(-0.2,0.2)
  + theme_classic() 


```
# Correlation plot

```{r corrplotTraits, fig.cap="ACorrelation of leaf traits."}
dplyr::select(Metradica_log, -Code, -Genus, -Species, -Name, -Forest, -Habitat, -Type, -HabitatType, -TreeDawkins) %>% 
  cor() %>% 
  corrplot::corrplot.mixed()
```

# 1 - Differences between habitats ? 

## A - TF vs BF

## gmin habitat collected
```{r}
# Global test

Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_gmin<-lm(Gmin ~ Habitat,  data = Metradica)
autoplot(Model_gmin)
summary(Model_gmin)
anova(Model_gmin) 

tukey <- HSD.test(aov(Model_gmin), trt = 'Habitat') 

#plot

stat.test.gmin<- aov(lm(Gmin~Habitat, data=Metradica)) %>% tukey_hsd() 

gmin <- ggboxplot(data = Metradica,x = "Habitat", y = "Gmin", fill = "Habitat") + 
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Minimal conductance (mmol.m-2.s-1)", 
 fill = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.gmin, label = "p.adj.signif",
                       y.position = c(5), hide.ns = TRUE)
                                                                       
gmin
```

## TLP habitat collected
```{r}
# Global test

Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_TLP<-lm(TLP ~ Habitat,  data = Metradica)
autoplot(Model_TLP)
summary(Model_TLP)
anova(Model_TLP) 

tukey <- HSD.test(aov(Model_TLP), trt = 'Habitat') 

#plot

stat.test.TLP<- aov(lm(TLP~Habitat, data=Metradica)) %>% tukey_hsd() 

TLP <- ggboxplot(data = Metradica,x = "Habitat", y = "TLP", fill = "Habitat") + 
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Turgor loss point (MPa)", 
 fill = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.TLP, label = "p.adj.signif",
                       y.position = c(-0.1), hide.ns = TRUE)
                                                                       
TLP
```

## LSWC habitat collected

```{r}
# Global test

Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_LSWC<-lm(LSWC ~ Habitat,  data = Metradica)
autoplot(Model_LSWC)
summary(Model_LSWC)
anova(Model_LSWC) 

tukey <- HSD.test(aov(Model_LSWC), trt = 'Habitat') 

#plot

stat.test.LSWC<- aov(lm(LSWC~Habitat, data=Metradica)) %>% tukey_hsd() 

LSWC <- ggboxplot(data = Metradica,x = "Habitat", y = "LSWC", fill = "Habitat") + 
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Leaf saturated water content (g.g)", 
 fill = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.LSWC, label = "p.adj.signif",
                       y.position = c(1.3), hide.ns = TRUE)
                                                                       
LSWC
```

## MajVLA habitat collected

```{r}
# Global test

Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_MajVLA<-lm(MajVLA ~ Habitat,  data = Metradica)
autoplot(Model_MajVLA)
summary(Model_MajVLA)
anova(Model_MajVLA) 

tukey <- HSD.test(aov(Model_MajVLA), trt = 'Habitat') 

#plot

stat.test.MajVLA<- aov(lm(MajVLA~Habitat, data=Metradica)) %>% tukey_hsd() 

MajVLA <- ggboxplot(data = Metradica,x = "Habitat", y = "MajVLA", fill = "Habitat") + 
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Major vein density (mm.mm-2)", 
 fill = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.MajVLA, label = "p.adj.signif",
                       y.position = c(3), hide.ns = TRUE)
                                                                       
MajVLA
```

```{r Summary tlp, gmin, vein, lswc}
library(ggpubr)

ggarrange(TLP, gmin, LSWC, MajVLA, ncol=2, nrow=2, common.legend = TRUE, legend="bottom", labels = c('A', 'B', 'C', 'D'))
```

## B - Trait ~ TWI 

## gmin 
```{r}

#plot

gmin <- ggscatter(data = Metradica,x = "TWI_JC", y = "Gmin", color = "Habitat", 
                  add = "reg.line",  # Add regression line)
                  add.params = list(color = "Habitat", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                  ) +
  stat_cor(aes(color = Habitat), label.x = 10, size = 6) +
  scale_color_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = "Topographic wetness index", y = "Minimal conductance (mmol.m-2.s-1)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
     
                                                        
gmin
```

## TLP 
```{r}

#plot

TLP <- ggscatter(data = Metradica,x = "TWI_JC", y = "TLP", color = "Habitat", 
                  add = "reg.line",  # Add regressin line)
                  add.params = list(color = "Habitat", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                 ) +
  stat_cor(aes(color = Habitat), label.x = 10, size = 6)+
  scale_color_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = "Topographic wetness index", y = "Turgor loss point (MPa)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
    
                                                                  
TLP
```

## LSWC 
```{r}

#plot

LSWC <- ggscatter(data = Metradica,x = "TWI_JC", y = "LSWC", color = "Habitat", 
                  add = "reg.line",  # Add regressin line)
                  add.params = list(color = "Habitat", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                  ) +
  stat_cor(aes(color = Habitat), label.x = 10, size = 6) +
  scale_color_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = "Topographic wetness index", y = "Leaf saturated water content (g.g-1)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
    
                                                                  
LSWC
```

## MajVLA 
```{r}

#plot

MajVLA <- ggscatter(data = Metradica,x = "TWI_JC", y = "MajVLA", color = "Habitat", 
                  add = "reg.line",  # Add regressin line)
                  add.params = list(color = "Habitat", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                  ) +
  stat_cor(aes(color = Habitat), label.x = 10, size = 6)+
  scale_color_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = "Topographic wetness index", y = "Major vein density (mm.mm-2)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
    
                                                                  
MajVLA
```

```{r Summary tlp, gmin, vein, lswc}
library(ggpubr)

ggarrange(TLP, gmin, LSWC, MajVLA, ncol=2, nrow=2, common.legend = TRUE, legend="bottom", labels = c('A', 'B', 'C', 'D'))
```

## C - Strategies in each habitat

```{r}
test <- Metradica %>% filter(Habitat == 'TF') %>% filter(Type =='TF')


gmin_TF <- ggscatter(data = test,x = "TWI_JC", y = "Gmin", color = "Name", 
                  add = "reg.line",  # Add regression line)
                  add.params = list(color = "Name", fill = "lightgray"), # Customize reg. line
                  conf.int = FALSE, # Add confidence interval
                  ) +
  stat_cor(aes(color = Name), label.x = 10, size = 6) +
 labs(x = "Topographic wetness index", y = "Minimal conductance (mmol.m-2.s-1)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
gmin_TF
test <- Metradica %>% filter(Habitat == 'BF') %>% filter(Type =='BF')


gmin_SF <- ggscatter(data = test,x = "TWI_JC", y = "Gmin", color = "Name", 
                  add = "reg.line",  # Add regression line)
                  add.params = list(color = "Name", fill = "lightgray"), # Customize reg. line
                  conf.int = FALSE, # Add confidence interval
                  ) +
  stat_cor(aes(color = Name), label.x = 12, size = 6) +
 labs(x = "Topographic wetness index", y = "Minimal conductance (mmol.m-2.s-1)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
gmin_SF

ggarrange(gmin_TF, gmin_SF, ncol=2, nrow=1, common.legend = TRUE, legend="bottom", labels = c('Terra firme specialists', 'Seasoanlly flooded specialists'))

```



# 2- Habitat preference 


## A - Trait ~ TWI 

## gmin 
```{r}

#plot

gmin <- ggscatter(data = Metradica,x = "TWI_JC", y = "Gmin", color = "Type", 
                  add = "reg.line",  # Add regression line)
                  add.params = list(color = "Type", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                  ) +
  stat_cor(aes(color = Type), label.x = 12, size = 6) +
  scale_color_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404", 
      Generalist = "#53db46"
    )) +
 labs(x = "Topographic wetness index", y = "Minimal conductance (mmol.m-2.s-1)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
     
                                                        
gmin
```

## TLP 
```{r}

#plot

TLP <- ggscatter(data = Metradica,x = "TWI_JC", y = "TLP", color = "Type", 
                  add = "reg.line",  # Add regressin line)
                  add.params = list(color = "Type", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                 ) +
  stat_cor(aes(color = Type), label.x = 10, size = 6)+
  scale_color_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404",
      Generalist = "#53db46"
    )) +
 labs(x = "Topographic wetness index", y = "Turgor loss point (MPa)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
    
                                                                  
TLP
```

## LSWC 
```{r}

#plot

LSWC <- ggscatter(data = Metradica,x = "TWI_JC", y = "LSWC", color = "Type", 
                  add = "reg.line",  # Add regressin line)
                  add.params = list(color = "Type", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                  ) +
  stat_cor(aes(color = Type), label.x = 12, size = 6) +
  scale_color_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404",
      Generalist = "#53db46"
    )) +
 labs(x = "Topographic wetness index", y = "Leaf saturated water content (g.g-1)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
    
                                                                  
LSWC
```

## MajVLA 
```{r}

#plot

MajVLA <- ggscatter(data = Metradica,x = "TWI_JC", y = "MajVLA", color = "Type", 
                  add = "reg.line",  # Add regressin line)
                  add.params = list(color = "Type", fill = "lightgray"), # Customize reg. line
                  conf.int = TRUE, # Add confidence interval
                  ) +
  stat_cor(aes(color = Type), label.x = 12, size = 6)+
  scale_color_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404",
      Generalist = "#53db46"
    )) +
 labs(x = "Topographic wetness index", y = "Major vein density (mm.mm-2)") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 15), 
 plot.caption = element_text(size = 15), axis.title.y = element_text(size = 15), axis.title.x = element_text(size = 15)) + theme(axis.title = element_text(size = 15)) 
    
                                                                  
MajVLA
```

```{r Summary tlp, gmin, vein, lswc}
library(ggpubr)

ggarrange(TLP, gmin, LSWC, MajVLA, ncol=2, nrow=2, common.legend = TRUE, legend="bottom", labels = c('A', 'B', 'C', 'D'))
```

## B- Boxplot generalist BF vs generalist TF ? 
## gmin

```{r}


# Global test

Metradica$HabitatType <- as.factor(Metradica$HabitatType)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Name <- as.factor(Metradica$Name)
Model_gmin<-lm(Gmin ~ HabitatType,  data = Metradica)
autoplot(Model_gmin)
summary(Model_gmin)
anova(Model_gmin) 

tukey <- HSD.test(aov(Model_gmin), trt = 'HabitatType') 

#plot

stat.test.gmin<- aov(lm(Gmin~HabitatType, data=Metradica)) %>% tukey_hsd() 

gmin <- ggboxplot(data = Metradica,x = "HabitatType", y = "Gmin", fill = "Type", color = "Habitat") +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#b58404"
    )) + 
  scale_colour_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Minimal conductance (mmol.m-2.s-1)", 
 fill = "Habitat preference", color = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.gmin, label = "p.adj.signif",
                       y.position = c(5), hide.ns = TRUE)
                                                                       
gmin
```



## TLP

```{r}
# Global test

Metradica$HabitatType <- as.factor(Metradica$HabitatType)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Name <- as.factor(Metradica$Name)
Model_TLP<-lm(TLP ~ HabitatType,  data = Metradica)
autoplot(Model_TLP)
summary(Model_TLP)
anova(Model_TLP) 

tukey <- HSD.test(aov(Model_TLP), trt = 'HabitatType') 

#plot

stat.test.TLP<- aov(lm(TLP~HabitatType, data=Metradica)) %>% tukey_hsd() 

TLP <- ggboxplot(data = Metradica,x = "HabitatType", y = "TLP", fill = "Type", color = "Habitat") +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#b58404"
    )) + 
  scale_colour_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Turgor loss point (MPa)", 
 fill = "Habitat preference", color = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.TLP, label = "p.adj.signif",
                       y.position = c(0, 0.2), hide.ns = TRUE)
                                                                       
TLP
```

##LSWC

```{r}
# Global test

Metradica$HabitatType <- as.factor(Metradica$HabitatType)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Name <- as.factor(Metradica$Name)
Model_LSWC<-lm(LSWC ~ HabitatType,  data = Metradica)
autoplot(Model_LSWC)
summary(Model_LSWC)
anova(Model_LSWC) 

tukey <- HSD.test(aov(Model_LSWC), trt = 'HabitatType') 

#plot

stat.test.LSWC<- aov(lm(LSWC~HabitatType, data=Metradica)) %>% tukey_hsd() 

LSWC <- ggboxplot(data = Metradica,x = "HabitatType", y = "LSWC", fill = "Type", color = "Habitat") +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#b58404"
    )) + 
  scale_colour_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Leaf saturated water content (g.g-1)", 
 fill = "Habitat preference", color = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.LSWC, label = "p.adj.signif",
                       y.position = c(1.2, 1.4,1.6), hide.ns = TRUE)
                                                                       
LSWC
```

##MajVLA
```{r}
# Global test

Metradica$HabitatType <- as.factor(Metradica$HabitatType)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Name <- as.factor(Metradica$Name)
Model_MajVLA<-lm(MajVLA ~ HabitatType,  data = Metradica)
autoplot(Model_MajVLA)
summary(Model_MajVLA)
anova(Model_MajVLA) 

tukey <- HSD.test(aov(Model_MajVLA), trt = 'HabitatType') 

#plot

stat.test.MajVLA<- aov(lm(MajVLA~HabitatType, data=Metradica)) %>% tukey_hsd() 

MajVLA <- ggboxplot(data = Metradica,x = "HabitatType", y = "MajVLA", fill = "Type", color = "Habitat") +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#b58404"
    )) + 
  scale_colour_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Major vein density (mm.mm-2)", 
 fill = "Habitat preference", color = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.MajVLA, label = "p.adj.signif",
                       y.position = c(2.8, 3,3.2), hide.ns = TRUE)
                                                                       
MajVLA
```

```{r Summary tlp, gmin, vein, lswc}

ggarrange(TLP, gmin, LSWC, MajVLA, ncol=2, nrow=2, common.legend = TRUE, legend="bottom", labels = c('A', 'B', 'C', 'D'))
```


# 3- ITV

### CV
```{r}
cv <- function(traits){
  if(any(is.na(traits)))
    traits=traits[!is.na(traits)]
  N=length(traits)
  y_bar=mean(traits)
  s2_hat=var(traits)
  cv_2=s2_hat/y_bar^2
  cv_1=sqrt(cv_2)
  gamma_1=sum(((traits-y_bar)/s2_hat^0.5)^3)/N
  gamma_2=sum(((traits-y_bar)/s2_hat^0.5)^4)/N
  bias=cv_2^(3/2)/N*(3*cv_2^0.5-2*gamma_1)
  bias2=cv_1^3/N-cv_1/4/N-cv_1^2*gamma_1/2/N-cv_1*gamma_2/8/N
  cv1=sd(traits)/mean(traits)
  cv4=cv_1-bias2
  re=cv4
  return(re)
} 

cv <- Metradica %>% 
  group_by(Type) %>% 
  summarise_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth"), funs(cv))

cv <- bind_rows(cv,
                ungroup(cv) %>% 
                  summarise_all(mean) %>% 
                  mutate(Type = "mean"))

cv_long <- reshape2::melt(cv, "Type", variable.name = "trait", value.name = "CV") %>% 
  mutate(trait = recode(trait, "Ptlp" = "pi[TLP]", "gmin" = "g[min]"))


cv_long %>%  
  filter(Type != "mean") %>% 
  ggplot(aes(x = trait, y = CV)) +
  geom_boxplot() +
  geom_jitter(aes(col = Type)) +
  geom_text(aes(label = paste0(round(CV, 2)*100, "%")), y = 2, col = "black",
            data = filter(cv_long, Type == "mean")) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text()) +
  ylab(expression(CV[4])) +
  scale_color_discrete("") +
  scale_x_discrete(labels = scales::label_parse())

```

## CV table

```{r cvsptab}
knitr::kable(cv, caption = "Coefficients of variation ($CV_4$) across each species.", digits = 3) 
```

# 4- Partitionnement variance

```{r}
#Gmin, TLP, LA, SLA, LSWC, MajVLA, MidribWidth, SecundaryWidth

data <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica")  %>% 
  select(Code, Genus, Species, Name, Habitat, Forest, Type, HabitatType, Gmin, TLP, LA, SLA, LSWC, MajVLA, MidribWidth, SecundaryWidth) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth"), abs) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth"), log) %>% 
  na.omit()

varcomp.gmin<-varcomp(lme(Gmin~1,random=~1|Forest/Habitat/Species, data = data, na.action = na.omit),1) 

varcomp.tlp<-varcomp(lme(TLP~1,random=~1|Forest/Habitat/Species, data = data, na.action = na.omit),1)

varcomp.LA<-varcomp(lme(LA~1,random=~1|Forest/Habitat/Species, data = data, na.action = na.omit),1)

varcomp.SLA<-varcomp(lme(SLA~1,random=~1|Forest/Habitat/Species, data = data, na.action = na.omit),1)

varcomp.LSWC<-varcomp(lme(LSWC~1,random=~1|Forest/Habitat/Species, data = data, na.action = na.omit),1)

varcomp.MajVLA<-varcomp(lme(MajVLA~1,random=~1|Forest/Habitat/Species, data = data, na.action = na.omit),1)

vars <- bind_rows(varcomp.gmin, varcomp.tlp, varcomp.LA, varcomp.SLA, varcomp.LSWC, varcomp.MajVLA) %>% mutate(Trait = "")

#library(rio)
#export(vars, "vars.csv")

vars <- read_delim("vars_traits.csv", 
    delim = ";", escape_double = FALSE, trim_ws = TRUE)


vars <- reshape2::melt(vars, "Trait", variable.name = "level", value.name = "variance") 

```


```{r}

library(paletteer) 
paletteer_d("RColorBrewer::GnBu")

ggplot(vars, aes(fill=level, y=variance, x=Trait)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(
    values = list(
      Forest = "#A8DDB5FF",
      Habitat = "#2B8CBEFF",
      Species = "#e0b1e3",
      Residual = "#516363"
    )) + 
  theme_minimal() +
  labs(x = "", y = "Portion of total variance (%)")
```



### Par habitat : Trait en fonction du gradient de précipitation
```{r}
library(tidyr)
library(dplyr)

# Global test

Metradica$HabitatType <- as.factor(Metradica$HabitatType)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Name <- as.factor(Metradica$Name)
Model_MajVLA<-lm(MajVLA ~ HabitatType,  data = Metradica)
autoplot(Model_MajVLA)
summary(Model_MajVLA)
anova(Model_MajVLA) 

tukey <- HSD.test(aov(Model_MajVLA), trt = 'HabitatType') 

#plot

stat.test.MajVLA<- aov(lm(MajVLA~HabitatType, data=Metradica)) %>% tukey_hsd() 

MajVLA <- ggboxplot(data = Metradica,x = "HabitatType", y = "MajVLA", fill = "Type", color = "Habitat") +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#b58404"
    )) + 
  scale_colour_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Turgor loss point (MPa)", 
 fill = "Habitat preference", color = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.MajVLA, label = "p.adj.signif",
                       y.position = c(30), hide.ns = TRUE)
                                                                       
MajVLA

# trait across precipitation gradient

test <- Metradica %>% filter(Habitat == 'TF')


test$HabitatType <- as.factor(test$HabitatType)
test$Forest <- as.factor(test$Forest)
test$Forest<- ordered(test$Forest, levels=c('Bafog', 'Paracou', 'Kaw'))
test$Name <- as.factor(test$Name)
Model_MajVLA2<-lm(MajVLA ~ Forest,  data = test)
autoplot(Model_MajVLA2)
summary(Model_MajVLA2)
anova(Model_MajVLA2) 

tukey <- HSD.test(aov(Model_MajVLA2), trt = 'Forest') #le TF de bafog est diff des autres !!!

stat.test.MajVLA2<- aov(lm(MajVLA~Forest, data=test)) %>% tukey_hsd() 


#plot habitat TF 
ggboxplot(data = test,x = "Forest", y = "MajVLA", fill = "Forest", color = "HabitatType") + scale_x_discrete(labels = c('1500','3000','4000')) +
  scale_fill_manual(
    values = list(
      Bafog = "#eb4934",
      Paracou = "#d9c40d",
      Kaw = "#0dc4d9"
    )) + 
  scale_colour_manual(
    values = list(
      TFGeneralist = "#141313",
      TFTF = "#ff0000" 
      
    )) +
 labs(title = "Terra firme accross precipitation gradient", x = "Annual Precipitation (mm.an-1)", y = "Turgor loss point (MPa)", 
 fill = "Precipitation", color = "Habitat preference") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 10)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.MajVLA2, label = "p.adj.signif",
                       y.position = c(3,2.5), hide.ns = TRUE)
                 
#BF
test2 <- Metradica %>% filter(Habitat == 'BF')


test2$HabitatType <- as.factor(test2$HabitatType)
test2$Forest <- as.factor(test2$Forest)
test2$Forest<- ordered(test2$Forest, levels=c('Bafog', 'Paracou', 'Kaw'))
test2$Name <- as.factor(test2$Name)
Model_MajVLA3<-lm(MajVLA ~ Forest,  data = test2)
autoplot(Model_MajVLA3)
summary(Model_MajVLA3)
anova(Model_MajVLA3) 

tukey <- HSD.test(aov(Model_MajVLA3), trt = 'Forest') #le TF de bafog est diff des autres !!!

stat.test.MajVLA3<- aov(lm(MajVLA~Forest, data=test2)) %>% tukey_hsd() 


#plot habitat BF 
ggboxplot(data = test2,x = "Forest", y = "MajVLA", fill = "Forest", color = "HabitatType") + scale_x_discrete(labels = c('1500','3000','4000')) +
  scale_fill_manual(
    values = list(
      Bafog = "#eb4934",
      Paracou = "#d9c40d",
      Kaw = "#0dc4d9"
    )) + 
  scale_colour_manual(
    values = list(
      BFGeneralist = "#141313",
      BFBF = "#ff0000" 
      
    )) +
 labs(title = "SFF across precipiation gradient", x = "Annual precipitation (mm.an-1)", y = "Turgor loss point (MPa)", 
 fill = "Precipitation", color = "Habitat preference") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 10)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.MajVLA2, label = "p.adj.signif",
                       y.position = c(3,2.5), hide.ns = TRUE)

```


### Par habitat : Trait en fonction du gradient de précipitation
```{r}

# Global test

Metradica$HabitatType <- as.factor(Metradica$HabitatType)
Metradica$Habitat <- as.factor(Metradica$Habitat)
Metradica$Forest <- as.factor(Metradica$Forest)
Metradica$Name <- as.factor(Metradica$Name)
Model_gmin<-lm(Gmin ~ HabitatType,  data = Metradica)
autoplot(Model_gmin)
summary(Model_gmin)
anova(Model_gmin) 

tukey <- HSD.test(aov(Model_gmin), trt = 'HabitatType') 

#plot

stat.test.gmin<- aov(lm(Gmin~HabitatType, data=Metradica)) %>% tukey_hsd() 

gmin <- ggboxplot(data = Metradica_log,x = "HabitatType", y = "Gmin", fill = "Type", color = "Habitat") +
  scale_fill_manual(
    values = list(
      BF = "#6DB4EE",
      Generalist = "#B6F09A",
      TF = "#b58404"
    )) + 
  scale_colour_manual(
    values = list(
      BF = "#6DB4EE",
      TF = "#b58404"
    )) +
 labs(x = " ", y = "Minimal conductance (mmol.m-2.s-1)", 
 fill = "Habitat preference", color = "Habitat collected") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 20L)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.gmin, label = "p.adj.signif",
                       y.position = c(30), hide.ns = TRUE)
                                                                       
gmin

# trait across precipitation gradient

test <- Metradica %>% filter(Habitat == 'TF')


test$HabitatType <- as.factor(test$HabitatType)
test$Forest <- as.factor(test$Forest)
test$Forest<- ordered(test$Forest, levels=c('Bafog', 'Paracou', 'Kaw'))
test$Name <- as.factor(test$Name)
Model_gmin2<-lm(Gmin ~ Forest,  data = test)
autoplot(Model_gmin2)
summary(Model_gmin2)
anova(Model_gmin2) 

tukey <- HSD.test(aov(Model_gmin2), trt = 'Forest') #le TF de bafog est diff des autres !!!

stat.test.gmin2<- aov(lm(Gmin~Forest, data=test)) %>% tukey_hsd() 


#plot habitat TF 
ggboxplot(data = test,x = "Forest", y = "Gmin", fill = "Forest", color = "HabitatType") + scale_x_discrete(labels = c('1500','3000','4000')) +
  scale_fill_manual(
    values = list(
      Bafog = "#eb4934",
      Paracou = "#d9c40d",
      Kaw = "#0dc4d9"
    )) + 
  scale_colour_manual(
    values = list(
      TFGeneralist = "#141313",
      TFTF = "#ff0000" 
      
    )) +
 labs(title = "Terra firme accross precipitation gradient", x = "Annual Precipitation (mm.an-1)", y = "Minimal conductance (mmol.m-2.s-1)", 
 fill = "Precipitation", color = "Habitat preference") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 10)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.gmin2, label = "p.adj.signif",
                       y.position = c(4,3.5), hide.ns = TRUE)
                 
#BF
test2 <- Metradica %>% filter(Habitat == 'BF')


test2$HabitatType <- as.factor(test2$HabitatType)
test2$Forest <- as.factor(test2$Forest)
test2$Forest<- ordered(test2$Forest, levels=c('Bafog', 'Paracou', 'Kaw'))
test2$Name <- as.factor(test2$Name)
Model_gmin3<-lm(Gmin ~ Forest,  data = test2)
autoplot(Model_gmin3)
summary(Model_gmin3)
anova(Model_gmin3) 

tukey <- HSD.test(aov(Model_gmin3), trt = 'Forest') #le TF de bafog est diff des autres !!!

stat.test.gmin3<- aov(lm(Gmin~Forest, data=test2)) %>% tukey_hsd() 


#plot habitat TF 
ggboxplot(data = test2,x = "Forest", y = "Gmin", fill = "Forest", color = "HabitatType") + scale_x_discrete(labels = c('1500','3000','4000')) +
  scale_fill_manual(
    values = list(
      Bafog = "#eb4934",
      Paracou = "#d9c40d",
      Kaw = "#0dc4d9"
    )) + 
  scale_colour_manual(
    values = list(
      BFGeneralist = "#141313",
      BFBF = "#ff0000" 
      
    )) +
 labs(title = "SFF across precipiation gradient", x = "Annual precipitation (mm.an-1)", y = "Minimal conductance (mmol.m-2.s-1)", 
 fill = "Precipitation", color = "Habitat preference") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 10)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.gmin2, label = "p.adj.signif",
                       y.position = c(4,3.5), hide.ns = TRUE)

# trait across precipitation gradient

test <- Metradica %>% filter(Habitat == 'TF')


test$HabitatType <- as.factor(test$HabitatType)
test$Forest <- as.factor(test$Forest)
test$Forest<- ordered(test$Forest, levels=c('Bafog', 'Paracou', 'Kaw'))
test$Name <- as.factor(test$Name)
Model_TLP2<-lm(TLP ~ Forest,  data = test)
autoplot(Model_TLP2)
summary(Model_TLP2)
anova(Model_TLP2) 

tukey <- HSD.test(aov(Model_TLP2), trt = 'Forest') #le TF de bafog est diff des autres !!!

stat.test.TLP2<- aov(lm(TLP~Forest, data=test)) %>% tukey_hsd() 


#plot habitat TF 
ggboxplot(data = test,x = "Forest", y = "TLP", fill = "Forest", color = "HabitatType") + scale_x_discrete(labels = c('1500','3000','4000')) +
  scale_fill_manual(
    values = list(
      Bafog = "#eb4934",
      Paracou = "#d9c40d",
      Kaw = "#0dc4d9"
    )) + 
  scale_colour_manual(
    values = list(
      TFGeneralist = "#141313",
      TFTF = "#ff0000" 
      
    )) +
 labs(title = "Terra firme accross precipitation gradient", x = "Annual Precipitation (mm.an-1)", y = "Turgor loss point (MPa)", 
 fill = "Precipitation", color = "Habitat preference") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 10)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.TLP2, label = "p.adj.signif",
                       y.position = c(0), hide.ns = TRUE)
                 
#BF
test2 <- Metradica %>% filter(Habitat == 'BF')


test2$HabitatType <- as.factor(test2$HabitatType)
test2$Forest <- as.factor(test2$Forest)
test2$Forest<- ordered(test2$Forest, levels=c('Bafog', 'Paracou', 'Kaw'))
test2$Name <- as.factor(test2$Name)
Model_TLP3<-lm(TLP ~ Forest,  data = test2)
autoplot(Model_TLP3)
summary(Model_TLP3)
anova(Model_TLP3) 

tukey <- HSD.test(aov(Model_TLP3), trt = 'Forest') #le TF de bafog est diff des autres !!!

stat.test.TLP3<- aov(lm(TLP~Forest, data=test2)) %>% tukey_hsd() 


#plot habitat BF 
ggboxplot(data = test2,x = "Forest", y = "TLP", fill = "Forest", color = "HabitatType") + scale_x_discrete(labels = c('1500','3000','4000')) +
  scale_fill_manual(
    values = list(
      Bafog = "#eb4934",
      Paracou = "#d9c40d",
      Kaw = "#0dc4d9"
    )) + 
  scale_colour_manual(
    values = list(
      BFGeneralist = "#141313",
      BFBF = "#ff0000" 
      
    )) +
 labs(title = "SFF across precipiation gradient", x = "Annual precipitation (mm.an-1)", y = "Turgor loss point (MPa)", 
 fill = "Precipitation", color = "Habitat preference") +
 theme_minimal() +
 theme(plot.subtitle = element_text(size = 19L), 
 plot.caption = element_text(size = 10), axis.title.y = element_text(size = 10), axis.title.x = element_text(size = 10)) + theme(axis.title = element_text(size = 10))  + 
  stat_pvalue_manual(stat.test.TLP2, label = "p.adj.signif",
                       y.position = c(0), hide.ns = TRUE)

```

```

