---
title: "SupplementaryMaterials"
author: "Marion Boisseaux"
date: "2023-03-31"
output: html_document
---

# Supporting Information

Article title: The importance of local habitat in shaping functional tropical tree species’ strategies.

Authors: Marion Boisseaux1*, Daniela  Krebber1,2, Christopher Baraloto7, Benoit Burban1, Angela Casado-Garcia3, Jocelyn Cazal1, Jeanne Clément2, Géraldine Derroire1, Claire Fortunel2 Jean-Yves Goret1, Jonathan Heras3, Gaelle JaouenORCID=0000-0002-5655-904411, Isabelle Maréchaux2, Christine Scoffoni4, Ghislain Vieilledent2, Jason Vleminckx5, Sabrina Coste1, Heidy Schimann6, Clément Stahl1.


```{r libraries_SI}
library(tidyverse)
library(ggfortify)
library(factoextra)
library(FactoMineR) #for PCAs
library(kableExtra) #for tables
library(V.PhyloMaker) #phylogeny
library(ggtree) #tree vizualisation and annotation
library(readxl)
library(gridExtra)
library(rio)
library(dplyr)
library(tidyr)
library(janitor)
library(forcats)
library(ggplot2)
library(corrplot) #correlation
library("Hmisc") #for the significance for the correlation
library(magick) #for images
library(vegan) #for permanova
library(pairwiseAdonis) #for pairwise comparaison after permanova
```


#Figures

##Figure S1: The 21 selected species’ phylogeny.

```{r Figure S1, echo=FALSE, message=FALSE, warning=FALSE}

#select focal species
species <- data.frame(taxon = c(
  "Eperua_falcata", 
  "Iryanthera_hostmannii", 
  "Jacaranda_copaia subsp. copaia",
  "Pterocarpus_officinalis",
  "Symphonia_globulifera",
  "Tachigali_melinonii",
  "Virola_surinamensis", 
  "Bocoa_prouacensis",
  "Conceveiba_guianensis",
  "Eschweilera_coriacea",
  "Hymenopus_heteromorphus",
  "Protium_stevensonii",
  "Virola_michelii",
  "Carapa_surinamensis",
  "Laetia_procera",
  "Protium_opacum subsp. rabelianum",
  "Dicorynia_guianensis",
  "Gustavia_hexapetala",
  "Iryanthera_sagotiana",
  "Licania_membranacea",
  "Poraqueiba_guianensis"
))%>% separate(taxon, c("Genus", "Species"), sep = "_", remove = F)

species <- dplyr::select(species, taxon , Genus, Species)

#Use paracou database 30/08/2021 as the backbone phylogeny
paracou <- read_excel("../Metradica_Paracou/Document/Paracou_database20210830.xlsx") %>% 
  dplyr::select(Family, Genus, Species) %>% 
  unique() %>% 
  full_join(species) %>% 
  mutate(species = paste(Genus, Species), genus = Genus, family = Family) %>% 
  dplyr::select(species, genus, family, taxon) %>% 
  mutate(taxon = as.character(taxon))

#This function makes phylogenetic hypotheses for the focal species under three scenarios based on paracou database 30/08/2021. I use the default senario.
tree <- phylo.maker(sp.list = paracou, tree = GBOTB.extended, nodes = nodes.info.1, scenarios = "S3")

#remove "#" for the next two lines when running for the first time, to save and reload the phylogeny.

#save(tree, file = "./Results/phylogeny_subset.Rdata")
#load("./Results/phylogeny_subset.Rdata")

#build tree and visualize it
A<- fortify(tree$scenario.3) %>% 
  mutate(species = gsub("_", " ", label)) %>% 
  left_join(paracou) %>% 
  ggtree(aes(col = taxon), layout="circular") + 
  geom_tiplab2(aes(alpha = !is.na(taxon), size = !is.na(taxon))) +
  theme_tree(legend.position='bottom', legend.text = element_text(face = "italic")) +
  scale_alpha_manual("taxon", values = c(0.2, 4)) +
  scale_size_manual("taxon", values = c(1, 4))

#save and choose saving format
ggsave(file="phylo_subset.svg", plot=A, width=15, height=10)
ggsave(file="phylo_subset.jpg", plot=A, width=15, height=10)
```

##Figure S2: Discrimination of the habitats using the topographic wetness index.

```{r Figure S2}
Data <- read.csv("Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv")
Data$Forest <- as.factor(Data$Forest)
Data$Habitat <- dplyr::recode(Data$Habitat, BF='Seasonally flooded', TF= 'Terra Firme')

TWI_plot <- Data %>%
mutate(Forest = fct_relevel(Forest, 
            "Bafog", "Paracou", "Kaw")) %>%
ggplot() +
aes(x = Forest, y = log(TWI), fill = Habitat) +
geom_boxplot() +
scale_fill_manual(
    values = c(`Seasonally flooded` = "#56B4E9",
    `Terra Firme` = "#E79F02")
                  ) +
ylab("Topographic wetness index")+
theme_minimal()+
theme(text = element_text(size = 16))     

ggsave(filename = "TWI in habitats.png", plot = TWI_plot, bg = "white", width = 10, height = 8, dpi = 600)
```

##Figure S3. Indval values for the studied species. 

We explored the degree of habitat preference using **Indicator Species Analysis** (Dufrene & Legendre 1997). It takes account of both relative abundance and relative frequencies of each species across the two main habitats in French Guiana, seasonally flooded forest and Terra firme forests.

*Out of the 654 species identified from Baraloto et al 2021, we only considered 5 % highest IndVals to qualify them as specialists of a habitat. This corresponded to a threshold of IndVal ≥  0.2 for SF specialists and IndVal ≥  0.2598  for TF specialists. Those with an equal or lower IndVal in both habitats were considered without any preference and therefore called generalists.*

```{r Indval}
#Supplementary data from the Baraloto et al 2021.

indval_baraloto <- readxl::read_xlsx("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/Divers/Species_choice_Indval/Indval_Peru_&_FG.xlsx")

indval_baraloto <- indval_baraloto %>% select(...8, ...9, ...10, ...11, ...12, ...13)

indval_FG <- indval_baraloto[-(1:4),-5]

indval_FG <- janitor::row_to_names(indval_FG, 1)

probs <- c(0.95)
quantiles_SF <- quantile(as.numeric(indval_FG$SF), prob=probs) # Top 5% highest values for SF specialists : indval >= 0.2 
#95% 
#0.2 
quantiles_TF <- quantile(as.numeric(indval_FG$TF), prob=probs) 
#   95% 
# 0.2598 

indval_FG$SF<- as.numeric(indval_FG$SF)
indval_FG$TF<- as.numeric(indval_FG$TF)

#SF data 
Data_SF<- indval_FG %>%
  select(Species, Abund, SF, TF, `P-value`) %>%
  filter(SF >= 0.2) %>%
  rename(Indval_SF =SF, Indval_TF =TF)

#TF data
Data_TF<- indval_FG %>%
  select(Species, Abund,SF, TF, `P-value`) %>%
  filter(TF >= 0.2598)%>%
  rename(Indval_SF =SF, Indval_TF =TF)
```

Our analysis identified 9 generalist taxa, 8 SFF specialist taxa and 7 terra firme specialist taxa.

```{r Species within indval threshold}

species <- data.frame(Species = c("Eperua_falcata", 
  "Iryanthera_hostmannii", 
  "Jacaranda_copaia", # subsp. copaia
  "Pterocarpus_officinalis",
  "Symphonia_globulifera",
  "Tachigali_melinonii",
  "Virola_surinamensis", 
  "Bocoa_prouacensis",
  "Chrysophyllum_prieurii",
  "Conceveiba_guianensis",
  "Eschweilera_coriacea",
  "Hymenopus_heteromorphus",
  "Protium_stevensonii",
  "Virola_michelii", 
  "Carapa_surinamensis", 
  "Laetia_procera",
  "Protium_opacum", #subsp. rabelianum
  "Dicorynia_guianensis",
  "Gustavia_hexapetala",
  "Iryanthera_sagotiana",
  "Licania_membranacea",
  "Poraqueiba_guianensis"
  ))
  

Specialist_SF <- left_join(species, Data_SF) %>% na.omit()

Specialist_TF <- left_join(identified_species, Data_TF) %>% na.omit()

Generalist_high_indval_both_habitats <- inner_join(Specialist_SF, Specialist_TF )


Specialist_TF <- Specialist_TF %>% 
  filter(Species != "Conceveiba_guianensis") %>% #con.gui in both, removed it
  mutate(Type = "TF specialist")
Specialist_SF <- Specialist_SF %>% 
  filter(Species != "Conceveiba_guianensis") %>%#con.gui in both, removed it
   mutate(Type = "SF specialist")

#indval graphs

#SF specialists
indval_SF_plot <- Specialist_SF  %>%
  mutate(Species = fct_reorder(Species, Indval_SF)) %>% 
  ggplot(aes(x = Species, y = Indval_SF, fill = Species)) +
  geom_col() +
  scale_fill_brewer(palette = "YlGnBu", direction = 1) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x=element_text(angle=40, hjust = 1))+
  theme(legend.position="none", axis.title.x = element_blank())

#TF specialists
indval_TF_plot<- Specialist_TF  %>%
  mutate(Species = fct_reorder(Species, Indval_TF)) %>% 
  ggplot(aes(x = Species, y = Indval_TF, fill = Species)) +
  geom_col() +
  scale_fill_brewer(palette = "YlOrRd", direction = 1) +
  theme_minimal(base_size = 12) +
  theme(axis.text.x=element_text(angle=40, hjust = 1))+
  theme(legend.position="none", axis.title.x = element_blank())

#Generalists
Generalist <- left_join(identified_species, indval_FG) 
Generalist <- Generalist %>% rename(Indval_SF = SF, Indval_TF = TF)
Generalist <-  Generalist %>%
  na.omit() %>%
  filter(Indval_TF <= 0.2598) %>%
  filter(Indval_SF <= 0.2)

#casearia too high in one habitat to consider it a generalist!
Generalist <- Generalist %>% 
  filter(Species != "Casearia_javitensis") %>%
  filter(Abund != 5) 


Generalist_all  <-rbind(Generalist, Generalist_fort_indval_deux_habitats)
Generalist_all <- Generalist_all %>% 
  mutate(Diff_Indval = abs(Indval_SF-Indval_TF)) %>%
  mutate(Type = "Generalist")

Generalist_diff_indval<- ggplot(Generalist_all) +
   aes(x = Species, y = Diff_Indval, fill = Species) +
   geom_col() +
   scale_fill_brewer(palette = "RdYlBu", direction = 1) +
   theme_minimal(base_size = 12) +#les couleurs en faveur des BF, tacmel proche d'un SF spe donc couleur bleu
  theme(axis.text.x=element_text(angle=40, hjust = 1))+
  theme(legend.position="none")

group_figure <- ggpubr::ggarrange(
  indval_TF_plot + theme(legend.position="none"),
  indval_SF_plot + theme(legend.position="none"),
  Generalist_diff_indval + theme(legend.position="none"),
  labels = c("A", "B", "C"),
  nrow= 3, ncol=1)
ggsave(file="indval.svg", plot=group_figure, width=10, height=12)
ggsave(file="indval.png", plot=group_figure, width=10, height=12)

```

##Figure S4: Variation of leaf trait values among species. 

No imputation, not transformed. Visualizing raw trait variation.

```{r Figure S4}

Metradica <- read.csv("C://Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/ALL/Final_Metradica_OUT_30112022.csv") %>% 
  dplyr::select(Code, Genus, Species, Name, Habitat, Type, Forest, Plot, Gmin, TLP, LSWC, MajVLA, Nitrogen, Carbon, Phosphorous, Potassium, SD, TWI, DBH) %>%
  rename(K= Potassium,
         P = Phosphorous,
         C = Carbon, 
         N= Nitrogen)

sub_data_TF <- Metradica %>%
  filter(Name %in% c("Dicorynia_guianensis", "Iryanthera_sagotiana", "Gustavia_hexapetala", "Licania_membranacea", "Poraqueiba_guianensis", "Virola_michelii")) %>% filter(Habitat == "TF")

sub_data_SF <- Metradica %>%
  filter(Name %in% c("Eschweilera_coriacea","Eperua_falcata", "Iryanthera_hostmannii", "Laetia_procera", "Protium_opacum subsp. rabelianum", "Pterocarpus_officinalis", "Symphonia_globulifera", "Virola_surinamensis", "Carapa_surinamensis")) %>% filter(Habitat == "BF")

sub_data_G <-  Metradica %>%
  filter(Name %in% c("Bocoa_prouacensis", "Conceveiba_guianensis", "Jacaranda_copaia subsp. copaia", "Hymenopus_heteromorphus", "Protium_stevensonii", "Tachigali_melinonii"))

sub_data <- bind_rows(sub_data_TF, sub_data_SF, sub_data_G)

sub_data <- sub_data %>% mutate(Type= ifelse(Name == 'Virola_michelii','TF',Type))

sub_data <- sub_data %>% mutate(Type= ifelse(Name == 'Eschweilera_coriacea','BF',Type))

Metradica <- sub_data

data <- Metradica %>%
  dplyr::select(Name, Type, Gmin, TLP, LSWC, MajVLA, N, C, P, K, SD) %>% 
  reshape2::melt(c("Name", "Type"), variable.name = "Trait")

data$Type <- factor(data$Type, levels = c("BF", "TF", "Generalist")) 

p <-  data %>%
  mutate(Trait = as.character(Trait)) %>% 
  mutate(Trait = dplyr::recode(Trait, "Gmin" = "g[min]~(mmol%.%m^{-2}%.%s^{-1})", "TLP" = "pi[tlp]~(MPa)", "C"= "C~('%')", "N" = "N~('%')", "K"= "K~(g%.%kg^{-1})", "LSWC" = "LSWC~('%')", "MajVLA" = "MajVLA~(mm%.%mm^{-2})", "P" = "P~(g%.%kg^{-1})", "SD" = "SD~(mm^{-2})")) %>% 
  left_join(dplyr::select(data, Type, Name) %>%
              unique() %>%
              arrange(Type, Name) %>%
              mutate(order_graph = 1:n())) %>%
  mutate(Name = gsub("_", " ", Name)) %>% 
  separate(Name, c("genus", "species")) %>% 
  mutate(Name = paste0(str_sub(genus, 1, 1), ". ", species)) %>% 
  ggplot(aes(x = reorder(Name, order_graph), y= value)) +
  geom_boxplot(aes(fill = Type),
  #              alpha = 0.5, col = "lightgrey") +
  #geom_violin(aes(fill = Type),
               alpha = 0.5, col = "lightgrey") +
  scale_fill_manual(name = "Species preference", 
                    values = c("TF" = "#E79F02", #orange for TF
                                "BF" =  "#56B4E9", #blue for SF
                                "Generalist" = "#009E72"),  #green for Generalists
                    labels = c("TF" = "TF specialist",
                               "Generalist" = "Generalist", 
                               "BF" = "SF specialist")) +
  facet_wrap(~ Trait, scales = "free_x", label = label_parsed) +
  theme_minimal() +
  coord_flip() +
  theme(axis.text.y = element_text(face = "italic"), axis.title = element_blank(),legend.position = "bottom") 

#ggsave(filename = "Trait Distribution.png", plot = p, bg = "white", width = 10, height = 8, dpi = 600)
```

##Figure S5: Trait contributions to first four principal component axes among leaf traits. 

PCA with log-transformed traits, that were imputed but without stomata.

```{r Figure S5}
Data <- read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") %>% 
  dplyr::select(-Code, -Genus, -Species, Habitat, Type, -SD) %>%
  rename(Potassium = K, 
         Phosphorous = P, 
         Nitrogen = N,
         Carbon = C) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium"), log) %>% 
  mutate(TLP = -TLP)

Data$Type <- dplyr::recode(Data$Type, BF='SF Specialist', TF= 'TF Specialist')
Data <- Data %>% na.omit()

#PCA without stomata
res.pca <- PCA(Data %>% dplyr::select(-Plot, -Forest, -Name, -Type, -Habitat, -TWI, -DBH), graph = FALSE)

#Eigenvalues
eig.val <- get_eigenvalue(res.pca)
eig.val
fviz_eig(res.pca, addlabels = TRUE, ylim = c(0, 50))

#Contributions of variables to PC1
axe1 <- fviz_contrib(res.pca, choice = "var", axes = 1, top = 10)

#Contributions of variables to PC2
axe2 <- fviz_contrib(res.pca, choice = "var", axes = 2, top = 10)

#Contributions of variables to PC3
axe3 <- fviz_contrib(res.pca, choice = "var", axes = 3, top = 10)

#Contributions of variables to PC4
axe4 <- fviz_contrib(res.pca, choice = "var", axes = 4, top = 10)

#arrange into one figure
axes_constribution <- ggpubr::ggarrange(
  axe1,
  axe2,
  axe3,
  axe4,
  labels = c("A", "B", "C"),
  common.legend = T,
  legend = 'none',
  nrow= 2, ncol=2)

ggsave(filename = "axes_contribution.png", plot = axes_constribution, bg = "white", width = 10, height = 10, dpi = 600)
```

##Figure S6: Spearman correlation coefficients among leaf traits. 

```{r Figure S6}
Data <- read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") %>% 
  dplyr::select(-Code, -Genus, -Species, Habitat, Type, -SD) %>%
  rename(Potassium = K, 
         Phosphorous = P, 
         Nitrogen = N,
         Carbon = C) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium"), log) %>% 
  mutate(TLP = -TLP)

traits <- Data %>% 
  rename(`  K` = Potassium, 
         `  P` = Phosphorous, 
         `  N` = Nitrogen,
         `  C` = Carbon,
         gmin = Gmin) %>% 
  dplyr::select(-Name, -Habitat, -Type, -Forest, -Plot, -TWI, -DBH) 

#to add significance
testRes = cor.mtest(traits, conf.level = 0.95)

#image output, have to run until last live dev.off() for it to work.
png(height=500, width=500, file="mycorr_noTWI_noSD_imputed.png", type = "cairo")

#create correlation matrix
cor_matrix <- traits %>%
  na.omit() %>%
  cor(method = "spearman")

#correlation plot with no rows and column labels and without colors in the diagonal
corrplot(cor_matrix, p.mat = testRes$p, method = 'circle',  #addCoef.col ='black', insig='blank',
         sig.level = 0.10, addrect = 2, diag = FALSE, tl.pos = FALSE)

# Add labels to the diagonal
text(rev(1:nrow(cor_matrix)), 1:nrow(cor_matrix), rev(colnames(cor_matrix)), 
     cex = 1.5, pos = 4, offset = -1.5, col= "red", ifelse(is.na(diag(cor_matrix)), NA, 1))

dev.off()

```

##Figure S7: Correlation between stomatal density and minimal leaf conductance. 

Leaf traits are ln-transformed. The adjusted R squared is equal to 0.011. 

```{r Figure S7}

Data <- read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_not_imputed/Subset.csv")
#SD and gmin

p <- ggplot(Data) +
  aes(x = log(SD), y = log(Gmin)) +
  geom_point(shape = "circle", size = 1.5, colour = "#112446") +
  geom_smooth(method = "lm") +
  theme_minimal(base_size = 22)
library(jtools)
model <- lm(log(SD) ~ log(Gmin), data = Data)
A <- get_formula(model)
```

#Tables

##Table S1. Sampling sites supplementary information. 

```{r Table S1 }

#get authorization 
googlesheets4::gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets.readonly" )

#googlesheet
Plot_table <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1XoQH2pg5bcuvFzSdmY4v_lC-D_u9LMye4RTiJU4XRmg/edit#gid=0")

Plot_table <- Plot_table %>% 
  dplyr::select(-PlotName, -Xutm, -Yutm, -Localization)
  
Plot_table %>%
  kbl(caption = "Summary of sampling site information", escape = FALSE, digits = 2) %>%
  row_spec(0, bold = TRUE) %>% 
  kable_classic(full_width = F, html_font = "Cambria") %>%
  save_kable(file = "../Tables_SI/Plot_info_summary.png", zoom = 5)
```

##Table S2. Individuals per species collected in the three sampling sites. 

```{r Table S2}

#get authorization 
googlesheets4::gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets.readonly" )

Family <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1XoQH2pg5bcuvFzSdmY4v_lC-D_u9LMye4RTiJU4XRmg/edit#gid=122243583", sheet = "Species_SI") %>% select(Family, Genus, Species)

#Marion's computer path METRADICA/Divers/Species_choice_Indval/Metradica_species_subset_total.csv
#campaign subset data
#data added to drive for co-authors
Data <- read.csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") 

Paracou <- Data %>% 
  filter(Forest == "Paracou") %>%
  group_by(Name) %>%
  summarise(Paracou = n())

Bafog <- Data %>% 
  filter(Forest == "Bafog") %>%
  group_by(Name) %>%
  summarise(Bafog = n())

Kaw <- Data %>% 
  filter(Forest == "Kaw") %>%
  group_by(Name) %>%
  summarise(Kaw = n())

Paracou <- left_join(Paracou, Bafog)

Totaux_table <- left_join(Paracou, Kaw)

Data <- Data %>% dplyr::select(Genus, Species, Name) %>%unique()

Data <-   left_join(Totaux_table, Data)%>%
  relocate(Genus, .before =Name) %>%
  relocate(Species, .after = Genus)

Totaux_table <- left_join(Data, Family)

Totaux_table <- Totaux_table %>%
  select(-Name) %>%
  relocate(Family, .before="Genus") %>%
  adorn_totals("row")


Totaux_table <- Totaux_table %>%
  replace(is.na(.), 0) %>%
  mutate(Total = rowSums(select(., -Family, -Genus, -Species)))

options(knitr.kable.NA = '') #replace NA by blank spaces in table

Totaux_table %>%
  kbl(caption = "Individuals per species collected on the 3 sites") %>% 
  kable_classic(full_width = F, html_font = "Cambria") %>%
  column_spec(2:3, italic = T) %>%
  row_spec(0, bold= T) %>%
  row_spec(22, background = "#666;", color = "white") %>%
  column_spec(7,  background = "#666;", color = "white" ) %>%
save_kable(file = "../METRADICAproject/Results/Tables_SI/Sampling_subset.png")

```

##Table S3: Species chosen for the study according to the Indicator values (Indval) within each habitat in French Guiana. 

```{r Table S3}

#get authorization
googlesheets4::gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets.readonly" )

#indval data 
Indval <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1XoQH2pg5bcuvFzSdmY4v_lC-D_u9LMye4RTiJU4XRmg/edit#gid=122243583", sheet = "Species_SI") %>% select(-Paracou, -Bafog, -Kaw)

Indval <- with(Indval, Indval[order(Type) , ]) #ordering per type

options(knitr.kable.NA = '') #replace NA by blank spaces in table

Indval %>%
  kbl() %>%
  row_spec(0, bold = TRUE) %>% 
  column_spec(1:2, italic = TRUE) %>%
  kable_classic_2(full_width = F) %>% save_kable(file = "../METRADICAproject/Results/Tables_SI/IndVal_subset.png", zoom = 10)

```


##Table S4: Permutational Manova analysis and post-hoc pairwise analysis.

PERMANOVA, (permutational multivariate ANOVA), is a non-parametric alternative to MANOVA, or multivariate ANOVA test. It is appropriate with multiple sets of variables that do not meet the assumptions of MANOVA, namely multivariate normality.

Null hypothesis: Groups do not differ/ are equivalent in spread or position multivariate space.

```{r Table S4}
#Data
Data <- read.csv("Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") %>% 
  rename(Potassium = K, 
         Phosphorous = P, 
         Nitrogen = N,
         Carbon = C) %>% 
  relocate(SD, .after = MajVLA) %>%
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "SD", "Phosphorous","Carbon", "Nitrogen", "Potassium", "TWI"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "SD", "Phosphorous","Carbon", "Nitrogen", "Potassium", "TWI"), log) %>% 
  mutate(TLP = -TLP) 


data_PCA <- Data[, c(1:17)][,-c(1,2,3,4,5,6,7,8,13)]

adonis_type<-adonis2(data_PCA~Metradica_log$Type, permutations = 999, method = "euclidean") 
adonis_habitat<-adonis2(data_PCA~Metradica_log$Habitat, permutations = 999, method = "euclidean") 

permanova <-adonis_type %>%
  kbl(caption="Permutational Multivariate Analysis of Variance (PERMANOVA)", digits = 3, booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down", full_width = FALSE) %>%
  kable_classic(full_width = F, html_font = "Cambria") #%>%
#save_kable(file = "Permanova_type.png")

permanova <-adonis_habitat %>%
  kbl(caption="Permutational Multivariate Analysis of Variance (PERMANOVA)", digits = 3, booktabs=TRUE) %>% 
  kable_styling(latex_options="scale_down", full_width = FALSE) %>%
  kable_classic(full_width = F, html_font = "Cambria") #%>%
#save_kable(file = "Permanova_type.png")

#P-value (0.001) *** is significant so our group types have different means.

#Process a pairwise analyse to detect which treatments are different from each other.
pairwise_adonis_type <- pairwise.adonis(data_PCA,Data$Type, sim.method = "euclidean")
pairwise_adonis_type$pairs[1] <- "TF specialist vs SF specialist"
pairwise_adonis_type$pairs[2] <- "TF specialist vs generalist"
pairwise_adonis_type$pairs[3] <- "SF specialist vs generalist"
pairwise_adonis_habitat <- pairwise.adonis(data_PCA,Data$Habitat, sim.method = "euclidean") 
pairwise_adonis_habitat$pairs[1] <- "TF habitat vs SF habitat"

#Species preference
pairwise_adonis_type_table <- pairwise_adonis_type %>%
  relocate(pairs, .after = sig) %>%
  kbl(caption = "A. Species' preferences",digits =3) %>% 
  kable_classic(full_width = F, html_font = "Cambria") %>%
  save_kable(file = "A. Species' preferences.png", zoom = 5)

#Habitat of collect
pairwise_adonis_habitat_table <- pairwise_adonis_habitat %>%
  relocate(pairs, .after = sig) %>%
  kbl(caption = "B. Habitat of collect",digits =3) %>% 
  kable_classic(full_width = F, html_font = "Cambria") %>%
  save_kable(file = "B. Habitat of collect.png", zoom = 5)
```


## Table S5: Pairwise tables for the spearman correlation.

Coefficients (A) and associated p-values (B) of leaf traits for the 21 studied species (n=552).

```{r Table S5}
#same beginning of script as for the Figure S6: Spearman corerlation.
Data <- read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") %>% 
  dplyr::select(-Code, -Genus, -Species, Habitat, Type, -SD) %>%
  rename(Potassium = K, 
         Phosphorous = P, 
         Nitrogen = N,
         Carbon = C) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium"), log) %>% 
  mutate(TLP = -TLP)

traits <- Data %>% 
  rename(`  K` = Potassium, 
         `  P` = Phosphorous, 
         `  N` = Nitrogen,
         `  C` = Carbon,
         gmin = Gmin) %>% 
  dplyr::select(-Name, -Habitat, -Type, -Forest, -Plot, -TWI, -DBH) 

#to add significance
testRes = cor.mtest(traits, conf.level = 0.95)

#image output, have to run until last live dev.off() for it to work.
png(height=500, width=500, file="mycorr_noTWI_noSD_imputed.png", type = "cairo")

#create correlation matrix
cor_matrix <- traits %>%
  na.omit() %>%
  cor(method = "spearman")

#correlation plot with no rows and column labels and without colors in the diagonal
corrplot(cor_matrix, p.mat = testRes$p, method = 'circle',  #addCoef.col ='black', insig='blank',
         sig.level = 0.10, addrect = 2, diag = FALSE, tl.pos = FALSE)

# Add labels to the diagonal
text(rev(1:nrow(cor_matrix)), 1:nrow(cor_matrix), rev(colnames(cor_matrix)), 
     cex = 1.5, pos = 4, offset = -1.5, col= "red", ifelse(is.na(diag(cor_matrix)), NA, 1))

dev.off()

#significance
res <- rcorr(as.matrix(traits), type = "spearman")
res
# Extract the correlation coefficients


res$r %>%
  kbl(caption ="", digits =2)  %>%
  add_header_above(c("<span style='font-size: 20px; font-weight: bold;'>A. Pairwise table of the correlation coefficients</span>" = 9), escape = FALSE) %>%
  kable_classic(full_width = F, html_font = "Cambria")  %>%
  save_kable("corr_coef.png")
  
img <- image_read("corr_coef.png")
img_resized <- image_scale(img, "800x600")

# Save the resized image
image_write(img_resized, "corr_coef_resized.png")


# Extract p-values associated to the correlation coefficients
res$P%>%
  kbl(caption ="", digits =3)  %>%
  add_header_above(c("<span style='font-size: 20px; font-weight: bold;'>B. Pairwise table of the associated p-values</span>" = 9), escape = FALSE) %>%
  kable_classic(full_width = F, html_font = "Cambria") %>%
  save_kable("corr_pvalue.png")

img <- image_read("corr_pvalue.png")
img_resized <- image_scale(img, "800x600")

# Save the resized image
image_write(img_resized, "corr_pvalue_resized.png")


```

## Table S6: Model summary for each trait from equation 1.

```{r Table 6}
#library used
library(nlme) #to fit the model and do the variance partitioning with ML method
library(lme4) #for the VarCorr function
library(dplyr) #to pipe
library(ggplot2) #to plot
library(kableExtra) #to build nice tables

#data used (log on all traits)
Data <- read.csv("Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") %>% 
  rename(Carbon = C,
         Nitrogen = N,
         Potassium = K, 
         Phosphorous = P) %>% 
  relocate(SD, .after = MajVLA) %>%
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "SD", "Carbon", "Nitrogen", "Phosphorous", "Potassium", "TWI"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "SD",  "Carbon", "Nitrogen", "Phosphorous", "Potassium", "TWI"), log) %>% 
  mutate(TLP = -TLP)

Data$Forest <- as.factor(Data$Forest)

#function for extracting the coefficient of the model
model_coef_table <- function(Trait, Mydata){

  #Rename the trait column
  colnames(Mydata)[which(colnames(Mydata) == Trait)] <- "Trait"  
  
  # Fit the linear mixed-effects model
  model <- nlme::lme(Trait ~ TWI + Forest,  random=~1|Name, data = Mydata, na.action = na.omit, method = "ML")
  
  # build coef table 
  coef_table <- coef(summary(model))
  coef_table <- as.data.frame(coef_table)
  
  return(coef_table)
}


# For all traits call model_coef_table function
coef_tables <- list()

for (i in colnames(Data)[9:17]){

  coef_tables[[i]] <- model_coef_table(i, Data)
}

# Combine all coefficient tables into one data frame
coef_table <- do.call(rbind, coef_tables)


# create nice table
coef_table %>%
  kbl(caption = "", escape = FALSE, digits = 3) %>%
  row_spec(0, bold = TRUE) %>% 
  kable_classic(full_width = F, html_font = "Cambria") %>%
  save_kable(file = "../Tables_SI/Model_summaries.png", zoom = 5)
```

