---
title: "PCA_MFA"
author: "Marion Boisseaux"
date: "08/09/2022"
output: html_document
---
# Libraries

```{r librairies_results}
library(tidyverse)
library(ggfortify)
library(dplyr)
library(factoextra)
library(FactoMineR)
library(Factoshiny)
library(corrplot) 
library(ggpubr)
library(ggfortify)
library(agricolae)
library(rstatix)
library(kableExtra)
library(V.PhyloMaker)
library(ggfortify)
library(ggtree)
library(readxl)
library(lme4)
library(ggeffects) #draw plots of models
library(nlme)
library(sjPlot) #for plotting lmer and glmer mods
library(gridExtra)
library(rio)
library(vegan)
```

# Data

```{r Data_results, message=FALSE, warning=FALSE}

# data

library(dplyr)
Metradica_log <- read.csv("C://Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/Metradica_trait_OUT.csv") %>% 
  dplyr::select(Code, Genus, Species, Name, Habitat, Type, Forest, Gmin, TLP, LSWC, MajVLA, Nitrogen, Carbon, Phosphorous, Potassium, SD) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium", "SD"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium", "SD"), log) %>% 
  mutate(TLP = -TLP) 

sub_data_TF <- Metradica_log %>%
  filter(Name %in% c("Dicorynia_guianensis", "Iryanthera_sagotiana", "Gustavia_hexapetala", "Licania_membranacea", "Poraqueiba_guianensis", "Virola_michelii"))

sub_data_SF <- Metradica_log %>%
  filter(Name %in% c("Eschweilera_coriacea","Eperua_falcata", "Iryanthera_hostmannii", "Laetia_procera", "Protium_opacum subsp. rabelianum", "Pterocarpus_officinalis", "Symphonia_globulifera", "Virola_surinamensis", "Carapa_surinamensis"))

sub_data_G <-  Metradica_log %>%
  filter(Name %in% c("Bocoa_prouacensis", "Conceveiba_guianensis", "Jacaranda_copaia subsp. copaia", "Hymenopus_heteromorphus", "Protium_stevensonii", "Tachigali_melinonii"))

sub_data <- bind_rows(sub_data_TF, sub_data_SF, sub_data_G)

Metradica <- sub_data

Metradica$Type <- as.character(Metradica$Type)
Metradica$Name <- as.character(Metradica$Name)
Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Virola_michelii','TF',Type))

Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Eschweilera_coriacea','BF',Type))


write.csv(Metradica, "METRADICA_subset.csv")



```

#exploring na
```{r}

#check the nas
pMiss <- function(x){sum(is.na(x))/length(x)*100}
apply(Metradica,2,pMiss)

#we see that SD is almost 30% missing values, the rest is below a threshold of 5%
library(VIM)
aggr_plot <- aggr(Metradica, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, labels=names(Metradica), cex.axis=.7, gap=3, ylab=c("Histogram of missing data","Pattern"))
```


# MFA 

I log-transformed the data to reduce the skewness but checking the normality using shapiro's test was significative (not following normality).

I have variables from different groups:

-Categorical groups : Name of species *Name*; Habitat of collect *habitat*; specialist or generalist behavior *Type*; specifying which type of specialist and where it was collected for the geenralists *HabitatType*; the forest where is was sampled *Forest*

-water related traits: *Gmin*, *TLP*, *LSWC*, *MajVLA*, *SD*
-Chemistry: *Potassium*, *Phosphorous*, *Carbon*, *Nitrogen*
-Tree characteristics: *DBH* , **Dawkins** ?
-Habitat characterization : *TWI*, **CWD**?

```{r}

Data <- Metradica %>% dplyr::select(-Code, -Genus, -Species, -Habitat, -Type) %>% relocate(LSWC, .after = TLP) %>%  relocate(MajVLA, .after = LSWC)


res = MFA(Data, group=c(3,4,4,4,1), type=c("n",rep("s",4)), name.group=c("Identity","Water_related","Carbon_related","Leaf_chemistry", "DBH"), num.group.sup=c(1,5))

fviz_screeplot(res)
fviz_mfa_var(res, "group")

#Metradica_log: the data set used
#group: a vector indicating the number of variables in each group
#type: the type of the variables in each group. "s" for scaled continuous variables, "c" for centered (unscaled) continuous variables and "n" for categorical variables
#ncp: number of dimensions kept in the result
#name.group: names of the groups
#num.group.sup: indexes of the supplementary groups

#red color = active groups of variables
#green color = supplementary groups of variables

# Contribution to the first dimension
fviz_contrib(res, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res, "group", axes = 2)

quanti.var <- get_mfa_var(res, "quanti.var")
quanti.var 

fviz_mfa_var(res, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

# Coordinates
head(quanti.var$coord)
# Cos2: quality on the factore map
head(quanti.var$cos2)
# Contributions to the dimensions
head(quanti.var$contrib)

# Contributions to dimension 1
fviz_contrib(res, choice = "quanti.var", axes = 1, top = 20, col.var= "group", color= "white" ) +  scale_fill_manual("Groups", values = c("#dec33c", "#5bb349", "#1e81b0"))

# Contributions to dimension 2
fviz_contrib(res, choice = "quanti.var", axes = 2, top = 20, col.var= "group", color= "white" ) +  scale_fill_manual("Groups", values = c("#dec33c", "#5bb349", "#1e81b0"))

# Contributions to dimension 3
fviz_contrib(res, choice = "quanti.var", axes = 3, top = 20, col.var= "group", color= "white" ) +  scale_fill_manual("Groups", values = c("#dec33c", "#5bb349", "#1e81b0"))

# axe 2 et 3
fviz_mfa_var(res, "quanti.var", palette = "jco", axes= c(2,3), 
             col.var.sup = "violet", repel = TRUE)

# Color by cos2 values: quality on the factor map
fviz_mfa_var(res, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             col.var.sup = "violet", repel = TRUE)

#create a bar plot of variables cos2
fviz_cos2(res, choice = "quanti.var", axes = 1)

#for individuals
ind <- get_mfa_ind(res)
ind

fviz_mfa_ind(res, quali.var="Name", label="non", #remove points labelling
             palette = "jco",
             repel = TRUE)

fviz_mfa_ind(res, 
             habillage = "HabitatType", # color by groups 
             palette = c("#00AFBB", #BFBF
                         "#03fc56",#GBF
                         "#fcba03", #GTF
                         "#fc4e03"), #TFTF
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE, # Avoid text overlapping
             label="none") 

fviz_ellipses(res, c("Name", "HabitatType"), repel = TRUE, label= "none")

#to remove individuals add : invisible = c("ind","ind.sup")

#ellipses
#"Character specifying frame type. Possible values are "convex", "confidence" or types supported by stat_ellipse() including one of c("t", "norm", "euclid") for plotting concentration ellipses.

#"convex": plot convex hull of a set o points.

#"confidence": plot confidence ellipses arround group mean points as coord.ellipse()[in FactoMineR].

#"t": assumes a multivariate t-distribution.

#"norm": assumes a multivariate normal distribution.

#"euclid": draws a circle with the radius equal to level, representing the euclidean distance from the center. This ellipse probably won't appear circular unless coord_fixed() is applied.#
```

#PCA

##data PCA
```{r}
#data with stomata

data_withNA <- read.csv("Dataset/METRADICA_subset.csv") %>% dplyr::select(-X) # 596 indv

data_without_NA <- read.csv("Dataset/METRADICA_subset.csv") %>% dplyr::select(-X) #379 indv %>%na.omit()

#data withOUT stomata
data_withNA_no_stomata <- read.csv("Dataset/METRADICA_subset.csv") %>% dplyr::select(-X, -SD) # 596

data_withOUTNA_no_stomata <- read.csv("Dataset/METRADICA_subset.csv") %>% dplyr::select(-X, -SD) %>% na.omit() #537 indv

# Contribution to the first dimension
fviz_contrib(res, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res, "group", axes = 2)

quanti.var <- get_mfa_var(res, "quanti.var")
quanti.var 

fviz_mfa_var(res, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)


```

#no trait imputation

##PCA without stomata

```{r}
data <-data_withOUTNA_no_stomata  %>% dplyr::select(-Code, -Genus, -Species, Habitat, Type) 

data$Type <- recode(data$Type, BF='SF Specialist', TF= 'TF Specialist')
#data <- mutate(data, Type = recode(Type, "BF" = "SF specialist")) #other way to do it

# v2
 
g_nostomata <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
 #scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

ggsave(filename = "PCA_full_HabitatPref_noSD.png", plot = g_nostomata, bg = "white", width = 8, height = 8, dpi = 600)
```



##PCA with stomata

```{r}
Data <- Metradica %>% dplyr::select(-Code, -Genus, -Species, Habitat, Type) 



# data
data <- Data %>% na.omit()

data$Type <- recode(data$Type, BF='SF Specialist', TF= 'TF Specialist')
#data <- mutate(data, Type = recode(Type, "BF" = "SF specialist")) #other way to do it

# v0
res.PCA <- FactoMineR::PCA(data[, c(1:13)][,-c(1,2,4)], quali.sup = 1, graph = F)
factoextra::fviz_pca_biplot(res.PCA, axes = c(1,2), label = "var", habillage = 1, repel = T,
                            addEllipses = T, ellipse.level = 0.8)  +
  scale_color_manual(values=c( "#34e042", "#6DB4EE", "#b58404")) +
  theme_classic()

# v2
 
autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

# v3
g <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

ggsave(filename = "PCA_full_HabitatPref.png", plot = g, bg = "white", width = 8, height = 8, dpi = 600)

# v4
g0 <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  theme(legend.position = c(0.85,0.2))

g1 <- g0 + stat_ellipse(aes(col = Type, alpha = Type), level = 0.85, size = 1.5) + scale_alpha_manual(guide = "none", values = c(0, 1, 1))

g3 <- g0 + stat_ellipse(aes(col = Type, alpha = Type), level = 0.85, size = 1.5) + scale_alpha_manual(guide = "none", values = c(1, 0, 0))

g2 <- g0 + stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)
cowplot::plot_grid(g0,g1, g2)

ggsave(filename = "PCA_0.png", plot = g0, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_1.png", plot = g1, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_2.png", plot = g2, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_3.png", plot = g3, bg = "white", width = 8, height = 8, dpi = 600)

# v5
data$Habitat <- recode(data$Habitat, BF='SF soils', TF= 'TF soils')

g5<- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, alpha = "Type", size = 2, col = "Habitat",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         loadings.label.colour = 'black', loadings.colour = 'black') +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse()+
  scale_alpha_manual(guide = "none", values = c(0, 0.4, 0.4)) +
  scale_color_manual("Habitat of\ncollect", values = c("#6DB4EE", "#b58404")) 

ggsave(filename = "PCA_5.png", plot = g5, bg = "white", width = 8, height = 8, dpi = 600)
```

#trait imputation for all traits except Stomata

##PCA without stomata
```{r}

```

##PCA with stomata

```{r}


Data <- read_csv("Dataset/Subset_imputation_exceptSD.csv", col)
Data <- Data %>% dplyr::select(-Code, -Genus, -Species, Habitat, Type) 



# data
data <- Data %>% na.omit() #423 observation

data$Type <- recode(data$Type, BF='SF Specialist', TF= 'TF Specialist')
#data <- mutate(data, Type = recode(Type, "BF" = "SF specialist")) #other way to do it

# v0
res.PCA <- FactoMineR::PCA(data[, c(1:13)][,-c(1,2,4)], quali.sup = 1, graph = F)
factoextra::fviz_pca_biplot(res.PCA, axes = c(1,2), label = "var", habillage = 1, repel = T,
                            addEllipses = T, ellipse.level = 0.8)  +
  scale_color_manual(values=c( "#34e042", "#6DB4EE", "#b58404")) +
  theme_classic()

# v2
 
autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

# v3
g <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

ggsave(filename = "PCA_full_HabitatPref.png", plot = g, bg = "white", width = 8, height = 8, dpi = 600)

# v4
g0 <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  theme(legend.position = c(0.85,0.2))

g1 <- g0 + stat_ellipse(aes(col = Type, alpha = Type), level = 0.85, size = 1.5) + scale_alpha_manual(guide = "none", values = c(0, 1, 1))

g3 <- g0 + stat_ellipse(aes(col = Type, alpha = Type), level = 0.85, size = 1.5) + scale_alpha_manual(guide = "none", values = c(1, 0, 0))

g2 <- g0 + stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)
cowplot::plot_grid(g0,g1, g2)

ggsave(filename = "PCA_0.png", plot = g0, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_1.png", plot = g1, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_2.png", plot = g2, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_3.png", plot = g3, bg = "white", width = 8, height = 8, dpi = 600)

# v5
data$Habitat <- recode(data$Habitat, BF='SF soils', TF= 'TF soils')

g5<- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, alpha = "Type", size = 2, col = "Habitat",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         loadings.label.colour = 'black', loadings.colour = 'black') +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse()+
  scale_alpha_manual(guide = "none", values = c(0, 0.4, 0.4)) +
  scale_color_manual("Habitat of\ncollect", values = c("#6DB4EE", "#b58404")) 

ggsave(filename = "PCA_5.png", plot = g5, bg = "white", width = 8, height = 8, dpi = 600)
```


#MANOVA

```{r Claire code}

data_sub <- Metradica %>% filter(!is.na(Metradica$Genus))
trait_list_sub<-names(data_sub)[c(8:16)]

#Puis, j’ai loggé les traits avant de faire l’ACP. (deja loge depuis le debut)

data_pca<-data_sub %>%
  select(c("Name","Habitat","Type",trait_list_sub)) %>%
  filter(complete.cases(.))
trait<-data_pca[,4:ncol(data_pca)]
vars<-data_pca[,1:3]
res.pca<-PCA(trait, scale.unit=T, ncp=5, graph=F)
res.pca.ind<-get_pca_ind(res.pca)
m<-manova(res.pca.ind$coord ~ data_pca $Habitat + data_pca $Type + data_pca $Name) 
```

#PERMANOVA

PERMANOVA assumes no distribution, allows for differences in between-group variation, is insensitive to multicollinearity, allows for multiple variables and is insensitive to many zeros.

```{r}
data_PCA <- data

data_PCA <- Metradica[, c(1:13)][]

res.PCA <- FactoMineR::PCA(data_PCA, quali.sup = 1, graph = F)

```


```{r}
dis <- vegdist(data_PCA,method="euclidean", na.rm = TRUE)
mod <- betadisper(dis,Metradica$Type)
anova(mod)
```
the null hypothesis of no differences between types can be rejected (pvalue 0.35)

H0 = no difference
H1 = differences

P-value = 0.35 so we reject H0 : our group dispersions are different between types.

Check if our treatments have different means. Use a permuting method to check if the difference is really due to the treatments.

```{r}
adonis2(data_PCA~data$Type, permutations = 999, na.rm = TRUE)
```

P-value (0.001) *** is always significant so our group types have different means.

Process a pairwise analyse to detect which treatments are different from each other.

install pairwise : ` install_github("pmartinezarbizu/pairwiseAdonis/pairwiseAdonis")`

```{r}
library(pairwiseAdonis)
pairwise_adonis <- pairwise.adonis(data_PCA,Metradica$Type)

require(dplyr)
require(gt)
pairwise_adonis %>%
  gt() %>%
  tab_header(title = md("*Permutational MANOVA on habitat preference*"))

```

