---
title: "Boxplots"
author: "Marion Boisseaux"
date: "13/09/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---


# Libraries

```{r}
library(tidyverse)
library(dplyr)
library(ggfortify)
library(corrplot) 
library(ggpubr)
library(ggfortify)
library(agricolae)
library(rstatix)
library(readxl)
library(lme4)
library(ggeffects) #draw plots of models
library(nlme)
library(sjPlot) #for plotting lmer and glmer mods
library(gridExtra)
library(rio)
library(multcomp) #for lmer model to do anovas
library(lmerTest) #same
library(emmeans)#same
library(ggplotify)
library(car)
 
```
#function
```{r}
log_abs_trans <- function() {
    scales::trans_new(
        name = "log_abs", 
        transform = function(x) log(abs(x)), 
        inverse = function(x) exp(x));
}

library(broom)
get_formula <- function(model) {
  
  broom::tidy(model)[, 1:2] %>%
    mutate(sign = ifelse(sign(estimate) == 1, ' + ', ' - ')) %>% #coeff signs
    mutate_if(is.numeric, ~ abs(round(., 2))) %>% #for improving formatting
    mutate(a = ifelse(term == '(Intercept)', paste0('y ~ ', estimate), paste0(sign, estimate, ' * ', term))) %>%
    summarise(formula = paste(a, collapse = '')) %>%
    as.character
  
}



```
#Colors
```{r}
#From color blind palette
library(ggpubfigs)
#from palette ito_seven
E79F02 #orange for TF
56B4E9 #blue for SF
009E72 #green for Generalists

```


# Data



```{r Data log subset, message=FALSE, warning=FALSE}

# data

library(dplyr)
Metradica_log <- read.csv("C://Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/ALL/Final_Metradica_OUT_30112022.csv") %>% 
  dplyr::select(Code, Genus, Species, Name, Habitat, Type, Forest, Gmin, TLP, LSWC, MajVLA, Nitrogen, Carbon, Phosphorous, Potassium, SD, TWI) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium", "SD"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium", "SD"), log) %>% 
  mutate(TLP = -TLP) %>%
  rename(K= Potassium,
         P = Phosphorous,
         C = Carbon, 
         N= Nitrogen)

sub_data_TF <- Metradica_log %>%
  filter(Name %in% c("Dicorynia_guianensis", "Iryanthera_sagotiana", "Gustavia_hexapetala", "Licania_membranacea", "Poraqueiba_guianensis", "Virola_michelii"))

sub_data_SF <- Metradica_log %>%
  filter(Name %in% c("Eschweilera_coriacea","Eperua_falcata", "Iryanthera_hostmannii", "Laetia_procera", "Protium_opacum subsp. rabelianum", "Pterocarpus_officinalis", "Symphonia_globulifera", "Virola_surinamensis", "Carapa_surinamensis"))

sub_data_G <-  Metradica_log %>%
  filter(Name %in% c("Bocoa_prouacensis", "Conceveiba_guianensis", "Jacaranda_copaia subsp. copaia", "Hymenopus_heteromorphus", "Protium_stevensonii", "Tachigali_melinonii"))

sub_data <- bind_rows(sub_data_TF, sub_data_SF, sub_data_G)

Metradica_log <- sub_data



```

```{r Data not log subset}

# data

library(dplyr)
Metradica <- read.csv("C://Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/ALL/Final_Metradica_OUT_30112022.csv") %>% 
  dplyr::select(Code, Genus, Species, Name, Habitat, Type, Forest, Gmin, TLP, LSWC, MajVLA, Nitrogen, Carbon, Phosphorous, Potassium, SD, TWI) %>%
  rename(K= Potassium,
         P = Phosphorous,
         C = Carbon, 
         N= Nitrogen)

sub_data_TF <- Metradica %>%
  filter(Name %in% c("Dicorynia_guianensis", "Iryanthera_sagotiana", "Gustavia_hexapetala", "Licania_membranacea", "Poraqueiba_guianensis", "Virola_michelii"))

sub_data_SF <- Metradica %>%
  filter(Name %in% c("Eschweilera_coriacea","Eperua_falcata", "Iryanthera_hostmannii", "Laetia_procera", "Protium_opacum subsp. rabelianum", "Pterocarpus_officinalis", "Symphonia_globulifera", "Virola_surinamensis", "Carapa_surinamensis"))

sub_data_G <-  Metradica %>%
  filter(Name %in% c("Bocoa_prouacensis", "Conceveiba_guianensis", "Jacaranda_copaia subsp. copaia", "Hymenopus_heteromorphus", "Protium_stevensonii", "Tachigali_melinonii"))

sub_data <- bind_rows(sub_data_TF, sub_data_SF, sub_data_G)

Metradica <- sub_data

```

#exploring na
```{r}

#check the nas
pMiss <- function(x){sum(is.na(x))/length(x)*100}
apply(Metradica,2,pMiss)

#we see that SD is almost 30% missing values, the rest is below a threshold of 5%
library(VIM)
aggr_plot <- aggr(Metradica, col=c('navyblue','red'), numbers=TRUE, sortVars=TRUE, labels=names(Metradica), cex.axis=.7, gap=3, ylab=c("Histogram of missing data","Pattern"))

#imputing th emissing data for all traits 
library(mice)
tempData <- mice(Metradica,m=5,maxit=50,meth='pmm',seed=500)
summary(tempData)
completedData <- complete(tempData,1)

#no imputation of SD
data <- Metradica %>% dplyr::select(-SD)
tempData_noSD <- mice(data,m=5,maxit=50,meth='pmm',seed=500) #m=5 is 5 datasets
summary(tempData_noSD)
completedData <- complete(tempData_noSD,1) #1 is choosing dataset 1 out of the 5

B <- Metradica %>% dplyr::select(Code, SD)

A <- left_join(completedData, B,  c("Code"))

write.csv(A, "Subset_imputation_exceptSD.csv", col.names = FALSE, row.names = FALSE)

#inspecting data after imputation
densityplot(tempData_noSD)
tempData_noSD$imp$K

```


# Trait variation - raw data 

No imputation.

```{r}

data <- sub_data %>%
  dplyr::select(Name, Type, Gmin, TLP, LSWC, MajVLA, N, C, P, K, SD) %>% 
  reshape2::melt(c("Name", "Type"), variable.name = "Trait")
```


```{r Trait distribution coord_flip}
data$Type <- factor(data$Type, levels = c("BF", "TF", "Generalist")) 
p <-  data %>%
  mutate(Trait = as.character(Trait)) %>% 
  mutate(Trait = dplyr::recode(Trait, "Gmin" = "g[min]~(mmol%.%m^{-2}%.%s^{-1})", "TLP" = "pi[tlp]~(MPa)", "C"= "C~('%')", "N" = "N~('%')", "K"= "K~(g%.%kg^{-1})", "LSWC" = "LSWC~('%')", "MajVLA" = "MajVLA~(mm%.%mm^{-2})", "P" = "P~(g%.%kg^{-1})", "SD" = "SD~(mm^{-2})")) %>% 
  left_join(dplyr::select(data, Type, Name) %>%
              unique() %>%
              arrange(Type, Name) %>%
              mutate(order_graph = 1:n())) %>%
  mutate(Name = gsub("_", " ", Name)) %>% 
  separate(Name, c("genus", "species")) %>% 
  mutate(Name = paste0(str_sub(genus, 1, 1), ". ", species)) %>% 
  ggplot(aes(x = reorder(Name, order_graph), y= value)) +
  geom_boxplot(aes(fill = Type),
  #              alpha = 0.5, col = "lightgrey") +
  #geom_violin(aes(fill = Type),
               alpha = 0.5, col = "lightgrey") +
  scale_fill_manual(name = "Habitat preference", 
                    values = c("TF" = "#E79F02", #orange for TF
                                "BF" =  "#56B4E9", #blue for SF
                                "Generalist" = "#009E72"),  #green for Generalists
                    labels = c("TF" = "TF specialist",
                               "Generalist" = "Generalist", 
                               "BF" = "SF specialist")) +
  facet_wrap(~ Trait, scales = "free_x", label = label_parsed) +
  theme_minimal() +
  coord_flip() +
  theme(axis.text.y = element_text(face = "italic"), axis.title = element_blank(),legend.position = "bottom") 

ggsave(filename = "Trait Distribution.png", plot = p, bg = "white", width = 10, height = 8, dpi = 600)
```


#PCA

##no trait imputation

###PCA without stomata

```{r}
#data is already logged

data_withOUTNA_no_stomata <-read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_not_imputed/METRADICA_subset.csv") %>% dplyr::select(-SD) %>% na.omit() #537 indv


data <- data_withOUTNA_no_stomata  %>% 
  dplyr::select(-Code, -Genus, -Species, Habitat, Type) 

data$Type <- dplyr::recode(data$Type, BF='SF Specialist', TF= 'TF Specialist')

g_nostomata <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
 #scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#009E72", "#56B4E9", "#E79F02")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

ggsave(filename = "PCA_full_HabitatPref_noSD.png", plot = g_nostomata, bg = "white", width = 8, height = 8, dpi = 600)

```



###PCA with stomata

```{r}


data_without_NA <- read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_not_imputed/METRADICA_subset.csv") %>% na.omit() #379 indv 

data <- data_without_NA %>%
  dplyr::select(-Code, -Genus, -Species, Habitat, Type)  

data$Type <- dplyr::recode(data$Type, BF='SF Specialist', TF= 'TF Specialist')
 
gSD <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#009E72", "#56B4E9", "#E79F02")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

ggsave(filename = "PCA_full_HabitatPref_SD.png", plot = gSD, bg = "white", width = 8, height = 8, dpi = 600)

```

##trait imputation for all traits except Stomata

###PCA without stomata
```{r}
Data <- read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") %>% 
  dplyr::select(-Code, -Genus, -Species, Habitat, Type, -SD) %>%
  rename(Potassium = K, 
         Phosphorous = P, 
         Nitrogen = N,
         Carbon = C) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium"), log) %>% 
  mutate(TLP = -TLP)

Data$Type <- dplyr::recode(Data$Type, BF='SF Specialist', TF= 'TF Specialist')
#data <- mutate(data, Type = recode(Type, "BF" = "SF specialist")) #other way to do it

Data <- Data %>% na.omit()

g <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen, data = Data, cor = T),
         data = Data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
 # scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#009E72", "#56B4E9", "#E79F02")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

ggsave(filename = "PCA_full_HabitatPref_imputed.png", plot = g, bg = "white", width = 8, height = 8, dpi = 600)
```

###PCA with stomata

```{r}
Data <- read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") %>% 
  dplyr::select(-Code, -Genus, -Species, Habitat, Type) %>%
  rename(Potassium = K, 
         Phosphorous = P, 
         Nitrogen = N,
         Carbon = C) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium", "SD"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium", "SD"), log) %>% 
  mutate(TLP = -TLP)

Data$Type <- dplyr::recode(Data$Type, BF='SF Specialist', TF= 'TF Specialist')
#data <- mutate(data, Type = recode(Type, "BF" = "SF specialist")) #other way to do it

Data <- Data %>% na.omit()

g_with_stomata <- autoplot(princomp(~ Gmin + TLP + LSWC + MajVLA + Potassium + Phosphorous + Carbon + Nitrogen + SD, data = Data, cor = T),
         data = Data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#009E72", "#56B4E9", "#E79F02")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

ggsave(filename = "PCA_full_HabitatPref_SD_imputed.png", plot = g_with_stomata, bg = "white", width = 8, height = 8, dpi = 600)

```

# Colinearity

No trait imputation for this section.
Log or not logged, correlations are going to be the same.

```{r}

library(corrplot)

traits <- Metradica_log %>% 
  dplyr::select(Gmin, TLP, LSWC, MajVLA, N, C, P, K, SD, TWI) 

png(height=500, width=500, file="mycorr.png", type = "cairo")
traits %>% na.omit() %>% # attention, la presence de NA bloque le processus pour regarder la colinearité
  cor(method = "spearman") %>% 
  corrplot::corrplot.mixed()
dev.off()

#other way to do it
corrplot(df2, #type = 'lower',
        # order = "alphabet", 
         p.mat = testRes$p, 
         sig.level = c(.001, .01, .05), #significant level, with default value 0.05. If the p-value in p-mat is bigger than sig.level, then the corresponding correlation coefficient is regarded as insignificant.
         pch.cex = 1.8, #star size
         insig = 'label_sig', pch.col = 'grey20',
         tl.pos="d", #write names of variables in the diagonal
         outline=FALSE,
         tl.cex = 1, #size of trait labels,
         col = COL2('RdBu', 10))

```

#Summary of variables 
```{r}
png(height=500, width=500, file="summary_traits.png")
plot(Metradica[,8:16])
dev.off()

#logged traits
png(height=500, width=500, file="summary_traits_log.png")
plot(Metradica_log[,8:16])
dev.off()

```
Interesting variables to look at
```{r}
#TLP and LSWC
p <- ggplot(Metradica_log) +
  aes(x = TLP, y = LSWC) +
  geom_point(shape = "circle", size = 1.5, colour = "#112446") +
  geom_smooth(method = "lm") +
  theme_minimal()
  
model <- lm(LSWC ~ TLP, data = Metradica_log)
get_formula(model)

r_squared <- scales::percent(summary(model)$r.squared, accuracy = 0.01)

p + geom_text(x = -0.8, y = 5.6,
            label = get_formula(model),
            color = 'red') +
  geom_text(x = -0.8, y = 5.4,
            label = r_squared,
            color = 'blue')

#TLP and SD
l <- ggplot(Metradica) +
  aes(x = TLP, y = SD) +
  geom_point(shape = "circle", size = 1.5, colour = "#112446") +
  geom_smooth(method = "lm") +
  theme_minimal()
  
model <- lm(SD ~ TLP, data = Metradica_log)
get_formula(model)

r_squared <- scales::percent(summary(model)$r.squared, accuracy = 0.01)

l + geom_text(x = -0.8, y = 7.2,
            label = get_formula(model),
            color = 'red') +
  geom_text(x = -0.8, y = 6.8,
            label = r_squared,
            color = 'blue')

#LSWC and K
n <- ggplot(Metradica_log) +
  aes(x = K, y = LSWC) +
  geom_point(shape = "circle", size = 1.5, colour = "#112446") +
  geom_smooth(method = "lm") +
  theme_minimal()
  
model <- lm(LSWC ~ K, data = Metradica_log)
get_formula(model)

r_squared <- scales::percent(summary(model)$r.squared, accuracy = 0.01)

n + geom_text(x = 0.8, y = 5.6,
            label = get_formula(model),
            color = 'red') +
  geom_text(x = 0.8, y = 5.4,
            label = r_squared,
            color = 'blue')

#SD and P
m <- ggplot(Metradica) +
  aes(x = P, y = SD) +
  geom_point(shape = "circle", size = 1.5, colour = "#112446") +
  geom_smooth(method = "lm") +
  theme_minimal()
  
model <- lm(SD ~ P, data = Metradica_log)
get_formula(model)

r_squared <- scales::percent(summary(model)$r.squared, accuracy = 0.01)

m + geom_text(x = -0.8, y = 7.2,
            label = get_formula(model),
            color = 'red') +
  geom_text(x = -0.8, y = 6.8,
            label = r_squared,
            color = 'blue')

```




# Question 1
**Question (H1) Specialist species of contrasting habitats differ in trait values.**


$$ M0 : Y_{ik} = \mu + E_{ik}, \quad E_{ik}\sim \mathcal{N} (0,\sigma^2) $$
$$ M1 : Y_{ik} = \mu + \alpha_i +  E_{ik}, \quad E_{ik}\sim \mathcal{N} (0,\sigma^2) $$

Mais je veux prendre en compte que l'echantillonage a ete réalisé dans 3 forets qui chacune a les 2 habitats. je veux accepter les variations de mon site mais pas les etudier forcement.



$$ M2 : Y_{ijk} = \mu + \alpha_i +  \beta_j + \gamma_{ij} + E_{ijk}, \quad E_{ijk}\sim \mathcal{N} (0,\sigma^2) $$


Et prendre en compte que j'ai plein d'espèces differentes. 

Ces espèces ne sont pas très equilibrée. 


$$ M_{comp} : Y_{ijsk} = \mu + \alpha_i +  \beta_j + \gamma_{ij} +  A_{is} +  E_{ijsk}, \quad E_{ijsk}\sim \mathcal{N} (0,\sigma^2), \quad A_{is}\sim \mathcal{N} (0,\sigma^2_S),  $$

## Specialist data
```{r data specialist}
Metradica$Type <- as.character(Metradica$Type)
Metradica$Name <- as.character(Metradica$Name)
Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Virola_michelii','TF',Type))

Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Eschweilera_coriacea','BF',Type))

data_specialist <- Metradica %>% filter(Type !="Generalist")


```

## graphs
```{r graph specialist}

#basic plot 
ggplot(data_specialist, aes(x = Type, y = Gmin)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(Gmin)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist")) + theme_classic()

#plot2

gmin.summary <- aggregate(Gmin ~ Type, mean, data=data_specialist)
gmin <- ggplot(data_specialist,aes(x=Type,y=Gmin, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Protium_opacum subsp. rabelianum"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=gmin.summary, aes(ymin = Gmin, ymax = Gmin),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(gmin~(mmol.m^-2~.s^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20)) 

gmin

#plot across forests

ggplot(data, aes(x = Type, y = Gmin, colour = Type)) +
      facet_wrap(~Forest, ncol=3) +   # a panel for each mountain range
      geom_boxplot(alpha = 0.5) +
      theme_classic() +
      theme(legend.position = "none",
            panel.spacing = unit(2, "lines"))  # adding space between panels

```



## gmin 
```{r H1 gmin}
# Global test

data_specialist$Name <- as.factor(data_specialist$Name)
data_specialist$Type <- as.factor(data_specialist$Type)
data_specialist <- data_specialist %>% mutate(Type = relevel(Type, ref = "TF")) #changer la reference
gmin_habitat <- lm(Gmin ~Type, data= data_specialist)
summary(gmin_habitat)
anova(gmin_habitat) #table analyse de la variance avec petit A. calcule des sommes de carrés seulement de type 1. 1 objet : type 1 / 2 objets : comparaisons de deux modeles. 
Anova(gmin_habitat, type = "II" ) # attention ici Anova avec grand A pour les types II

#plan d'experience equilibrer, il n'y aura aucune difference entre type 1 et type 2. les patates des facteurs ne seront pas confondus, mais distincts, pas d'ambiguité.


gmin_forest <- lm(Gmin ~Type + Forest, data =  data_specialist)
anova(gmin_habitat, gmin_forest)  #qu'est ce que l'on gagne a rajouter un effet forest après avoir pris en compte l'habitat
Anova(gmin_forest, gmin_habitat) #symetrisation de l'habitat et de la forest. on regarde l'habitat sachant que forest est deja considere.

model_gmin <- lmer(Gmin ~ Type + Forest + (1|Name), data=data_specialist) 



summary(model_gmin)

#Check normality of residuals 

plot(model_gmin) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.

#pour lmer
str(model_gmin)
model_gmin #you access the lmer objects through@
resid(model_gmin)
hist(resid(model_gmin), main = "Residual Histogram")
boxplot(resid(model_gmin), main="Residual Box Plot")
qqnorm(resid(model_gmin)) 
qqline(resid(model_gmin))

#plot
sjPlot::plot_model(model_gmin)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(gmin_habitat, 
                   axis.labels=c("TF Specialists"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on Gmin")

#estimated marginal means to compare TF specialists and SF specialists for each trait. ?

emmeans(gmin_comp, list(pairwise ~  Type), adjust = "tukey")


```

## TLP
```{r}

# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_tlp <- lmer(TLP ~ Type + (1|Forest/Type/Name), data=data) #so better to use it like that, simpler
summary(model_tlp)


#Check normality of residuals 

plot(model_tlp) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_tlp)
model_tlp #you access the lmer objects through@
resid(model_tlp)
hist(resid(model_tlp), main = "Residual Histogram")
boxplot(resid(model_tlp), main="Residual Box Plot")
qqnorm(resid(model_tlp)) 
qqline(resid(model_tlp))

#plot
sjPlot::plot_model(model_tlp)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_tlp, 
                   axis.labels=c("TWI"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of TWI on TLP")


#anova
summary(glht(model_tlp, linfct = mcp(Type = "Tukey")), test = adjusted("holm"))

emmeans(model_tlp, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'TLP')
  
#plot 
tlp.summary <- aggregate(TLP ~ Type, mean, data=data)
tlp <- ggplot(data,aes(x=Type,y=TLP, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=tlp.summary, aes(ymin = TLP, ymax = TLP),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(TLP~(MPa))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))  + 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(5), hide.ns = TRUE)

#plot raw 


ggplot(data, aes(x = Type, y = TLP)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(TLP)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
  
```

## LSWC 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_lswc <- lmer(LSWC ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_lswc)

model_lswc2 <- lm(LSWC ~ Type, data=data) 
#Check normality of residuals 

plot(model_lswc) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_lswc)
model_lswc #you access the lmer objects through@
resid(model_lswc)
hist(resid(model_lswc), main = "Residual Histogram")
boxplot(resid(model_lswc), main="Residual Box Plot")
qqnorm(resid(model_lswc2)) 
qqline(resid(model_lswc2))

#plot
sjPlot::plot_model(model_lswc)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_lswc, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on LSWC")


#tukey

emmeans(model_lswc, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'LSWC')


#plot 

LSWC.summary <- aggregate(LSWC ~ Type, mean, data=data)
LSWC <- ggplot(data,aes(x=Type,y=LSWC, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=LSWC.summary, aes(ymin = LSWC, ymax = LSWC),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(LSWC~(g.g^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(1.2), hide.ns = TRUE)

LSWC
#plot raw 


ggplot(data, aes(x = Type, y = LSWC)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(LSWC)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
```

## MajVLA 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)

model_majvla <- lmer(MajVLA ~ Type + (1|Forest/Habitat/Name), data=data) 
summary(model_majvla)


#Check normality of residuals 

plot(model_majvla) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_majvla)
model_majvla #you access the lmer objects through@
resid(model_majvla)
hist(resid(model_majvla), main = "Residual Histogram")
boxplot(resid(model_majvla), main="Residual Box Plot")
qqnorm(resid(model_majvla)) 
qqline(resid(model_majvla))

#plot
sjPlot::plot_model(model_majvla)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_majvla, 
                   #axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on MajVLA")


#tukey

emmeans(model_majvla, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'MajVLA')

MajVLA.summary <- aggregate(MajVLA ~ Type, mean, data=data)
MajVLA <- ggplot(data,aes(x=Type,y=MajVLA, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=MajVLA.summary, aes(ymin = MajVLA, ymax = MajVLA),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(MajVLA~(mm.mm^-2))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(2.9), hide.ns = TRUE)
MajVLA
#plot raw 


ggplot(data, aes(x = Type, y = MajVLA)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(MajVLA)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
```

## LA 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_la <- lmer(LA ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_la)


#Check normality of residuals 

plot(model_la) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_la)
model_la #you access the lmer objects through@
resid(model_la)
hist(resid(model_la), main = "Residual Histogram")
boxplot(resid(model_la), main="Residual Box Plot")
qqnorm(resid(model_la)) 
qqline(resid(model_la))

#plot
sjPlot::plot_model(model_la)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_la, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on LA")


#tukey

emmeans(model_la, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'LA')
LA.summary <- aggregate(LA ~ Type, mean, data=data)
LA <- ggplot(data,aes(x=Type,y=LA, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=LA.summary, aes(ymin = LA, ymax = LA),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(LA~(cm²))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(5.5), hide.ns = TRUE)
LA

#plot raw 


ggplot(data, aes(x = Type, y = LA)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(LA)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```


## K 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_K <- lmer(K ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_K)


#Check normality of residuals 

plot(model_K) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_K)
model_K #you access the lmer objects through@
resid(model_K)
hist(resid(model_K), main = "Residual Histogram")
boxplot(resid(model_K), main="Residual Box Plot")
qqnorm(resid(model_K)) 
qqline(resid(model_K))

#plot

sjPlot::plot_model(model_K, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on K")


#tukey

emmeans(model_K, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'K')

K.summary <- aggregate(K ~ Type, mean, data=data)
K <- ggplot(data,aes(x=Type,y=K, col=Name)) + 
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE","Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE",  "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=K.summary, aes(ymin = K, ymax = K),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(K~(g.kg^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(3.2), hide.ns = TRUE)

K
#plot raw 


ggplot(data, aes(x = Type, y = K)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(K)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## P 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_P <- lmer(P ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_P)


#ChecP normality of residuals 

plot(model_P) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_P)
model_P #you access the lmer objects through@
resid(model_P)
hist(resid(model_P), main = "Residual Histogram")
boxplot(resid(model_P), main="Residual Box Plot")
qqnorm(resid(model_P)) 
qqline(resid(model_P))

#plot

sjPlot::plot_model(model_P, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on P")


#tuPey

emmeans(model_P, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'P')

P.summary <- aggregate(P ~ Type, mean, data=data)
P <- ggplot(data,aes(x=Type,y=P, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=P.summary, aes(ymin = P, ymax = P),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(P~(g.kg^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(0.5), hide.ns = TRUE)
P

#plot raw 


ggplot(data, aes(x = Type, y = P)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(P)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## C 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_C <- lmer(C ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_C)


#ChecP normality of residuals 

plot(model_C) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_C)
model_C #you access the lmer objects through@
resid(model_C)
hist(resid(model_C), main = "Residual Histogram")
boxplot(resid(model_C), main="Residual Box Plot")
qqnorm(resid(model_C)) 
qqline(resid(model_C))

#plot

sjPlot::plot_model(model_C, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on C")


#tuPey

emmeans(model_C, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'C')

C.summary <- aggregate(C ~ Type, mean, data=data)
C <- ggplot(data,aes(x=Type,y=C, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=C.summary, aes(ymin = C, ymax = C),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(C~("%"))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(4.1), hide.ns = TRUE)

C

#plot raw 


ggplot(data, aes(x = Type, y = C)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(C)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## N 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_N <- lmer(N ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_N)


#ChecP normality of residuals 

plot(model_N) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_N)
model_N #you access the lmer objects through@
resid(model_N)
hist(resid(model_N), main = "Residual Histogram")
boxplot(resid(model_N), main="Residual Box Plot")
qqnorm(resid(model_N)) 
qqline(resid(model_N))

#plot

sjPlot::plot_model(model_N, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on N")


#tuPey

emmeans(model_N, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'N')

N.summary <- aggregate(N ~ Type, mean, data=data)
N <-ggplot(data,aes(x=Type,y=N, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=N.summary, aes(ymin = N, ymax = N),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(N~("%"))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(1.2), hide.ns = TRUE)
N

#plot raw 


ggplot(data, aes(x = Type, y = N)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(N)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```




# boucle


Trait ~ Type + Forest + (1/Name)

Fixed effet of habitat preference and forest and nested random effect of species.


```{r boucle}

#data from the clean data from Checks per trait per species script
library(ggplotify)

name_list <- NULL
Nbcol <- match(colnames(data)[8:17],colnames(data)) 
count <- 0
for ( i in data[,Nbcol]){
  count <-  count + 1
  name <- names(data[Nbcol[count]])
 
  #write the formula
  formu <- formula(paste(name,"~Type + Forest + (1|Name)"))
 
  # Create the graphz
  Scale_loc <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      sqrt(abs(resid(.)))~fitted(.),
      type=c("p","smooth"),
      col.line=1,
      xlab=paste0("Fitted  ",name),
      ylab=expression(sqrt("Standardized residuals")))
    )
 

  QQ <- as.ggplot(
    lattice::qqmath(
      lmer(formula=formu,data=data))
      )
   
 
  Res_Fit <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      type=c("p","smooth"),
      col.line = 1),
      xlab=paste0("Fitted  ",name),
      ylab=expression(sqrt("Residuals"))
    )
 
  Res_lev <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      rstudent(.)~hatvalues(.),
      xlab=paste0("Leverage  ",name),
      ylab=expression(sqrt("Residuals"))
     
      )
    )
 
  # Save them
  plot <- arrangeGrob(Res_Fit,
                      QQ,
                      Scale_loc,
                      Res_lev,
                      ncol = 2,
                      nrow = 2)
 
  ggsave(plot,
         filename=paste0("lmer_diagnostic_",name,".jpg"),
         device = "jpg",
         path = "./Results/Model/Model_2/Subset/Diag",
         width = 7,
         height = 9,
         units = "in")
 
  name_list <- c(name_list,name)
  
  #plot model
   print(sjPlot::plot_model(lmer(formula=formu,data=data), axis.labels=c("Specialist TF"), show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on",
         file=paste0("./Results/Model/Model_2/Subset/Plot/",name,".jpeg")))
   
  # Create an html summary table
  print(sjPlot::tab_model(lmer(formula=formu,data=data),file=paste0("./Results/Model/Model_2/Subset/Table/",name,".html")
                          )
        )
  # # convert it to png
  # webshot::webshot(paste0("./Results/Boxplot/Subset/Table/",name,".html"),
  #         paste0("./Results/Boxplot/Subset/Table/",name,".png")
  #         )
}
```

Plot everything together

```{r}

model_gmin1 <- lmer(Gmin ~ TWI + (1|Name), data= data)

mydata$model_gmin1_predicted <- predict(model_gmin1)

ggplot(data, aes(x = Type, y = Gmin, colour = Type)) +
      facet_wrap(~Forest, ncol=3) +   # a panel for each mountain range
      geom_boxplot(alpha = 0.5) +
      theme_classic() +
      #geom_line(data = cbind(data, pred = predict(model_gmin1)), aes(y = pred), size = 1) +  # adding predicted line from mixed model 
  # geom_smooth(method = "lm", se = FALSE) thisis the predicted line comapring only the chosen variables
      theme(legend.position = "none",
            panel.spacing = unit(2, "lines"))  # adding space between panels

```

# Question 2

**(H2) Functional divergence among individuals of generalists between habitats in terms of water usage during the dry season.**

IL y aurait un effet du TWI sur les traits fonctionnels et cela serait propre à chaque espèce.

$$ MComp : Y_{ik} = \mu + \alpha_i + (\beta+ \gamma_{i}) x_{ik} + E_{ik}, \quad E_{ik}\sim \mathcal{N} (0,\sigma^2) $$

la pente $$\mu$$ commune a tout le monde 
$$\alpha_i$$ effet diff de l'espèce sur l'ordonnée à l'origine
$$\beta$$ pente commune a tout le monde
$$\gamma$$ effet diff sur la pente liée au TWI

H0 : "pas d'effet ni de l'espèce ni du TWI


$$ M0 : Y_{ik} = \mu + E_{ik}, \quad E_{ik}\sim \mathcal{N} (0,\sigma^2) $$


##generalist data
```{r data generalist}
Metradica$Type <- as.character(Metradica$Type)
Metradica$Name <- as.character(Metradica$Name)
Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Virola_michelii','TF',Type))

Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Eschweilera_coriacea','BF',Type))

data_generalist <- Metradica %>% filter(Type =="Generalist")
```

## graph
```{r graph generalist, echo=FALSE}
library(ggplot2)
ggplot(data_generalist) +
  aes(x = TWI, y = Gmin, colour = Name) +
  geom_point(shape = "circle", size = 1.5) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal()

```


## gmin
```{r}
MO_generalist <- lm(Gmin ~ 1, data = data_generalist)
M1_generalist <- lm(Gmin ~Species + TWI, data = data_generalist) #meme pente pour tout le monde

anova(MO_generalist, M1_generalist)

#on peut rejetter l'hypothèse H0, il y a au moins un effet du TWI ou de l'espece sur Gmin.

M_complet <- lm(Gmin ~Species + TWI + Species:TWI, data = data_generalist)

anova(M1_generalist, M_complet)

autoplot(M_complet) #tout parait ok, pas trop de structure, pas trop d'effet levier: 58 ?


#plot results

```




# Question 3
**(H3) Generalist species express a higher intraspecific trait variability than specialist species.**

CV : pour quantifier l’ITV : absolute variation of the intraspecific trait with respect to the interspecific mean. 

CV is defined as the ratio of the standard deviation \sigma to the mean , expressed as a percentage. CV is convenient to compare variation of traits among species as it requires no ad hoc assumptions and is unitless. 

# CV
```{r}


cv_eff <- function(traits){
  if(any(is.na(traits)))
    traits=traits[!is.na(traits)]
  N=length(traits)
  y_bar=mean(traits)
  s2_hat=var(traits)
  cv_2=s2_hat/y_bar^2
  cv_1=sqrt(cv_2)
  gamma_1=sum(((traits-y_bar)/s2_hat^0.5)^3)/N
  gamma_2=sum(((traits-y_bar)/s2_hat^0.5)^4)/N
  bias=cv_2^(3/2)/N*(3*cv_2^0.5-2*gamma_1)
  bias2=cv_1^3/N-cv_1/4/N-cv_1^2*gamma_1/2/N-cv_1*gamma_2/8/N
  cv1=sd(traits)/mean(traits)
  cv4=cv_1-bias2
  re=cv4
  return(list(cv= re, eff = N))
} 


cv <- function(traits){
  if(any(is.na(traits)))
    traits=traits[!is.na(traits)]
  N=length(traits)
  y_bar=mean(traits)
  s2_hat=var(traits)
  cv_2=s2_hat/y_bar^2
  cv_1=sqrt(cv_2)
  gamma_1=sum(((traits-y_bar)/s2_hat^0.5)^3)/N
  gamma_2=sum(((traits-y_bar)/s2_hat^0.5)^4)/N
  bias=cv_2^(3/2)/N*(3*cv_2^0.5-2*gamma_1)
  bias2=cv_1^3/N-cv_1/4/N-cv_1^2*gamma_1/2/N-cv_1*gamma_2/8/N
  cv1=sd(traits)/mean(traits)
  cv4=cv_1-bias2
  re=cv4
  return(re)
}


# For generalists

cv_G <- sub_data_G %>% 
  group_by(Name) %>% 
  summarise_at(c("Gmin","TLP", "LSWC", "MajVLA", "SD", "K", "C", "N", "P", "SD"), funs(cv))

cv_G <- bind_rows(cv_G,
                  ungroup(cv_G) %>% 
                  summarise_all(mean) %>% 
                  mutate(Name = "mean"))

cv_long_G <- reshape2::melt(cv_G, "Name", variable.name = "trait", value.name = "CV")

cv_long_G$Type <- c("Generalist")



# For TF specialist


cv_TF <- sub_data_TF %>% 
  group_by(Name) %>% 
  summarise_at(c("Gmin","TLP", "LSWC", "MajVLA", "SD", "K", "C", "N", "P", "SD"), funs(cv))
#cannot calculate mean for lic.mem because does not exist. I do it by hand.
cv_SD <- (cv_TF$SD[1] + cv_TF$SD[2] + cv_TF$SD[3] + cv_TF$SD[5] + cv_TF$SD[6])/5

cv_TF <- bind_rows(cv_TF,
                   ungroup(cv_TF) %>% 
                  summarise_all(mean) %>% 
                  mutate(Name = "mean"))

cv_TF$SD[1] <- cv_SD

cv_long_TF <- reshape2::melt(cv_TF, "Name", variable.name = "trait", value.name = "CV")

cv_long_TF$Type <- c("TF")

cv_long_TF[35,3] <- cv_SD

# For BF specialist

cv_BF <- sub_data_SF %>% 
  group_by(Name) %>% 
  summarise_at(c("Gmin","TLP", "LSWC", "MajVLA","K", "C", "N", "P", "SD"), funs(cv))

#cannot calculate mean for car.sur because does not exist. I do it by hand.
cv_SD_BF <- (cv_BF$SD[2] + cv_BF$SD[3] + cv_BF$SD[4] + cv_BF$SD[5] + cv_BF$SD[6] +cv_BF$SD[7] + cv_BF$SD[8] + cv_BF$SD[9])/8

cv_BF <- bind_rows(cv_BF,
                ungroup(cv_BF) %>% 
                  summarise_all(mean) %>% 
                  mutate(Name = "mean")) 

cv_long_BF <- reshape2::melt(cv_BF, "Name", variable.name = "trait", value.name = "CV") 

cv_long_BF$Type <- c("BF")

cv_tot <- bind_rows(cv_long_G, cv_long_BF, cv_long_TF) 
cv_long_BF[90,3] <- cv_SD_BF

```


### plot cv
```{r}
# plot all 

cv_plot <- cv_tot %>% 
  mutate(CV =CV*100) %>%
  mutate(trait = dplyr::recode(trait, "Gmin" = "g[min]", "TLP" = "pi[tlp]")) %>%
  filter(Name != "mean") %>% 
  ggplot(aes(x = trait, y = CV, fill = Type, alpha=0.4)) +
  #scale_color_manual(values = c("Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Protium_opacum subsp. rabelianum"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE","Casearia_javitensis" ="#b58404", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Vouacapoua_americana"="#b58404", "Bocoa_prouacensis"="#34e042", "Eschweilera_coriacea"="#34e042", "Conceveiba_guianensis"="#34e042", "Virola_michelii"="#34e042", "Protium_stevensonii"="#34e042", "Hymenopus_heteromorphus"="#34e042", "Jacaranda_copaia subsp. copaia"="#34e042"))+
  geom_jitter() + 
  geom_boxplot(alpha=0.7)+
  scale_fill_manual("Habitat\npreference", 
                    values = c("#56B4E9", "#009E72",  "#E79F02"), 
                    labels = c("TF" = "TF specialist",
                               "Generalist" = "Generalist", 
                               "BF" = "SF specialist")) +
  scale_shape_discrete("Habitat\npreference") +
  ggtitle("Coefficient of variation (%)")+
  scale_x_discrete(labels = scales::label_parse()) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text())+
  theme(plot.title = element_text(size=14, face="bold")) +
  ylab("") + xlab("")+
    theme_minimal(base_size = 22)

ggsave(filename = "CV_plot.png", plot = cv_plot, bg = "white", width = 12, height = 8, dpi = 600)

```

###anova cv
```{r}
# Anova on CV
#We want to know if there is any significant difference between the average cv for each trait for the three habitat preferences.
cv_BF$Type <- c("BF")
cv_TF$Type <- c("TF")
cv_G$Type <- c("Generalist")

cv_tot2 <- rbind(cv_G, cv_BF, cv_TF) %>% filter(Name != "mean")

cv_tot2$Type <- as.factor(cv_tot2$Type)
levels(cv_tot2$Type)

#do it one trait at a time
cv_gmin <- cv_tot2 %>% dplyr::select(Name, Gmin, Type)
# Compute the analysis of variance
res.aov <- aov(Gmin ~ Type, data = cv_gmin)
# 1. Homogeneity of variances
plot(res.aov, 1)
# 2. Normality
plot(res.aov, 2)
# Summary of the analysis
summary(res.aov)
kruskal.test(Gmin ~ Type, data = cv_gmin)

#tlp
cv_tlp <- cv_tot2 %>% dplyr::select(Name,TLP, Type)
res.aov <- aov(TLP ~ Type, data = cv_tlp)
plot(res.aov, 1)
plot(res.aov, 2)
summary(res.aov)
kruskal.test(TLP ~ Type, data = cv_tlp)

#SD
cv_SD <- cv_tot2 %>% dplyr::select(Name,SD, Type)
res.aov <- aov(SD ~ Type, data = cv_SD)
plot(res.aov, 1)
plot(res.aov, 2)
summary(res.aov)
kruskal.test(SD ~ Type, data = cv_SD)

#majvla
cv_MajVLA <- cv_tot2 %>% dplyr::select(Name,MajVLA, Type)
res.aov <- aov(MajVLA ~ Type, data = cv_MajVLA)
plot(res.aov, 1)
plot(res.aov, 2)
summary(res.aov)
kruskal.test(MajVLA ~ Type, data = cv_MajVLA)

#K
cv_K <- cv_tot2 %>% dplyr::select(Name,K, Type)
res.aov <- aov(K ~ Type, data = cv_K)
plot(res.aov, 1)
plot(res.aov, 2)
summary(res.aov) #pvalue <0.05
pairwise.t.test(cv_K$K, cv_K$Type,
                 p.adjust.method = "BH") #generalist and BF are different
kruskal.test(K ~ Type, data = cv_K)

#C
cv_C <- cv_tot2 %>% dplyr::select(Name,C, Type)
res.aov <- aov(C ~ Type, data = cv_C)
plot(res.aov, 1)
plot(res.aov, 2)
summary(res.aov) 

#P
cv_P <- cv_tot2 %>% dplyr::select(Name,P, Type)
res.aov <- aov(P ~ Type, data = cv_P)
plot(res.aov, 1)
plot(res.aov, 2)
summary(res.aov) 

#N
cv_N <- cv_tot2 %>% dplyr::select(Name,N, Type)
res.aov <- aov(N ~ Type, data = cv_N)
plot(res.aov, 1)
plot(res.aov, 2)
summary(res.aov)

#LSWC
cv_LSWC <- cv_tot2 %>% dplyr::select(Name,LSWC, Type)
res.aov <- aov(LSWC ~ Type, data = cv_LSWC)
plot(res.aov, 1)
plot(res.aov, 2)
summary(res.aov)

```

#VP - variance partitioning


[Géraldine DERROIRE] Be careful with variance partitioning as your sample is not balance between the different level (your work with Sylvain), and think carefully of the order you nest things into one another, there may be different possibility showing different things
```{r}
# Take into account only generalists. Variance partitioning 

vars <- sub_data_G %>% 
  dplyr::select(Forest, Habitat, Name, LSWC, TLP, Gmin, MajVLA, N, C, P, K, SD) %>% 
  reshape2::melt(c("Forest", "Habitat", "Name"), variable.name = "trait") %>% 
  na.omit() %>% 
  group_by(trait, Name) %>%
  group_by(trait) %>%
  do(var = nlme::lme(value ~ 1, random=~1|Forest/Habitat/Name, data = .) %>% 
       ape::varcomp(scale = F, cum = F) %>% 
       as.vector() %>% 
       data.frame(level = c("Forest", "Habitat", "Name"), variance = as.vector(.))) %>% 
  unnest(var) %>% 
  group_by(trait) %>% 
  mutate(pct = variance / sum(variance)*100)

#variance partitionning for these traits
library(ape)

varcomp.gmin<-varcomp(lme(Gmin~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1) 

varcomp.gmin$Trait <- c("Gmin")

varcomp.tlp<-varcomp(lme(TLP~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1)

varcomp.tlp$Trait <- c("TLP")

varcomp.LSWC<-varcomp(lme(LSWC~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1)

varcomp.LSWC$Trait <- c("LSWC")

varcomp.MajVLA<-varcomp(lme(MajVLA~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1)

varcomp.MajVLA$Trait <- c("MajVLA")

varcomp.SD<-varcomp(lme(SD~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1)

varcomp.SD$Trait <- c("SD")

varcomp.C<-varcomp(lme(C~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1)

varcomp.C$Trait <- c("C")

varcomp.K<-varcomp(lme(K~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1)

varcomp.K$Trait <- c("K")

varcomp.N<-varcomp(lme(N~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1)

varcomp.N$Trait <- c("N")

varcomp.P<-varcomp(lme(P~1,random=~1|Forest/Habitat/Species, data = sub_data_G, na.action = na.omit),1)

varcomp.P$Trait <- c("P")


vars <- bind_rows(varcomp.gmin, varcomp.tlp, varcomp.MajVLA, varcomp.LSWC, varcomp.SD, varcomp.C, varcomp.N, varcomp.K, varcomp.P) 


vars <- reshape2::melt(vars, "Trait", variable.name = "level", value.name = "variance") 

#plot

library(paletteer) 
paletteer_d("RColorBrewer::GnBu")

v<- vars %>%  
  mutate(Trait = dplyr::recode(Trait, "Gmin" = "g[min]", "TLP" = "pi[tlp]")) %>%
  ggplot(aes(fill=level, y=variance, x=Trait)) + 
  geom_bar(position="stack", stat="identity") +
  theme_minimal(base_size = 22) +
  ylab("") + xlab("")+
  theme(legend.text = element_text(face = "italic"),legend.position = "bottom") +
    scale_fill_manual("", values = c("#029A88","#C33110", "#CCBC44", "#EE6778"), 
                    labels = c("Forest" = "Forest\n(Paracou, Bafog, Kaw)",
                               "Habitat" = "Habitat\n(SF, TF)", 
                               "Species" = "Species\n(n=6)")) +
  scale_x_discrete(labels = scales::label_parse()) +
  ggtitle("Portion of total variance (%)")

ggsave(filename = "Variance_partitioning.png", plot = v, bg = "white", width = 10, height = 8, dpi = 600)
```


