---
title: "Boxplots"
author: "Marion Boisseaux"
date: "13/09/2022"
output: html_document
editor_options: 
  chunk_output_type: inline
---


# Libraries

```{r}
library(tidyverse)
library(dplyr)
library(ggfortify)
library(corrplot) 
library(ggpubr)
library(ggfortify)
library(agricolae)
library(rstatix)
library(readxl)
library(lme4)
library(ggeffects) #draw plots of models
library(nlme)
library(sjPlot) #for plotting lmer and glmer mods
library(gridExtra)
library(rio)
library(multcomp) #for lmer model to do anovas
library(lmerTest) #same
library(emmeans)#same
library(ggplotify)
library(car)
```

# Data

```{r Data_results, message=FALSE, warning=FALSE}

# data
library(googlesheets4)
gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets.readonly" )

Metradica_log <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica") %>% dplyr::select(Code, Genus, Species, Name, Habitat, Type, HabitatType, Forest, Gmin, TLP, LA, LSWC, MajVLA, K, P, C, N, MidribWidth, SecundaryWidth, DBH, TWI) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth", "K", "P", "C", "N"), abs) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth", "TWI","K", "P", "C", "N"), log) %>% 
  mutate(TLP = -TLP) %>% 
  na.omit() 

sub_data_TF <- Metradica_log %>%
  filter(Name %in% c("Dicorynia_guianensis", "Iryanthera_sagotiana", "Gustavia_hexapetala", "Licania_membranacea", "Poraqueiba_guianensis", "Virola_michelii"))

sub_data_SF <- Metradica_log %>%
  filter(Name %in% c("Eperua_falcata", "Iryanthera_hostmannii", "Laetia_procera", "Protium_opacum subsp. rabelianum", "Pterocarpus_officinalis", "Symphonia_globulifera", "Virola_surinamensis", "Eschweilera_coriacea"))

sub_data_G <-  Metradica_log %>%
  filter(Name %in% c("Bocoa_prouacensis", "Conceveiba_guianensis", "Jacaranda_copaia subsp. copaia", "Hymenopus_heteromorphus", "Tachigali_melinonii", "Protium_stevensonii"))

sub_data <- bind_rows(sub_data_TF, sub_data_SF, sub_data_G)

Metradica <- sub_data

```

# Question 1
**Question (H1) Specialist species of contrasting habitats differ in trait values.**


$$ M0 : Y_{ik} = \mu + E_{ik}, \quad E_{ik}\sim \mathcal{N} (0,\sigma^2) $$
$$ M1 : Y_{ik} = \mu + \alpha_i +  E_{ik}, \quad E_{ik}\sim \mathcal{N} (0,\sigma^2) $$

Mais je veux prendre en compte que l'echantillonage a ete réalisé dans 3 forets qui chacune a les 2 habitats. je veux accepter les variations de mon site mais pas les etudier forcement.



$$ M2 : Y_{ijk} = \mu + \alpha_i +  \beta_j + \gamma_{ij} + E_{ijk}, \quad E_{ijk}\sim \mathcal{N} (0,\sigma^2) $$


Et prendre en compte que j'ai plein d'espèces differentes. 

Ces espèces ne sont pas très equilibrée. 


$$ M_{comp} : Y_{ijsk} = \mu + \alpha_i +  \beta_j + \gamma_{ij} +  A_{is} +  E_{ijsk}, \quad E_{ijsk}\sim \mathcal{N} (0,\sigma^2), \quad A_{is}\sim \mathcal{N} (0,\sigma^2_S),  $$

## Specialist data
```{r data specialist}
Metradica$Type <- as.character(Metradica$Type)
Metradica$Name <- as.character(Metradica$Name)
Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Virola_michelii','TF',Type))

data_specialist <- Metradica %>% filter(Type !="Generalist")


```

## graphs
```{r graph specialist}

#basic plot 
ggplot(data_specialist, aes(x = Type, y = Gmin)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(Gmin)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist")) + theme_classic()

#plot2

gmin.summary <- aggregate(Gmin ~ Type, mean, data=data_specialist)
gmin <- ggplot(data_specialist,aes(x=Type,y=Gmin, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Protium_opacum subsp. rabelianum"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=gmin.summary, aes(ymin = Gmin, ymax = Gmin),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(gmin~(mmol.m^-2~.s^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20)) 

gmin

#plot across forests

ggplot(data, aes(x = Type, y = Gmin, colour = Type)) +
      facet_wrap(~Forest, ncol=3) +   # a panel for each mountain range
      geom_boxplot(alpha = 0.5) +
      theme_classic() +
      theme(legend.position = "none",
            panel.spacing = unit(2, "lines"))  # adding space between panels

```



## gmin 
```{r H1 gmin}
# Global test

data_specialist$Name <- as.factor(data_specialist$Name)
data_specialist$Type <- as.factor(data_specialist$Type)
data_specialist <- data_specialist %>% mutate(Type = relevel(Type, ref = "TF")) #changer la reference
gmin_habitat <- lm(Gmin ~Type, data= data_specialist)
summary(gmin_habitat)
anova(gmin_habitat)

gmin_forest <- lm(Gmin ~Type + Forest, data =  data_specialist)
anova(gmin_habitat, gmin_forest)  #qu'est ce que l'on gagne a rajouter un effet forest après avoir pris en compte l'habitat
Anova(gmin_forest) #symetrisation de l'habitat et de la forest. on regarde l'habitat sachant que forest est deja considere.

gmin_comp <- lmer(Gmin ~ Type + Forest + (1|Name), data=data_specialist) 



summary(gmin_comp)

#Check normality of residuals 

plot(model_gmin1) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.

#pour lmer
str(model_gmin)
model_gmin #you access the lmer objects through@
resid(model_gmin)
hist(resid(model_gmin), main = "Residual Histogram")
boxplot(resid(model_gmin), main="Residual Box Plot")
qqnorm(resid(model_gmin)) 
qqline(resid(model_gmin))

#plot
sjPlot::plot_model(gmin_comp)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(gmin_habitat, 
                   axis.labels=c("TF Specialists"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on Gmin")

#estimated marginal means to compare TF specialists and SF specialists for each trait. ?

emmeans(gmin_comp, list(pairwise ~  Type), adjust = "tukey")


```

## TLP
```{r}

# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_tlp <- lmer(TLP ~ Type + (1|Forest/Type/Name), data=data) #so better to use it like that, simpler
summary(model_tlp)


#Check normality of residuals 

plot(model_tlp) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_tlp)
model_tlp #you access the lmer objects through@
resid(model_tlp)
hist(resid(model_tlp), main = "Residual Histogram")
boxplot(resid(model_tlp), main="Residual Box Plot")
qqnorm(resid(model_tlp)) 
qqline(resid(model_tlp))

#plot
sjPlot::plot_model(model_tlp)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_tlp, 
                   axis.labels=c("TWI"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of TWI on TLP")


#anova
summary(glht(model_tlp, linfct = mcp(Type = "Tukey")), test = adjusted("holm"))

emmeans(model_tlp, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'TLP')
  
#plot 
tlp.summary <- aggregate(TLP ~ Type, mean, data=data)
tlp <- ggplot(data,aes(x=Type,y=TLP, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=tlp.summary, aes(ymin = TLP, ymax = TLP),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(TLP~(MPa))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))  + 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(5), hide.ns = TRUE)

#plot raw 


ggplot(data, aes(x = Type, y = TLP)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(TLP)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
  
```

## LSWC 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_lswc <- lmer(LSWC ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_lswc)

model_lswc2 <- lm(LSWC ~ Type, data=data) 
#Check normality of residuals 

plot(model_lswc) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_lswc)
model_lswc #you access the lmer objects through@
resid(model_lswc)
hist(resid(model_lswc), main = "Residual Histogram")
boxplot(resid(model_lswc), main="Residual Box Plot")
qqnorm(resid(model_lswc2)) 
qqline(resid(model_lswc2))

#plot
sjPlot::plot_model(model_lswc)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_lswc, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on LSWC")


#tukey

emmeans(model_lswc, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'LSWC')


#plot 

LSWC.summary <- aggregate(LSWC ~ Type, mean, data=data)
LSWC <- ggplot(data,aes(x=Type,y=LSWC, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=LSWC.summary, aes(ymin = LSWC, ymax = LSWC),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(LSWC~(g.g^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(1.2), hide.ns = TRUE)

LSWC
#plot raw 


ggplot(data, aes(x = Type, y = LSWC)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(LSWC)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
```

## MajVLA 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)

model_majvla <- lmer(MajVLA ~ Type + (1|Forest/Habitat/Name), data=data) 
summary(model_majvla)


#Check normality of residuals 

plot(model_majvla) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_majvla)
model_majvla #you access the lmer objects through@
resid(model_majvla)
hist(resid(model_majvla), main = "Residual Histogram")
boxplot(resid(model_majvla), main="Residual Box Plot")
qqnorm(resid(model_majvla)) 
qqline(resid(model_majvla))

#plot
sjPlot::plot_model(model_majvla)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_majvla, 
                   #axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on MajVLA")


#tukey

emmeans(model_majvla, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'MajVLA')

MajVLA.summary <- aggregate(MajVLA ~ Type, mean, data=data)
MajVLA <- ggplot(data,aes(x=Type,y=MajVLA, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=MajVLA.summary, aes(ymin = MajVLA, ymax = MajVLA),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(MajVLA~(mm.mm^-2))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(2.9), hide.ns = TRUE)
MajVLA
#plot raw 


ggplot(data, aes(x = Type, y = MajVLA)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(MajVLA)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
```

## LA 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_la <- lmer(LA ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_la)


#Check normality of residuals 

plot(model_la) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_la)
model_la #you access the lmer objects through@
resid(model_la)
hist(resid(model_la), main = "Residual Histogram")
boxplot(resid(model_la), main="Residual Box Plot")
qqnorm(resid(model_la)) 
qqline(resid(model_la))

#plot
sjPlot::plot_model(model_la)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_la, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on LA")


#tukey

emmeans(model_la, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'LA')
LA.summary <- aggregate(LA ~ Type, mean, data=data)
LA <- ggplot(data,aes(x=Type,y=LA, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=LA.summary, aes(ymin = LA, ymax = LA),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(LA~(cm²))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(5.5), hide.ns = TRUE)
LA

#plot raw 


ggplot(data, aes(x = Type, y = LA)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(LA)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```


## K 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_K <- lmer(K ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_K)


#Check normality of residuals 

plot(model_K) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_K)
model_K #you access the lmer objects through@
resid(model_K)
hist(resid(model_K), main = "Residual Histogram")
boxplot(resid(model_K), main="Residual Box Plot")
qqnorm(resid(model_K)) 
qqline(resid(model_K))

#plot

sjPlot::plot_model(model_K, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on K")


#tukey

emmeans(model_K, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'K')

K.summary <- aggregate(K ~ Type, mean, data=data)
K <- ggplot(data,aes(x=Type,y=K, col=Name)) + 
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE","Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE",  "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=K.summary, aes(ymin = K, ymax = K),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(K~(g.kg^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(3.2), hide.ns = TRUE)

K
#plot raw 


ggplot(data, aes(x = Type, y = K)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(K)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## P 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_P <- lmer(P ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_P)


#ChecP normality of residuals 

plot(model_P) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_P)
model_P #you access the lmer objects through@
resid(model_P)
hist(resid(model_P), main = "Residual Histogram")
boxplot(resid(model_P), main="Residual Box Plot")
qqnorm(resid(model_P)) 
qqline(resid(model_P))

#plot

sjPlot::plot_model(model_P, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on P")


#tuPey

emmeans(model_P, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'P')

P.summary <- aggregate(P ~ Type, mean, data=data)
P <- ggplot(data,aes(x=Type,y=P, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=P.summary, aes(ymin = P, ymax = P),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(P~(g.kg^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(0.5), hide.ns = TRUE)
P

#plot raw 


ggplot(data, aes(x = Type, y = P)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(P)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## C 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_C <- lmer(C ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_C)


#ChecP normality of residuals 

plot(model_C) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_C)
model_C #you access the lmer objects through@
resid(model_C)
hist(resid(model_C), main = "Residual Histogram")
boxplot(resid(model_C), main="Residual Box Plot")
qqnorm(resid(model_C)) 
qqline(resid(model_C))

#plot

sjPlot::plot_model(model_C, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on C")


#tuPey

emmeans(model_C, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'C')

C.summary <- aggregate(C ~ Type, mean, data=data)
C <- ggplot(data,aes(x=Type,y=C, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=C.summary, aes(ymin = C, ymax = C),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(C~("%"))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(4.1), hide.ns = TRUE)

C

#plot raw 


ggplot(data, aes(x = Type, y = C)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(C)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## N 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_N <- lmer(N ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_N)


#ChecP normality of residuals 

plot(model_N) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_N)
model_N #you access the lmer objects through@
resid(model_N)
hist(resid(model_N), main = "Residual Histogram")
boxplot(resid(model_N), main="Residual Box Plot")
qqnorm(resid(model_N)) 
qqline(resid(model_N))

#plot

sjPlot::plot_model(model_N, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on N")


#tuPey

emmeans(model_N, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'N')

N.summary <- aggregate(N ~ Type, mean, data=data)
N <-ggplot(data,aes(x=Type,y=N, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=N.summary, aes(ymin = N, ymax = N),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(N~("%"))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(1.2), hide.ns = TRUE)
N

#plot raw 


ggplot(data, aes(x = Type, y = N)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(N)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```




# boucle


Trait ~ Type + Forest + (1/Name)

Fixed effet of habitat preference and forest and nested random effect of species.


```{r boucle}

#data from the clean data from Checks per trait per species script
data <- clean

name_list <- NULL
Nbcol <- match(colnames(data)[9:18],colnames(data)) 
count <- 0
for ( i in data[,Nbcol]){
  count <-  count + 1
  name <- names(data[Nbcol[count]])
 
  #write the formula
  formu <- formula(paste(name,"~Type + Forest + (1|Name)"))
 
  # Create the graphz
  Scale_loc <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      sqrt(abs(resid(.)))~fitted(.),
      type=c("p","smooth"),
      col.line=1,
      xlab=paste0("Fitted  ",name),
      ylab=expression(sqrt("Standardized residuals")))
    )
 

  QQ <- as.ggplot(
    lattice::qqmath(
      lmer(formula=formu,data=data))
      )
   
 
  Res_Fit <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      type=c("p","smooth"),
      col.line = 1),
      xlab=paste0("Fitted  ",name),
      ylab=expression(sqrt("Residuals"))
    )
 
  Res_lev <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      rstudent(.)~hatvalues(.),
      xlab=paste0("Leverage  ",name),
      ylab=expression(sqrt("Residuals"))
     
      )
    )
 
  # Save them
  plot <- arrangeGrob(Res_Fit,
                      QQ,
                      Scale_loc,
                      Res_lev,
                      ncol = 2,
                      nrow = 2)
 
  ggsave(plot,
         filename=paste0("lmer_diagnostic_",name,".jpg"),
         device = "jpg",
         path = "./Results/Model/Model_2/Subset/Diag",
         width = 7,
         height = 9,
         units = "in")
 
  name_list <- c(name_list,name)
  
  #plot model
   print(sjPlot::plot_model(lmer(formula=formu,data=data), axis.labels=c("Specialist TF"), show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on",
         file=paste0("./Results/Model/Model_2/Subset/Plot/",name,".jpeg")))
   
  # Create an html summary table
  print(sjPlot::tab_model(lmer(formula=formu,data=data),file=paste0("./Results/Model/Model_2/Subset/Table/",name,".html")
                          )
        )
  # # convert it to png
  # webshot::webshot(paste0("./Results/Boxplot/Subset/Table/",name,".html"),
  #         paste0("./Results/Boxplot/Subset/Table/",name,".png")
  #         )
}
```

Plot everything together

```{r}

model_gmin1 <- lmer(Gmin ~ TWI + (1|Name), data= data)

mydata$model_gmin1_predicted <- predict(model_gmin1)

ggplot(data, aes(x = Type, y = Gmin, colour = Type)) +
      facet_wrap(~Forest, ncol=3) +   # a panel for each mountain range
      geom_boxplot(alpha = 0.5) +
      theme_classic() +
      #geom_line(data = cbind(data, pred = predict(model_gmin1)), aes(y = pred), size = 1) +  # adding predicted line from mixed model 
  # geom_smooth(method = "lm", se = FALSE) thisis the predicted line comapring only the chosen variables
      theme(legend.position = "none",
            panel.spacing = unit(2, "lines"))  # adding space between panels

```

# Question 2

**(H2) Functional divergence among individuals of generalists between habitats in terms of water usage during the dry season.**

IL y aurait un effet du TWI sur les traits fonctionnels et cela serait propre à chaque espèce.

$$ MComp : Y_{ik} = \mu + \alpha_i + (\beta+ \gamma_{i}) x_{ik} + E_{ik}, \quad E_{ik}\sim \mathcal{N} (0,\sigma^2) $$

la pente $$\mu$$ commune a tout le monde 
$$\alpha_i$$ effet diff de l'espèce sur l'ordonnée à l'origine
$$\beta$$ pente commune a tout le monde
$$\gamma$$ effet diff sur la pente liée au TWI

H0 : "pas d'effet ni de l'espèce ni du TWI


$$ M0 : Y_{ik} = \mu + E_{ik}, \quad E_{ik}\sim \mathcal{N} (0,\sigma^2) $$


##generalist data
```{r data generalist}

Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Virola_michelii','TF',Type))

data_generalist <- Metradica %>% filter(Type =="Generalist")
```

## graph
```{r graph generalist, echo=FALSE}
library(ggplot2)
ggplot(data_generalist) +
  aes(x = TWI, y = Gmin, colour = Name) +
  geom_point(shape = "circle", size = 1.5) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal()

```


## gmin
```{r}
MO_generalist <- lm(Gmin ~ 1, data = data_generalist)
M1_generalist <- lm(Gmin ~Species + TWI, data = data_generalist) #meme pente pour tout le monde

anova(MO_generalist, M1_generalist)

#on peut rejetter l'hypothèse H0, il y a au moins un effet du TWI ou de l'espece sur Gmin.

M_complet <- lm(Gmin ~Species + TWI + Species:TWI, data = data_generalist)

anova(M1_generalist, M_complet)

autoplot(M_complet) #tout parait ok, pas trop de structure, pas trop d'effet levier: 58 ?


#plot results

```




# Question 3
**(H3) Generalist species express a higher intraspecific trait variability than specialist species.**

CV : pour quantifier l’ITV : absolute variation of the intraspecific trait with respect to the interspecific mean. 

CV is defined as the ratio of the standard deviation \sigma to the mean , expressed as a percentage. CV is convenient to compare variation of traits among species as it requires no ad hoc assumptions and is unitless. 

# CV
```{r}


cv <- function(traits){
  if(any(is.na(traits)))
    traits=traits[!is.na(traits)]
  N=length(traits)
  y_bar=mean(traits)
  s2_hat=var(traits)
  cv_2=s2_hat/y_bar^2
  cv_1=sqrt(cv_2)
  gamma_1=sum(((traits-y_bar)/s2_hat^0.5)^3)/N
  gamma_2=sum(((traits-y_bar)/s2_hat^0.5)^4)/N
  bias=cv_2^(3/2)/N*(3*cv_2^0.5-2*gamma_1)
  bias2=cv_1^3/N-cv_1/4/N-cv_1^2*gamma_1/2/N-cv_1*gamma_2/8/N
  cv1=sd(traits)/mean(traits)
  cv4=cv_1-bias2
  re=cv4
  return(list(cv= re, eff = N))
} 


# For generalists



  
cv_G <- sub_data_G %>% 
  group_by(Name) %>% 
  summarise_at(c("Gmin","TLP", "LSWC", "MajVLA", "LA", "K", "C", "N", "P"), funs(cv))

cv_G <- bind_rows(cv_G,
                ungroup(cv_G) %>% 
                  summarise_all(mean) %>% 
                  mutate(Name = "mean")) 

cv_long_G <- reshape2::melt(cv_G, "Name", variable.name = "trait", value.name = "CV")

cv_long_G$Type <- c("Generalist")

cv_long_G %>%  
  filter(Name != "mean") %>% 
  ggplot(aes(x = trait, y = CV)) +
  geom_boxplot() +
  geom_jitter(aes(col = Name), size=3) +
  geom_text(aes(label = paste0(round(CV, 2)*100, "%")), y = 1.25, col = "black",
            data = filter(cv_long_G, Name == "mean")) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text()) +
  ylab("Coefficient of variation") +
  scale_color_discrete("") +
  scale_x_discrete(labels = scales::label_parse())


# For TF specialist


cv_TF <- sub_data_TF %>% 
  group_by(Name) %>% 
  summarise_at(c("Gmin","TLP", "LSWC", "MajVLA", "LA", "K", "C", "N", "P"), funs(cv))

cv_TF <- bind_rows(cv_TF,
                ungroup(cv_TF) %>% 
                  summarise_all(mean) %>% 
                  mutate(Name = "mean")) 

cv_long_TF <- reshape2::melt(cv_TF, "Name", variable.name = "trait", value.name = "CV")

cv_long_TF$Type <- c("TF")

cv_long_TF%>% 
  filter(Name != "mean") %>% 
  ggplot(aes(x = trait, y = CV)) +
  geom_boxplot() +
  geom_jitter(aes(col = Name), size=3) +
  geom_text(aes(label = paste0(round(CV, 2)*100, "%")), y = 1.25, col = "black",
            data = filter(cv_long_TF, Name == "mean")) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text()) +
  ylab("Coefficient of variation") +
  scale_color_discrete("") +
  scale_x_discrete(labels = scales::label_parse())
 

# For BF specialist

cv_BF <- sub_data_SF %>% 
  group_by(Name) %>% 
  summarise_at(c("Gmin","TLP", "LSWC", "MajVLA", "LA","K", "C", "N", "P"), funs(cv))

cv_BF <- bind_rows(cv_BF,
                ungroup(cv_BF) %>% 
                  summarise_all(mean) %>% 
                  mutate(Name = "mean")) 

cv_long_BF <- reshape2::melt(cv_BF, "Name", variable.name = "trait", value.name = "CV") 

cv_long_BF$Type <- c("BF")

 cv_long_BF%>%  
  filter(Name != "mean") %>% 
  ggplot(aes(x = trait, y = CV)) +
  geom_boxplot() +
  geom_jitter(aes(col = Name), size=3) +
  geom_text(aes(label = paste0(round(CV, 2)*100, "%")), y = 1.25, col = "black",
            data = filter(cv_long_BF, Name == "mean")) +
  theme(axis.title.x = element_blank(), axis.text.x = element_text()) +
  ylab("Coefficient of variation") +
  scale_color_discrete("") +
  scale_x_discrete(labels = scales::label_parse())


cv_tot <- bind_rows(cv_long_G, cv_long_BF, cv_long_TF)


```


## graphs all
```{r}
# plot all 
cv_tot %>% mutate(CV =CV*100)%>%
  filter(Name != "mean") %>% 
  filter(CV>0)%>%
  ggplot(aes(x = trait, y = CV, fill = Type, alpha=0.4)) +
  #scale_color_manual(values = c("Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Protium_opacum subsp. rabelianum"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE","Casearia_javitensis" ="#b58404", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Vouacapoua_americana"="#b58404", "Bocoa_prouacensis"="#34e042", "Eschweilera_coriacea"="#34e042", "Conceveiba_guianensis"="#34e042", "Virola_michelii"="#34e042", "Protium_stevensonii"="#34e042", "Hymenopus_heteromorphus"="#34e042", "Jacaranda_copaia subsp. copaia"="#34e042"))+
  geom_jitter() + 
  geom_boxplot(alpha=0.7)+
  scale_fill_manual("Habitat\npreference", values = c("#6DB4EE", "#34e042",  "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  ggtitle("Coefficient of variation %")+
  theme(axis.title.x = element_blank(), axis.text.x = element_text())+
  theme(plot.title = element_text(size=14, face="bold")) +
  ylab("") + xlab("")+
    theme_minimal()

# Anova on CV
#We want to know if there is any significant difference between the average cv for each trait for the three habitat preferences.

kruskal.test(CV ~ Type, data = cv_tot)

cv_tot2<- cv_tot %>% filter(Name != "mean") %>% select(-Name) %>% filter(trait =="TLP")
View(cv_tot2)

pairwise.wilcox.test(cv_tot2$CV, cv_tot2$Type,
                 p.adjust.method = "BH")


#nothing is significant except for LSWC: BF and Generalists
```


## gmin graph

```{r}
cv_tot %>% mutate(CV =CV*100)%>%
  filter(Name != "mean") %>% 
  filter(trait == "Gmin") %>% 
  ggplot(aes(x = trait, y = CV, fill = Type))+
  geom_jitter() + 
  geom_boxplot(alpha=0.7)+
  scale_fill_manual("Habitat\npreference", values = c("#6DB4EE", "#34e042",  "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  ggtitle("Coefficient of variation %")+
  theme(axis.title.x = element_blank(), axis.text.x = element_text())+
  theme(plot.title = element_text(size=14, face="bold")) +
  ylab("") + xlab("")+
    theme_minimal()

cv_tot_gmin <- cv_tot %>% filter(trait == "Gmin")

M_CV <- lm(CV ~ Type, data = cv_tot_gmin, weights = nbre_esp) # mettre un poids car cv n'a pas ete calculer pour meme individu par espece par trait.
summary(M_CV)

M_CV_0 <- lm(CV ~1, data=cv_tot_gmin)
anova(M_CV_0, M_CV)

```


