---
title: "Boxplots"
author: "Marion Boisseaux"
date: "13/09/2022"
output: html_document
---


# Libraries

```{r}
library(tidyverse)
library(dplyr)
library(ggfortify)
library(dplyr)
library(factoextra)
library(FactoMineR)
library(Factoshiny)
library(corrplot) 
library(ggpubr)
library(ggfortify)
library(agricolae)
library(rstatix)
library(kableExtra)
library(V.PhyloMaker)
library(ggfortify)
library(ggtree)
library(readxl)
library(lme4)
library(ggeffects) #draw plots of models
library(nlme)
library(sjPlot) #for plotting lmer and glmer mods
library(gridExtra)
library(rio)
library(multcomp) #for lmer model to do anovas
library(lmerTest) #same
library(emmeans)#same
library(ggplotify)
```

# Data

```{r Data_results, message=FALSE, warning=FALSE}

# dat
library(googleAuthR)
library(googledrive)
library(googlesheets4)
gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets.readonly" )

Metradica_log <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica") %>% dplyr::select(Code, Genus, Species, Name, Habitat, Type, HabitatType, Forest, Gmin, TLP, LA, SLA, LSWC, MajVLA, K, P, C, N, MidribWidth, SecundaryWidth, DBH, TWI) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth", "K", "P", "C", "N"), abs) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth", "TWI","K", "P", "C", "N"), log) %>% 
  mutate(TLP = -TLP) %>% 
  na.omit() 

sub_data_TF <- Metradica_log %>%
  filter(Name %in% c("Dicorynia_guianensis", "Iryanthera_sagotiana", "Gustavia_hexapetala", "Licania_membranacea", "Poraqueiba_guianensis", "Virola_michelii"))

sub_data_SF <- Metradica_log %>%
  filter(Name %in% c("Eperua_falcata", "Iryanthera_hostmannii", "Laetia_procera", "Pterocarpus_officinalis", "Symphonia_globulifera", "Virola_surinamensis"))

sub_data_G <-  Metradica_log %>%
  filter(Name %in% c("Bocoa_prouacensis", "Conceveiba_guianensis", "Jacaranda_copaia subsp. copaia"))

sub_data <- bind_rows(sub_data_TF, sub_data_SF, sub_data_G)

Metradica <- sub_data

```

## Specialist data
```{r}
Metradica$Type <- as.character(Metradica$Type)
Metradica$Name <- as.character(Metradica$Name)
Metradica <- Metradica %>% mutate(Type= ifelse(Name == 'Virola_michelii','TF',Type))

data <- Metradica %>% filter(Type !="Generalist")

```

## gmin 
```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)

model_gmin1 <- lmer(Gmin ~ Type + (1|Forest/Type/Name), data=data) 

summary(model_gmin1)


#Check normality of residuals 

plot(model_gmin) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.

#pour lmer
str(model_gmin)
model_gmin #you access the lmer objects through@
resid(model_gmin)
hist(resid(model_gmin), main = "Residual Histogram")
boxplot(resid(model_gmin), main="Residual Box Plot")
qqnorm(resid(model_gmin)) 
qqline(resid(model_gmin))

#plot
sjPlot::plot_model(model_gmin1)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_gmin1, 
                   axis.labels=c("TF Specialists"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on Gmin")


#anova
#summary(glht(model_gmin, linfct = mcp(Type = "Tukey")), test = adjusted("holm"))

emmeans(model_gmin1, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats_gmin<- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Subset") %>% filter(Trait == 'Gmin') 
  
#plot 

gmin.summary <- aggregate(Gmin ~ Type, mean, data=data)
gmin <- ggplot(data,aes(x=Type,y=Gmin, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=gmin.summary, aes(ymin = Gmin, ymax = Gmin),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(gmin~(mmol.m^-2~.s^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20)) # + 
  #stat_pvalue_manual(stats_gmin, label = "p.adj.signif",
                       y.position = c(5), hide.ns = TRUE)
gmin

#plot raw 


ggplot(data, aes(x = Type, y = Gmin)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(Gmin)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  

```

## TLP
```{r}

# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_tlp <- lmer(TLP ~ Type + (1|Forest/Type/Name), data=data) #so better to use it like that, simpler
summary(model_tlp)


#Check normality of residuals 

plot(model_tlp) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_tlp)
model_tlp #you access the lmer objects through@
resid(model_tlp)
hist(resid(model_tlp), main = "Residual Histogram")
boxplot(resid(model_tlp), main="Residual Box Plot")
qqnorm(resid(model_tlp)) 
qqline(resid(model_tlp))

#plot
sjPlot::plot_model(model_tlp)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_tlp, 
                   axis.labels=c("TWI"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of TWI on TLP")


#anova
summary(glht(model_tlp, linfct = mcp(Type = "Tukey")), test = adjusted("holm"))

emmeans(model_tlp, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'TLP')
  
#plot 
tlp.summary <- aggregate(TLP ~ Type, mean, data=data)
tlp <- ggplot(data,aes(x=Type,y=TLP, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=tlp.summary, aes(ymin = TLP, ymax = TLP),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(TLP~(MPa))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))  + 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(5), hide.ns = TRUE)

#plot raw 


ggplot(data, aes(x = Type, y = TLP)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(TLP)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
  
```

## LSWC 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_lswc <- lmer(LSWC ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_lswc)

model_lswc2 <- lm(LSWC ~ Type, data=data) 
#Check normality of residuals 

plot(model_lswc) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_lswc)
model_lswc #you access the lmer objects through@
resid(model_lswc)
hist(resid(model_lswc), main = "Residual Histogram")
boxplot(resid(model_lswc), main="Residual Box Plot")
qqnorm(resid(model_lswc2)) 
qqline(resid(model_lswc2))

#plot
sjPlot::plot_model(model_lswc)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_lswc, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on LSWC")


#tukey

emmeans(model_lswc, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'LSWC')


#plot 

LSWC.summary <- aggregate(LSWC ~ Type, mean, data=data)
LSWC <- ggplot(data,aes(x=Type,y=LSWC, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=LSWC.summary, aes(ymin = LSWC, ymax = LSWC),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(LSWC~(g.g^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(1.2), hide.ns = TRUE)

LSWC
#plot raw 


ggplot(data, aes(x = Type, y = LSWC)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(LSWC)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
```

## MajVLA 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)

model_majvla <- lmer(MajVLA ~ Type + (1|Forest/Habitat/Name), data=data) 
summary(model_majvla)


#Check normality of residuals 

plot(model_majvla) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_majvla)
model_majvla #you access the lmer objects through@
resid(model_majvla)
hist(resid(model_majvla), main = "Residual Histogram")
boxplot(resid(model_majvla), main="Residual Box Plot")
qqnorm(resid(model_majvla)) 
qqline(resid(model_majvla))

#plot
sjPlot::plot_model(model_majvla)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_majvla, 
                   #axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on MajVLA")


#tukey

emmeans(model_majvla, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'MajVLA')

MajVLA.summary <- aggregate(MajVLA ~ Type, mean, data=data)
MajVLA <- ggplot(data,aes(x=Type,y=MajVLA, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=MajVLA.summary, aes(ymin = MajVLA, ymax = MajVLA),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(MajVLA~(mm.mm^-2))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(2.9), hide.ns = TRUE)
MajVLA
#plot raw 


ggplot(data, aes(x = Type, y = MajVLA)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(MajVLA)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
  
```

## LA 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_la <- lmer(LA ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_la)


#Check normality of residuals 

plot(model_la) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately flat and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_la)
model_la #you access the lmer objects through@
resid(model_la)
hist(resid(model_la), main = "Residual Histogram")
boxplot(resid(model_la), main="Residual Box Plot")
qqnorm(resid(model_la)) 
qqline(resid(model_la))

#plot
sjPlot::plot_model(model_la)
# Notes: axis labels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_la, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on LA")


#tukey

emmeans(model_la, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'LA')
LA.summary <- aggregate(LA ~ Type, mean, data=data)
LA <- ggplot(data,aes(x=Type,y=LA, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=LA.summary, aes(ymin = LA, ymax = LA),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(LA~(cm²))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(5.5), hide.ns = TRUE)
LA

#plot raw 


ggplot(data, aes(x = Type, y = LA)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(LA)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## SLA 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_SLA <- lmer(SLA ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_SLA)


#Check normality of residuals 

plot(model_SLA) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_SLA)
model_SLA #you access the lmer objects through@
resid(model_SLA)
hist(resid(model_SLA), main = "Residual Histogram")
boxplot(resid(model_SLA), main="Residual Box Plot")
qqnorm(resid(model_SLA)) 
qqline(resid(model_SLA))

#plot
sjPlot::plot_model(model_SLA)
# Notes: axis SLAbels should be in order from bottom to top. 
# To see the values of the effect size and p-value, set show.values and show.p= TRUE. Pvalues will only be shown if the effect size values are too

sjPlot::plot_model(model_SLA, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on SLA")


#tukey

emmeans(model_SLA, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'SLA')

SLA.summary <- aggregate(SLA ~ Type, mean, data=data)
SLA <- ggplot(data,aes(x=Type,y=SLA, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=SLA.summary, aes(ymin = SLA, ymax = SLA),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", size=14, angle=0, color = c("#6DB4EE", "#b58404" )))+  
  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +  
  ylab(expression(SLA~(cm^2.g^-1))) + 
  theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))

SLA

#plot raw 


ggplot(data, aes(x = Type, y = SLA)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(SLA)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## K 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_K <- lmer(K ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it like that, simpler
summary(model_K)


#Check normality of residuals 

plot(model_K) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_K)
model_K #you access the lmer objects through@
resid(model_K)
hist(resid(model_K), main = "Residual Histogram")
boxplot(resid(model_K), main="Residual Box Plot")
qqnorm(resid(model_K)) 
qqline(resid(model_K))

#plot

sjPlot::plot_model(model_K, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on K")


#tukey

emmeans(model_K, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'K')

K.summary <- aggregate(K ~ Type, mean, data=data)
K <- ggplot(data,aes(x=Type,y=K, col=Name)) + 
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE","Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE",  "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=K.summary, aes(ymin = K, ymax = K),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(K~(g.kg^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(3.2), hide.ns = TRUE)

K
#plot raw 


ggplot(data, aes(x = Type, y = K)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(K)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## P 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_P <- lmer(P ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_P)


#ChecP normality of residuals 

plot(model_P) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_P)
model_P #you access the lmer objects through@
resid(model_P)
hist(resid(model_P), main = "Residual Histogram")
boxplot(resid(model_P), main="Residual Box Plot")
qqnorm(resid(model_P)) 
qqline(resid(model_P))

#plot

sjPlot::plot_model(model_P, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on P")


#tuPey

emmeans(model_P, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'P')

P.summary <- aggregate(P ~ Type, mean, data=data)
P <- ggplot(data,aes(x=Type,y=P, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=P.summary, aes(ymin = P, ymax = P),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(P~(g.kg^-1))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(0.5), hide.ns = TRUE)
P

#plot raw 


ggplot(data, aes(x = Type, y = P)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(P)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## C 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_C <- lmer(C ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_C)


#ChecP normality of residuals 

plot(model_C) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_C)
model_C #you access the lmer objects through@
resid(model_C)
hist(resid(model_C), main = "Residual Histogram")
boxplot(resid(model_C), main="Residual Box Plot")
qqnorm(resid(model_C)) 
qqline(resid(model_C))

#plot

sjPlot::plot_model(model_C, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on C")


#tuPey

emmeans(model_C, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'C')

C.summary <- aggregate(C ~ Type, mean, data=data)
C <- ggplot(data,aes(x=Type,y=C, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=C.summary, aes(ymin = C, ymax = C),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(C~("%"))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(4.1), hide.ns = TRUE)

C

#plot raw 


ggplot(data, aes(x = Type, y = C)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(C)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

## N 

```{r}
# Global test

data$Name <- as.factor(data$Name)
data$Type <- as.factor(data$Type)
model_N <- lmer(N ~ Type + (1|Forest/Habitat/Name), data=data) #so better to use it liPe that, simpler
summary(model_N)


#ChecP normality of residuals 

plot(model_N) #For the normality assumption to hold, the residuals should spread randomly around 0 and form a horizontal band.If the red trend line is approximately fSLAt and close to zero, then one can assume that the residuals are normally distributed.


#pour lmer
str(model_N)
model_N #you access the lmer objects through@
resid(model_N)
hist(resid(model_N), main = "Residual Histogram")
boxplot(resid(model_N), main="Residual Box Plot")
qqnorm(resid(model_N)) 
qqline(resid(model_N))

#plot

sjPlot::plot_model(model_N, 
                   axis.labels=c("Specialist TF"),
                   show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on N")


#tuPey

emmeans(model_N, list(pairwise ~ Type), adjust = "tukey")

#Adding the emmeans to a google sheet the results

stats <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/19VX7hTNn64D6G-HSF1b2L9JTMrf2UIfvL5jEhWyf6Ko/edit#gid=0", range = "Sheet1") %>% filter(Trait == 'N')

N.summary <- aggregate(N ~ Type, mean, data=data)
N <-ggplot(data,aes(x=Type,y=N, col=Name)) +
   scale_color_manual(values = c("Eperua_falcata" = "#6DB4EE", "Iryanthera_hostmannii"= "#6DB4EE", "Laetia_procera"= "#6DB4EE", "Pterocarpus_officinalis"= "#6DB4EE", "Symphonia_globulifera"= "#6DB4EE", "Virola_surinamensis"= "#6DB4EE", "Dicorynia_guianensis"="#b58404", "Iryanthera_sagotiana"="#b58404", "Gustavia_hexapetala"="#b58404", "Licania_membranacea"="#b58404", "Poraqueiba_guianensis"="#b58404", "Virola_michelii"="#b58404"))+ 
  #geom_jitter() + 
  geom_boxplot(alpha=0.2) + 
  geom_crossbar(data=N.summary, aes(ymin = N, ymax = N),
                  size=1,col="red", width = .5)+
  theme(axis.text.x = element_text(face="bold", 
                           size=12, angle=0, color = c("#6DB4EE", "#b58404" )))+  scale_x_discrete(name =c(""), labels = c("BF" = "SF specialist","TF" = "TF specialist")) +   ylab(expression(N~("%"))) + theme(axis.text.y = element_text(face="bold", size=12), axis.title.y = element_text(size = 20))+ 
  stat_pvalue_manual(stats, label = "p.adj.signif",
                       y.position = c(1.2), hide.ns = TRUE)
N

#plot raw 


ggplot(data, aes(x = Type, y = N)) +
geom_boxplot() +
geom_jitter(aes(colour= Name)) +
labs(x = "Habitat Preference", y = "Log(N)")+ scale_x_discrete("Habitat Preference", labels = c("BF" = "SF specialist","TF" = "TF specialist"))
```

#Summary

```{r}
# install.packages("devtools")
devtools::install_github("thomasp85/patchwork")
library(patchwork)

(gmin | tlp | LSWC)/(LA | SLA | MajVLA)/(K | P | C | N ) + plot_layout(guides = "collect")
```


# Model 1 

Trait ~ Type + (1|Forest/Habitat/Name)

Fixed effet of habitat preference and nested random effect of species within each habitat, and the habitats nested in the 3 forest sites.

There is an error with this model : **boundary (singular) fit: see help('isSingular')** which means that there are not enough foresst sites to put it as random.

```{r}

name_list <- NULL
Nbcol <- match(colnames(data)[9:18],colnames(data)) 
count <- 0
for ( i in data[,Nbcol]){
  count <-  count + 1
  name <- names(data[Nbcol[count]])
 
  #write the formula
  formu <- formula(paste(name,"~Type + (1|Forest/Habitat/Name)"))
 
  # Create the graphz
  Scale_loc <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      sqrt(abs(resid(.)))~fitted(.),
      type=c("p","smooth"),
      col.line=1,
      xlab=paste0("Fitted  ",name),
      ylab=expression(sqrt("Standardized residuals")))
    )
 

  QQ <- as.ggplot(
    lattice::qqmath(
      lmer(formula=formu,data=data))
      )
   
 
  Res_Fit <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      type=c("p","smooth"),
      col.line = 1),
      xlab=paste0("Fitted  ",name),
      ylab=expression(sqrt("Residuals"))
    )
 
  Res_lev <- as.ggplot(
    plot(
      lmer(formula=formu,data=data),
      rstudent(.)~hatvalues(.),
      xlab=paste0("Leverage  ",name),
      ylab=expression(sqrt("Residuals"))
     
      )
    )
 
  # Save them
  plot <- arrangeGrob(Res_Fit,
                      QQ,
                      Scale_loc,
                      Res_lev,
                      ncol = 2,
                      nrow = 2)
 
  ggsave(plot,
         filename=paste0("lmer_diagnostic_",name,".jpg"),
         device = "jpg",
         path = "./Results/Model/Model_1/Subset/Diag",
         width = 7,
         height = 9,
         units = "in")
 
  name_list <- c(name_list,name)
  
  #plot model
   print(sjPlot::plot_model(lmer(formula=formu,data=data), axis.labels=c("Specialist TF"), show.values=TRUE, show.p=TRUE,
                   title="Effect of habitat preference on N",
         file=paste0("./Results/Model/Model_1/Subset/Plot/",name,".jpeg")))
   
  # Create an html summary table
  print(sjPlot::tab_model(lmer(formula=formu,data=data),file=paste0("./Results/Model/Model_1/Subset/Table/",name,".html")
                          )
        )
  # # convert it to png
  # webshot::webshot(paste0("./Results/Boxplot/Subset/Table/",name,".html"),
  #         paste0("./Results/Boxplot/Subset/Table/",name,".png")
  #         )
}
```

Plot everything together

```{r}

model_gmin1 <- lmer(Gmin ~ TWI + (1|Name), data= data)

mydata$model_gmin1_predicted <- predict(model_gmin1)

ggplot(data, aes(x = Type, y = Gmin, colour = Type)) +
      facet_wrap(~Forest, ncol=3) +   # a panel for each mountain range
      geom_boxplot(alpha = 0.5) +
      theme_classic() +
      #geom_line(data = cbind(data, pred = predict(model_gmin1)), aes(y = pred), size = 1) +  # adding predicted line from mixed model 
  # geom_smooth(method = "lm", se = FALSE) thisis the predicted line comapring only the chosen variables
      theme(legend.position = "none",
            panel.spacing = unit(2, "lines"))  # adding space between panels

```


# Model 2

Every habitat belong to only one forest. = NESTED

Every habitat TF (TF1, TF2, TF3) has species1, species2, species3. = CROSSED
Every habitat BF (BF1, BF2, BF3) has species4, species5, species6.


