---
title: "Species habitat preferences"
author: "Marion Boisseaux"
date: "20/02/2022"
output: html_document
---
Habitat associations
In this study, I have categorised each species as associated with *terra firme*, seasonnally flooded habitat, or neither based on the density of stems per hectare in each habitat (abundance data from the 2020 Paracou regeneration survey). These simple 
categorisations broadly agree with previous studies of habitat associations for these 
species and these habitats in Paracou (Baraloto et al. 2007, Allie et al. 2015). 

# Caluclating species abundances in each habitat



Abundance: dividing the number of species from one group by the total number of species from all groups.  

```{r}

library(readr)
library(readxl)
library(dplyr)
library(tidyverse)

# import paracou database 20210830

Paracou <- read_csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/Metradica_Paracou/Document/Paracou_database20210830.csv")
Paracou <- Paracou %>% unite("GS", Genus:Species)

# import my species


MySpecies <- read_excel("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/Divers/Scoffoni/Species.xlsx")

MySpecies <- MySpecies %>% unite("GS", Genus:Species)


```

# import shapefiles

```{r}
library(rgdal)
library(ggplot2)
library(sf)
library(leaflet)
library(RColorBrewer) #for colors
library(tidyverse)
library(dplyr)

#import shapefile - plots

Plots <- readOGR(dsn = "./SIG",layer = "OverallPlots")
Plots <- spTransform(Plots, CRS("+proj=longlat +datum=WGS84")) 


# Subset only Paracou parcelles object
Plots_sub <- Plots[Plots$Project %in% c("ParacouCIRAD"), ]

Plots_sub2 = subset(Plots_sub, Plot=="1" & Plot=="2")

Plots_sub[Plots_sub$Plot >= "1" & Plots_sub$Plot <= "16", ]

plot(Plots_sub)

#import shapefile - topography

Topo <- readOGR(dsn = "./SIG",layer = "TopographicLevels")
Topo <- spTransform(Topo, CRS("+proj=longlat +datum=WGS84")) 


plot(Topo)

palSp <- colorFactor("viridis", MySpecies$GS)
limits <- st_read("./SIG/OverallPlots.shp", quiet = T)
leaflet(data = st_transform(MySpecies, crs = crs)) %>%
  addTiles() %>% 
  addPolylines(data = st_transform(limits, crs = crs), col = "grey") %>% 
  addCircles(color = ~palSp(GS), opacity = 1,
             label = ~ GS, radius = ~ DBH/5) %>% 
  addLegend(pal = palSp, values = ~ GS)



```


