---
title: "Climatic data in Guyane"
output:
 bookdown::html_document2:
  #base_format: rmarkdown::html_vignette
  #highlight: tango
  number_sections: true
  toc: true
  toc_float: true
  fig_caption: yes
link-citations: yes
date: '2022-06-13'
---

# Load librairies 

```{r librairies }
# Libraries
library(glue)
library(sf)
library(stars)
library(rgdal)
library(rgrass7)
## Define the working directory as the folder where is saved this .Rmd file
setwd(paste0(dirname(rstudioapi::getSourceEditorContext()$path)))
```

# French Guiana's border and extent  

```{r borders-extent, eval=FALSE}
## folder for the country's borders and extent 
dir.create(paste0(getwd(),"/borders"))

# Function to get the area's extent from GADM version 3.6 (https://gadm.org/download_country36.html)
get_extent <- function(ISO_country_code, EPSG,
                       area_borders=NULL,
                       verbose=TRUE, write=TRUE){
  
  if(is.null(area_borders)){
    URL <- paste0("https://geodata.ucdavis.edu/gadm/gadm3.6/gpkg/gadm36_", ISO_country_code, "_gpkg.zip")
    # Download file
    # The coordinate reference system is longitude/latitude and the WGS84 datum.
    download.file(URL, quiet = !verbose, method="auto",
                  paste0(getwd(), "/borders/gpkg_gadm36_", ISO_country_code, ".zip"))
  # Unzip 
  unzip(paste0(getwd(), "/borders/gpkg_gadm36_", ISO_country_code, ".zip"),
        exdir=paste0(getwd(), "/borders"), overwrite=TRUE)
  # Remove zip file
  file.remove(paste0(getwd(), "/borders/gpkg_gadm36_", ISO_country_code, ".zip"))
  # Read vector (level 0 for country borders)
  borders <- sf::st_read(paste0(getwd(), "/borders/gadm36_", ISO_country_code, ".gpkg"),
                         layer=paste0("gadm36_", ISO_country_code, "_0"), quiet=!verbose)
  } else{
  borders <- area_borders  
  }
  crs_borders <- st_crs(borders)
  bb_ll <- st_bbox(borders, crs=crs_borders)
  bb_utm <- bb_ll %>%
    st_as_sfc() %>%
    st_transform(crs=EPSG) %>%
    st_bbox()
  
  # Bounding box for French Guiana
  xmin <- as.integer((floor(bb_utm$xmin/1000)-5)*1000)
  xmax <- as.integer((ceiling(bb_utm$xmax/1000)+5)*1000)
  ymin <- as.integer((floor(bb_utm$ymin/1000)-5)*1000)
  ymax <- as.integer((ceiling(bb_utm$ymax/1000)+5)*1000)
  
  # Print extent with description (xmin, ymin, xmax, ymax)
  msg <- paste0("Extent of ", ISO_country_code," in EPSG:", EPSG)
  extent <- glue("xmin: {xmin}, ymin: {ymin}, xmax: {xmax}, ymax: {ymax}")
  if(write){writeLines(c(msg, extent), paste0(getwd(), "/borders/extent.txt"))}
  
  # Print extent (xmin, ymin, xmax, ymax)
  extent <- glue("{xmin} {ymin} {xmax} {ymax}")
  if(write){writeLines(extent, paste0(getwd(), "/borders/extent_short.txt"))}
  
return(c(xmin, ymin, xmax, ymax))
}

# Get extent of French Guiana 
# with a projection: unit=m, EPSG=32622
ISO_country_code <- "GUF"
EPSG <- 32622
Extent <- get_extent(ISO_country_code, EPSG,
                     write=TRUE, verbose=TRUE)
nodat <- -32767
```

# Topographic water index (TWI)

## Elevation 

### Download elevation data 

```{r download-elevation, eval=FALSE}
## folder for elevation data with 90m resolution
dir.create(paste0(getwd(),"/srtm_v1_4_90m"))
## folder for elevation data with 30m resolution
dir.create(paste0(getwd(),"/srtm_v1_4_30m"))

#====== Elevation #======
# SRTM at 90m resolution from https://dwtkns.com/srtm/ version 4.1
## Download and unzip CGIAR-CSI 90m DEM data
# Function to get tiles number of srtm to download
tiles_srtm <- function(extent_latlong){
  # Compute lat/long tiles for SRTM data from an extent.
  # This function computes lat/long tiles for SRTM data from an extent
  # in lat/long. See `<http://dwtkns.com/srtm/>`_. SRTM tiles are 5x5
  # degrees. x: -180/+180, y: +60/-60.
  # :param extent_latlong: Extent in lat/long: (xmin, ymin, xmax, ymax).
  # :return: A tuple of two strings indicating tile numbers for lat and long.
  
  # Tiles for SRTM data
  xmin_latlong = floor(extent_latlong[1])
  ymin_latlong = floor(extent_latlong[2])
  xmax_latlong = ceiling(extent_latlong[3])
  ymax_latlong = ceiling(extent_latlong[4])
  # Compute SRTM tile numbers
  tile_left = as.integer(ceiling((xmin_latlong + 180.0) / 5.0))
  tile_right = as.integer(ceiling((xmax_latlong + 180.0) / 5.0))
  if (tile_right == tile_left){
    # Trick to make curl globbing work in data_country.sh
    tile_right = tile_left + 1
  }
  tile_top = as.integer(ceiling((-ymax_latlong + 60.0) / 5.0))
  tile_bottom = as.integer(ceiling((-ymin_latlong + 60.0) / 5.0))
  if (tile_bottom == tile_top){
    tile_bottom = tile_top + 1
  }
  tiles_long = c(tile_left, tile_right)
  tiles_lat = c(tile_top, tile_bottom)
  return(list(long = tiles_long, lat=tiles_lat))
}

# French Guiana borders in latlong
ISO_country_code <- "GUF"
borders <- sf::st_read(paste0(getwd(), "/borders/gadm36_", ISO_country_code, ".gpkg"),
                       layer=paste0("gadm36_", ISO_country_code, "_0"))
plot(borders$geom, axes=TRUE)
extent_latlong <- st_bbox(borders, crs=4326)
# Get tiles number to download given the French Guiana extent
tiles <- tiles_srtm(extent_latlong)
# Format tiles, str_pad is for having 01 and not 1 values
tiles <- paste(stringr::str_pad(rep(tiles$long[1]:tiles$long[2],
                                    each=length(tiles$lat[1]:tiles$lat[2])),
                                width=2, pad="0"), 
               stringr::str_pad(tiles$lat[1]:tiles$lat[2], width=2, pad="0"), sep="_")
#tiles <- c("26_11","26_12")

# Download SRTM from https://dwtkns.com/srtm/ version 4.1
for (i in 1:length(tiles)) {
  dst <- paste0(paste0(getwd(), "/srtm_v1_4_90m/srtm_"), tiles[i],".zip")
  url.tile <- paste0("https://srtm.csi.cgiar.org/wp-content/uploads/files/srtm_5x5/TIFF/srtm_",
                     tiles[i],".zip")
  download.file(url=url.tile, destfile=dst, method="auto", quiet=TRUE)
  unzip(dst, exdir=paste0(getwd(),"/srtm_v1_4_90m"), overwrite=TRUE)
}
# remove zip files 
srtm.zip <- list.files(paste0(getwd(),"/srtm_v1_4_90m"), pattern=".zip", full.names=TRUE)
file.remove(srtm.zip)

## Combine the srtm_tiles.tif files downloaded in one map of elevation
destfile <- paste0(getwd(), "/srtm_v1_4_90m/elevation.vrt")
sourcefiles <- paste0(getwd(), "/srtm_v1_4_90m/srtm_", tiles, ".tif")
files.txt <- paste0(getwd(), "/srtm_v1_4_90m/files.txt")
# write in files.txt the sourcefiles path for srtm_tiles.tif 
writeLines(sourcefiles, files.txt)
# Mosaic with gdalbuildvrt 
system(glue("gdalbuildvrt {destfile} -input_file_list {files.txt}"))

# SRTM at 30m resolution from https://dwtkns.com/srtm30m/ version 4.1
## Create a free account and login to EOSDIS Earthdata 
## click to download all tiles of French Guiana
## Unzip CGIAR-CSI 30m DEM data
srtm.zip <- list.files(path=paste0(getwd(), "/srtm_v1_4_30m"),
                        pattern=".zip", full.names = TRUE)
for (i in 1:length(srtm.zip)) {
  unzip(srtm.zip[i], exdir=paste0(getwd(),"/srtm_v1_4_30m"), overwrite=TRUE)
}
# remove zip files 
file.remove(srtm.zip)

## Combine the srtm_tiles.hgt files downloaded in one map of elevation
sourcefiles <- list.files(path=paste0(getwd(), "/srtm_v1_4_30m"),
                          pattern=".hgt", full.names = TRUE)
# write in files.txt the sourcefiles path for srtm_tiles.hgt
files.txt <- paste0(getwd(), "/srtm_v1_4_30m/files.txt")
writeLines(sourcefiles, files.txt)
destfile <- paste0(getwd(), "/srtm_v1_4_30m/elevation.vrt")
# Mosaic with gdalbuildvrt 
system(glue("gdalbuildvrt {destfile} -input_file_list {files.txt} -srcnodata 0 -vrtnodata -32768"))
```

### Reproject elevation map from lat-long to meters (EPSG:32622)

```{r reproject-elevation, eval=FALSE}
## gdalwrap options
Extent <- readLines(paste0(getwd(), "/borders/extent_short.txt"))
# projection of source file (latlong)
proj.s <- "EPSG:4326"
# projection of output file
proj.t <- "EPSG:32622" 
# "EPSG:32622" not legal projection,
# "EPSG:2972" more conventional
## Reproject from lat long to UTM32N (epsg: 32622) and reframe on French Guyana
# (dstnodata need to be set to 32767 as we pass from Int16 (nodata=-32768) to INT2S (nodata=-32767) in R)

# SRTM resolution in m (cells of res x res)
for(res in c("30","90", "1000")){
  if(res==1000){
    sourcefile <- paste0(getwd(), "/srtm_v1_4_90m/elevation.vrt")
    destfile <- paste0(getwd(), "/srtm_v1_4_90m/elevation_1km.tif")
  } else{
    sourcefile <- paste0(getwd(), "/srtm_v1_4_", res, "m/elevation.vrt")
    destfile <- paste0(getwd(), "/srtm_v1_4_", res, "m/elevation.tif")
  }
  system(glue("gdalwarp -overwrite -s_srs {proj.s} -t_srs {proj.t} \\
            -srcnodata -32768 -dstnodata -32767 \\
            -r bilinear -tr {res} {res} -te {Extent} -ot Float64 -of GTiff \\
            {sourcefile} \\
            {destfile}"))
}
```

```{r elev-visualization}
# Elevation visualization and check with border  
ISO_country_code ="GUF"
for(res in c("30","90")){
  elev <- read_stars(paste0(getwd(), "/srtm_v1_4_", res, "m/elevation.tif"))
  border <- sf::st_read(paste0(getwd(), "/borders/gadm36_", ISO_country_code, ".gpkg"),
                        layer=paste0("gadm36_", ISO_country_code, "_0"))
  border <- st_transform(border, crs=st_crs(elev))
  plot(elev, axes=TRUE, reset = FALSE, main=paste0("SRTM ",res, "m"))
  plot(border$geom, add=TRUE, reset=FALSE)
}
```

## Compute TWI from elevation 

To do so we use the function [r.topixd](https://grass.osgeo.org/grass78/manuals/r.topidx.html) from the GRASS GIS software.

```{r compute-TWI, eval=FALSE}
## Initialize GRASS
# Path to grass library and version of grass in your computer
Sys.setenv(LD_LIBRARY_PATH=paste("/usr/lib/grass78/lib", Sys.getenv("LD_LIBRARY_PATH"), sep=":"))
# Use a georeferenced raster
# to define projection and resolution of maps produced
for(res in c("30","90")){
elevation <- paste0(getwd(), "/srtm_v1_4_", res, "m/elevation.tif")
system(glue('grass -c {elevation} grassdata/environ'))
# connect to grass database
initGRASS(gisBase="/usr/lib/grass78", 
          gisDbase="grassdata", home=tempdir(), 
          location="environ", mapset="PERMANENT",
          override=TRUE)
## Import raster in grass
system(glue("r.in.gdal --o input={elevation} output=elevation"))
# Compute radiation
cmd <- glue("r.topidx --o --verbose --overwrite input=elevation output=TWI")
system(cmd)
# Export
system(glue("r.out.gdal -f --overwrite input=TWI \\
  			 output={paste0(getwd(), '/output/TWI_', res, 'm.tif')} type=Float64 format=GTiff \\
  			 createopt='compress=lzw, predictor=2'"))
}
```

```{r TWI-visualization}
# TWI visualization and check with border  
ISO_country_code ="GUF"
for(res in c("30","90")){
TWI<- read_stars(paste0(getwd(), "/output/TWI_", res, "m.tif"))
border <- sf::st_read(paste0(getwd(), "/borders/gadm36_", ISO_country_code, ".gpkg"),
                      layer=paste0("gadm36_", ISO_country_code, "_0"))
border <- st_transform(border, crs=st_crs(TWI))
plot(TWI, axes=TRUE,reset = FALSE)
plot(border$geom, add=TRUE, reset=FALSE)
}
```


# Climatic water deficit (CWD)

##  Download climatic data from Chelsa 
Chelsa v2.1 Website : <https://chelsa-climate.org/>  

References:   

Scientific publication:  Karger, D.N., Conrad, O., Böhner, J., Kawohl, T., Kreft, H., Soria-Auza, R.W., Zimmermann, N.E., Linder, H.P. & Kessler, M. (2017) Climatologies at high resolution for the earth’s land surface areas. Scientific Data 4, 170122. <https://doi.org/10.1038/sdata.2017.122>.

Data citation: Karger, D.N., Conrad, O., Böhner, J., Kawohl, T., Kreft, H., Soria-Auza, R.W., Zimmermann, N.E., Linder, H.P. & Kessler, M. (2021) Climatologies at high resolution for the earth’s land surface areas. EnviDat. <https://doi.org/10.16904/envidat.228.v2.1>

We download the means monthly precipitation($kg/m^2$ equivalent to $mm$ or $L/m^2$) and potential evapotranspiration ($kg/m^2$), calculated with the Penman-Monteith equation, for the period 1981-2010. 

```{r Download-data-from-Chelsa, eval=FALSE}
## Create some directories
dir.create(paste0(getwd(),"/chelsa_v2_1")) ## folder for climatic data

# for(m in stringr::str_pad(1:12, 2, pad = "0")){
for(m in c(paste0('0',1:9),10:12)){
  ## Monthly precipitation (mm ~ kg/m2).
  download.file(paste0('https://os.zhdk.cloud.switch.ch/envicloud/chelsa/chelsa_V2/GLOBAL/climatologies/1981-2010/pr/CHELSA_pr_',
                       m, '_1981-2010_V.2.1.tif'),
                destfile=paste0(getwd(),"/chelsa_v2_1/", "pr_", m,".tif"), method = 'auto')
  
 ## Monthly potential evapotranspiration (mm ~ kg/m2) 
 ## calculated with the Penman-Monteith equation.
  download.file(paste0('https://os.zhdk.cloud.switch.ch/envicloud/chelsa/chelsa_V2/GLOBAL/climatologies/1981-2010/pet/CHELSA_pet_penman_',
                       m,'_1981-2010_V.2.1.tif'),
                destfile=paste0(getwd(), "/chelsa_v2_1/", "pet_", m, ".tif"), method = 'auto')
}
```

## Reproject and reframe climatic data on French Guyana 

```{r reproject-prec-pet, eval=FALSE}
## gdalwrap options
Extent <- readLines(paste0(getwd(), "/borders/extent_short.txt"))
# projection of source file (latlong)
proj.s <- "EPSG:4326"
# projection of output file
proj.t <- "EPSG:32622" 
# Resolution of output file (m)
Res <- 1000
# No data of output file
nodat <- -9999
# Reproject from lat long to UTM32N (epsg: 32622), set resolution to 1km
# Reframe on French Guyana and set no data values in sea
# according to elevation map
elev <- read_stars(paste0(getwd(), "/srtm_v1_4_90m/elevation_1km.tif"))
for(var in c("pr", "pet")){
  files.tif <- list.files(paste0(getwd(), "/chelsa_v2_1"),
                          pattern=var, full.names = TRUE)
  for(i in 1:length(files.tif)){
    sourcefile <- files.tif[i]
    destfile <- gsub(".tif", "_1km.tif", files.tif[i])
    system(glue("gdalwarp -overwrite -s_srs {proj.s} -t_srs {proj.t} \\
        -r bilinear -tr {Res} {Res} -te {Extent} -ot Int16 -of GTiff -srcnodata 0 -dstnodata {nodat} \\
        {sourcefile} \\
        {destfile}"))
  file.remove(sourcefile)
  }
  files.tif <- list.files(paste0(getwd(), "/chelsa_v2_1"), pattern=var, full.names = TRUE)
  r <- read_stars(gtools::mixedsort(files.tif), along="band") 
  # Define no data values out of French Guyana border 
  #borders <- sf::st_read(here("data_raw", "fao_gaul", paste0("gadm36_", ISO_country_code, ".gpkg")),
  #                       layer=paste0("gadm36_", ISO_country_code, "_0"), quiet=!verbose)
  #st_transform(borders, crs=EPSG)
  # st_crop(r, borders)
  # Define no data values in sea according to elevation map 
  r[[1]][is.na(elev[[1]])] <- nodat
  write_stars(obj=r, options = c("COMPRESS=LZW","PREDICTOR=2"), NA_value=nodat,
              dsn=paste0(getwd(), "/chelsa_v2_1/", var,"_1km.tif"))
 file.remove(files.tif)
}
```

## Compute CWD from monthly precipitation and evapotranspiration in French Guiana

The annual climatic water deficit (CWD) in mm, is based on monthly precipitation ($prec$) and potential evapotranspiration ($pet$) which is defined as the amount of evaporation that would occur in a month if a sufficient water source were available: $\mathrm{cwd}= \sum_{m=1}^{12}\min(0, \ \mathrm{prec}_m-\ \mathrm{pet}_m)$.

```{r compute-CWD}
# Function to compute cwd and ndm 
cwd.ndm.f <- function(Prec, Pet){
  nrow <- dim(Prec[,,,1])[1]
  ncol <- dim(Prec[,,,1])[2]
  # initialize
  cwd <- matrix(0, nrow, ncol)
  ndm <- matrix(0,  nrow, ncol)
  # loop on months
  for (i in 1:12){
    cat(paste("Month: ",i,"\n",sep=""))
    pe.diff <- Prec[,,,i]-Pet[,,,i]
    cwd <- cwd + pmin(pe.diff[[1]][,,1], 0.0) # climatic water deficit
    dm <- matrix(0,  nrow, ncol) # dry month
    dm[c(pe.diff[[1]][,,1]<0)] <- 1
    ndm <- ndm+dm
  }
  # make stars object
  CWD <- NDM <- Prec[,,,1]
  CWD[[1]][,,1] <- -cwd
  NDM[[1]][,,1] <- ndm
  NDM[is.na(Pet[,,,1])] <- NA # to account for NA values
  return (list(CWD=CWD,NDM=NDM))
}

# Prec and Pet
Prec <- read_stars(paste0(getwd(), "/chelsa_v2_1/pr_1km.tif"))
Pet <- read_stars(paste0(getwd(), "/chelsa_v2_1/pet_1km.tif"))

# Compute CWD 
results <- cwd.ndm.f(Prec, Pet)
CWD <- results$CWD
write_stars(CWD, paste0(getwd(), "/output/CWD_1km.tif"), options =c("COMPRESS=LZW","PREDICTOR=2"))
# CWD visualization and check with border  
ISO_country_code ="GUF"
CWD <- read_stars(paste0(getwd(), "/output/CWD_1km.tif"))
border <- sf::st_read(paste0(getwd(), "/borders/gadm36_", ISO_country_code, ".gpkg"),
                      layer=paste0("gadm36_", ISO_country_code, "_0"))
border <- st_transform(border, crs=st_crs(CWD))
plot(CWD, axes=TRUE,reset = FALSE)
plot(border$geom, add=TRUE, reset=FALSE)
```

# Extract data at selected coordinates

```{r extract-data}
METRADICA_dataset <- read.csv2(paste0(getwd(),"/Metradica - Metradica.csv"), sep=",", header=TRUE)
# remove NA
rows_na <- which(METRADICA_dataset[,c("Xutm", "Yutm")]=="",
                 arr.ind = TRUE)[,"row"]
dataset <- METRADICA_dataset[-rows_na,]
# Coordinates
xy <- as.matrix(dataset[,c("Xutm", "Yutm")])
# remove comma in numbers 
xy <- matrix(as.numeric(gsub(",", "", xy)), ncol=2)
colnames(xy) <- c("Xutm","Yutm")
# Extract data at selected coordinates 
## CWD resolution 1km 
CWD <- read_stars(paste0(getwd(), "/output/CWD_1km.tif"))
dataset$CWD_1km <- st_extract(x=CWD, at=xy)
METRADICA_dataset[-rows_na, "CWD_1km"] <- dataset$CWD_1km 

## TWI resolution 30m 
TWI <- read_stars(paste0(getwd(), "/output/TWI_30m.tif"))
dataset$TWI_30m <- st_extract(x=TWI, at=xy)
METRADICA_dataset[-rows_na, "TWI_30m"] <- dataset$TWI_30m 

# Visualization of coordinates 
xy <- sf::st_as_sf(data.frame(xy), coords=c("Xutm","Yutm"), crs=32622)
plot(CWD, reset=FALSE, axes=TRUE)
plot(xy, add=TRUE, reset=FALSE, col='red')

# Save csv 
write.csv2(METRADICA_dataset, file=paste0(getwd(), "/METRADICA.csv"))
head(METRADICA_dataset)

# Check with latlong coordinates 
# Xutm	         Yutm	      Latitude	  Longitude
# 286,315.69	583,636.63	5.277200222	-52.92810059
# 286,347.38	583,537.88	5.276299953	-52.92779922
# 286,328.34	583,621.81	5.277100086	-52.9280014
print(xy[1:3,])
print(st_transform(xy[1:3,], crs=4326))
# Check TWI with existing values
par(mfrow=c(1,1))
plot(METRADICA_dataset[657:691,"TWI"],
     METRADICA_dataset[657:691,"TWI_30m"])
# don't match but not same computation method and resolution 

```

# Fitting model 

```{r model}
data <- read.csv2(paste0(getwd(),"/METRADICA.csv"), sep=";", header=TRUE)
data[,c("Gmin", "TLP")] <- lapply(data[,c("Gmin", "TLP")], as.numeric)
# remove NA
data <- data[-is.na(data[,c("Gmin", "TLP")]),]
mod1 <- lm(log(Gmin) ~ CWD_1km, data)
mod2 <- lm(log(Gmin) ~ TWI_30m, data)
# log(TLP) produce NaN (negative values)
mod3 <- lm(TLP ~ CWD_1km, data)
mod4 <- lm(TLP ~ TWI_30m, data)
# summary(mod)
# plot(mod)
```



