---
title: "PCA_MFA"
author: "Marion Boisseaux"
date: "08/09/2022"
output: html_document
---
# Libraries

```{r librairies_results}
library(tidyverse)
library(ggfortify)
library(dplyr)
library(factoextra)
library(FactoMineR)
library(Factoshiny)
library(corrplot) 
library(ggpubr)
library(ggfortify)
library(agricolae)
library(rstatix)
library(kableExtra)
library(V.PhyloMaker)
library(ggfortify)
library(ggtree)
library(readxl)
library(lme4)
library(ggeffects) #draw plots of models
library(nlme)
library(sjPlot) #for plotting lmer and glmer mods
library(gridExtra)
library(rio)
library(vegan)
```

# Data

```{r Data_results, message=FALSE, warning=FALSE}

#not log

Data <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=738111573", range = "Metradica") %>% 
  dplyr::select(Code, Genus, Species, Name, Forest, Habitat, Type, HabitatType, Gmin, TLP, LA, SLA, LSWC, MajVLA, MidribWidth, SecundaryWidth, StomatalDensity, K, P, C, N, TreeHeight, BranchHeight, TreeDawkins, BranchDawkins, DBH, TWI) %>% 
  mutate(TreeHeight = as.numeric(TreeHeight), BranchHeight = as.numeric(BranchHeight)) 

#log
Metradica_log <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1rOl9sZl3A055GTajMcZxrJL_Ozx2bJfM_VEBdcpkD00/edit#gid=1375896520", range = "Metradica") %>% dplyr::select(Code, Genus, Species, Name, Habitat, Type, HabitatType, Forest, Gmin, TLP, LA, SLA, LSWC, MajVLA, K, P, C, N, MidribWidth, SecundaryWidth, DBH, TWI) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth", "K", "P", "C", "N"), abs) %>% 
  mutate_at(c("Gmin","TLP" ,"LA", "SLA", "LSWC", "MajVLA", "MidribWidth", "SecundaryWidth", "TWI","K", "P", "C", "N"), log) %>% 
  mutate(TLP = -TLP) %>% 
  na.omit() 

```

# MFA 

I log-transformed the data to reduce the skewness but checking the normality using shapiro's test was significative (not following normality).

I have variables from different groups:

-Categorical groups : Name of species *Name*; Habitat of collect *habitat*; specialist or generalist behavior *Type*; specifying which type of specialist and where it was collected for the geenralists *HabitatType*; the forest where is was sampled *Forest*

-water related traits: *Gmin*, *TLP*, *LSWC*, *MajVLA*
-morphological leaf traits: *LA*, *SLA*, *MidribWidth*, *SecundaryWidth*, *StomatalDensity*
-Chemistry: *K*, *P*, *C*, *N*
-Tree characteristics: *DBH* , **Dawkins** ?
-Habitat characterization : *TWI*, **CWD**?

```{r}

Data <- Metradica_log %>% dplyr::select(-Code, -Genus, -Species, -Habitat, -Type, -TWI) %>% relocate(LSWC, .after = TLP) %>% relocate(MidribWidth, .after = MajVLA) %>% relocate(SecundaryWidth, .after = MidribWidth)%>% relocate(MajVLA, .after = LSWC)


Data <- Data %>% dplyr::select(-Code, -Genus, -Species, -Habitat, -Type, -TWI) %>% relocate(LSWC, .after = TLP) %>% relocate(MidribWidth, .after = MajVLA) %>% relocate(SecundaryWidth, .after = MidribWidth) %>% relocate(MajVLA, .after = LSWC)

res = MFA(Data, group=c(3,4,4,4,1), type=c("n",rep("s",4)), name.group=c("Identity","Water_related","Carbon_related","Leaf_chemistry", "DBH"), num.group.sup=c(1,5))

fviz_screeplot(res)
fviz_mfa_var(res, "group")

#Metradica_log: the data set used
#group: a vector indicating the number of variables in each group
#type: the type of the variables in each group. "s" for scaled continuous variables, "c" for centered (unscaled) continuous variables and "n" for categorical variables
#ncp: number of dimensions kept in the result
#name.group: names of the groups
#num.group.sup: indexes of the supplementary groups

#red color = active groups of variables
#green color = supplementary groups of variables

# Contribution to the first dimension
fviz_contrib(res, "group", axes = 1)
# Contribution to the second dimension
fviz_contrib(res, "group", axes = 2)

quanti.var <- get_mfa_var(res, "quanti.var")
quanti.var 

fviz_mfa_var(res, "quanti.var", palette = "jco", 
             col.var.sup = "violet", repel = TRUE)

# Coordinates
head(quanti.var$coord)
# Cos2: quality on the factore map
head(quanti.var$cos2)
# Contributions to the dimensions
head(quanti.var$contrib)

# Contributions to dimension 1
fviz_contrib(res, choice = "quanti.var", axes = 1, top = 20, col.var= "group", color= "white" ) +  scale_fill_manual("Groups", values = c("#dec33c", "#5bb349", "#1e81b0"))

# Contributions to dimension 2
fviz_contrib(res, choice = "quanti.var", axes = 2, top = 20, col.var= "group", color= "white" ) +  scale_fill_manual("Groups", values = c("#dec33c", "#5bb349", "#1e81b0"))

# Color by cos2 values: quality on the factor map
fviz_mfa_var(res, col.var = "cos2",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"), 
             col.var.sup = "violet", repel = TRUE)

#create a bar plot of variables cos2
fviz_cos2(res, choice = "quanti.var", axes = 1)

#for individuals
ind <- get_mfa_ind(res)
ind

fviz_mfa_ind(res, quali.var="Name", label="non", #remove points labelling
             palette = "jco",
             repel = TRUE)

fviz_mfa_ind(res, 
             habillage = "HabitatType", # color by groups 
             palette = c("#00AFBB", #BFBF
                         "#03fc56",#GBF
                         "#fcba03", #GTF
                         "#fc4e03"), #TFTF
             addEllipses = TRUE, ellipse.type = "confidence", 
             repel = TRUE, # Avoid text overlapping
             label="none") 

fviz_ellipses(res, c("Name", "HabitatType"), repel = TRUE, label= "none")

#to remove individuals add : invisible = c("ind","ind.sup")

#ellipses
#"Character specifying frame type. Possible values are "convex", "confidence" or types supported by stat_ellipse() including one of c("t", "norm", "euclid") for plotting concentration ellipses.

#"convex": plot convex hull of a set o points.

#"confidence": plot confidence ellipses arround group mean points as coord.ellipse()[in FactoMineR].

#"t": assumes a multivariate t-distribution.

#"norm": assumes a multivariate normal distribution.

#"euclid": draws a circle with the radius equal to level, representing the euclidean distance from the center. This ellipse probably won't appear circular unless coord_fixed() is applied.#
```

#PCA

```{r}
Data <- Metradica_log %>% select(-Code, -Genus, -Species, Habitat, Type, -TWI) %>% relocate(LSWC, .after = TLP) %>% relocate(MidribWidth, .after = MajVLA) %>% relocate(SecundaryWidth, .after = MidribWidth)


# data
data <- Data

data$Type <- recode(data$Type, BF='SF Specialist', TF= 'TF Specialist')
#data <- mutate(data, Type = recode(Type, "BF" = "SF specialist")) #other way to do it

# v0
res.PCA <- FactoMineR::PCA(data[, c(1:18)][,-c(1,2,4,5)], quali.sup = 1, graph = F)
factoextra::fviz_pca_biplot(res.PCA, axes = c(1,2), label = "var", habillage = 1, repel = T,
                            addEllipses = T, ellipse.level = 0.8)  +
  scale_color_manual(values=c("#6DB4EE", "#34e042", "#b58404")) +
  theme_classic()

# v2
 
autoplot(princomp(~ Gmin + TLP + LA + SLA + LSWC + MajVLA + MidribWidth + SecundaryWidth + K + P + C + N, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

# v3
g <- autoplot(princomp(~ Gmin + TLP + LA + SLA + LSWC + MajVLA + MidribWidth + SecundaryWidth + K + P + C + N, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)+
    theme(legend.position = c(0.85,0.2))

ggsave(filename = "PCA_full_HabitatPref.png", plot = g, bg = "white", width = 8, height = 8, dpi = 600)

# v4
g0 <- autoplot(princomp(~ Gmin + TLP + LA + SLA + LSWC + MajVLA + MidribWidth + SecundaryWidth + K + P + C + N, data = data, cor = T),
         data = data, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042", "#6DB4EE", "#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  theme(legend.position = c(0.85,0.2))

g1 <- g0 + stat_ellipse(aes(col = Type, alpha = Type), level = 0.85, size = 1.5) + scale_alpha_manual(guide = "none", values = c(0, 1, 1))

g3 <- g0 + stat_ellipse(aes(col = Type, alpha = Type), level = 0.85, size = 1.5) + scale_alpha_manual(guide = "none", values = c(1, 0, 0))

g2 <- g0 + stat_ellipse(aes(col = Type), level = 0.85, size = 1.5)
cowplot::plot_grid(g0,g1, g2)

ggsave(filename = "PCA_0.png", plot = g0, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_1.png", plot = g1, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_2.png", plot = g2, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "PCA_3.png", plot = g3, bg = "white", width = 8, height = 8, dpi = 600)

# v5
data$Habitat <- recode(data$Habitat, BF='SF soils', TF= 'TF soils')

g5<- autoplot(princomp(~ Gmin + TLP + LA + SLA + LSWC + MajVLA + MidribWidth + SecundaryWidth + K + P + C + N, data = data, cor = T),
         data = data, alpha = "Type", size = 2, col = "Habitat",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         loadings.label.colour = 'black', loadings.colour = 'black') +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse()+
  scale_alpha_manual(guide = "none", values = c(0, 0.4, 0.4)) +
  scale_color_manual("Habitat of\ncollect", values = c("#6DB4EE", "#b58404")) 

ggsave(filename = "PCA_5.png", plot = g5, bg = "white", width = 8, height = 8, dpi = 600)
```

## Permutational MANOVA

PERMANOVA assumes no distribution, allows for differences in between-group variation, is insensitive to multicollinearity, allows for multiple variables and is insensitive to many zeros.

```{r}

data_PCA <- data[, c(1:18)][,-c(1,2,3,4,5)]

res.PCA <- FactoMineR::PCA(data_PCA, quali.sup = 1, graph = F)

```


```{r}
dis <- vegdist(data_PCA,method="euclidean")
mod <- betadisper(dis,data$Type)
anova(mod)
```
the null hypothesis of no differences between types is strongly rejected (pvalue 0.0003)

H0 = means are not different

P-value = 0.0003 so we reject H0 : our group dispersions are different between types.

Check if our treatments have different means. Use a permuting method to check if the difference is really due to the treatments.

```{r}
adonis2(data_PCA~data$Type, permutations = 999)
```

P-value (0.001) *** is always significant so our group types have different means.

Process a pairwise analyse to detect which treatments are different from each other.

install pairwise : ` install_github("pmartinezarbizu/pairwiseAdonis/pairwiseAdonis")`

```{r}
library(pairwiseAdonis)
pairwise_adonis <- pairwise.adonis(data_PCA,data$Type)


pairwise_adonis %>%
  gt() %>%
  tab_header(title = md("*Permutational MANOVA on habitat preference*"))

```

SF specialists are different from the two other groups.

## PCA per Type


```{r}

subdata_G <- data %>% subset(Type=="Generalist")

# generalist
generalist <- autoplot(princomp(~ Gmin + TLP + LA + SLA + LSWC + MajVLA + MidribWidth + SecundaryWidth + K + P + C + N, data = subdata_G, cor = T),
         data = subdata_G, colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#34e042")) +
  scale_shape_discrete("Habitat\npreference") +
  theme(legend.position = c(0.85,0.2))

subdata_SP_SF <- data %>% subset(Type=="SF Specialist")

# Specialist_BF
Specialist_SF <- autoplot(princomp(~ Gmin + TLP + LA + SLA + LSWC + MajVLA + MidribWidth + SecundaryWidth + K + P + C + N, data = subdata_SP_SF , cor = T),
         data = subdata_SP_SF , colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#6db4ee")) +
  scale_shape_discrete("Habitat\npreference") +
  theme(legend.position = c(0.85,0.2))

subdata_SP_TF <- data %>% subset(Type=="TF Specialist")

# Specialist_TF
Specialist_TF <- autoplot(princomp(~ Gmin + TLP + LA + SLA + LSWC + MajVLA + MidribWidth + SecundaryWidth + K + P + C + N, data = subdata_SP_TF , cor = T),
         data = subdata_SP_TF , colour = "Type", alpha = 0.4, size = 2, shape = "Type",
         loadings = T, loadings.label = T, loadings.label.repel = T, 
         #loadings.label.hjust = c(0, -1,0, 0,0),
         #loadings.label.vjust = c(0, 0, 0, 0, 0),
         loadings.label.colour = 'black', loadings.colour = 'black',
         loadings.label.size = 6) +
  geom_hline(aes(yintercept = 0), col = 'black', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'black', linetype = "dotted") +
  theme_classic() +
  scale_y_reverse() +
  scale_color_manual("Habitat\npreference", values = c("#b58404")) +
  scale_shape_discrete("Habitat\npreference") +
  theme(legend.position = c(0.85,0.2))

ggsave(filename = "generalist.png", plot = generalist, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "Specialist_SF.png", plot = Specialist_SF, bg = "white", width = 8, height = 8, dpi = 600)
ggsave(filename = "Specialist_TF.png", plot = Specialist_TF, bg = "white", width = 8, height = 8, dpi = 600)
```




