---
title: "Results"
author: "Marion Boisseaux"
date: "05/09/2022"
output: html_document
---

# Libraries

```{r librairies_results}
library(tidyverse)
library(ggfortify)
library(dplyr)
library(factoextra)
library(FactoMineR)
library(Factoshiny)
library(corrplot) 
library(ggpubr)
library(ggfortify)
library(agricolae)
library(rstatix)
library(kableExtra)
library(V.PhyloMaker)
library(ggfortify)
library(ggtree)
library(readxl)
library(lme4)
library(ggeffects) #draw plots of models
library(nlme)
library(sjPlot) #for plotting lmer and glmer mods
library(gridExtra)
library(rio)
library(vegan)
library("Hmisc")
```

# Data

```{r Data_results, message=FALSE, warning=FALSE}

Metradica_log <- read.csv("C://Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Metradica_trait_OUT.csv") %>% 
  dplyr::select(Code, Genus, Species, Name, Habitat, Type, Forest, Gmin, TLP, LSWC, MajVLA, Nitrogen, Carbon, Phosphorous, Potassium, SD) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium", "SD"), abs) %>% 
  mutate_at(c("Gmin","TLP", "LSWC", "MajVLA", "Nitrogen", "Carbon", "Phosphorous", "Potassium", "SD"), log) %>% 
  mutate(TLP = -TLP) 
  #na.omit() 

sub_data_TF <- Metradica_log %>%
  filter(Name %in% c("Dicorynia_guianensis", "Iryanthera_sagotiana", "Gustavia_hexapetala", "Licania_membranacea", "Poraqueiba_guianensis", "Virola_michelii"))

sub_data_SF <- Metradica_log %>%
  filter(Name %in% c("Eschweilera_coraicea","Eperua_falcata", "Iryanthera_hostmannii", "Laetia_procera", "Protium_opacum subsp. rabelianum", "Pterocarpus_officinalis", "Symphonia_globulifera", "Virola_surinamensis"))

sub_data_G <-  Metradica_log %>%
  filter(Name %in% c("Bocoa_prouacensis", "Conceveiba_guianensis", "Jacaranda_copaia subsp. copaia", "Hymenopus_heteromorphus", "Protium_stevensonii", "Tachigali_melinonii"))

sub_data <- bind_rows(sub_data_TF, sub_data_SF, sub_data_G)

Metradica <- sub_data

```



# RDA Analyses

## Sub data

```{r Subdata_Specialisation_Results}

# matrice with envt variables
Envt <- Metradica %>% select(Code, Habitat, Type, Forest)
  
# matrice with trais
traits <- Metradica %>% select(TLP, Gmin, LSWC, MajVLA, SD, Potassium, Phosphorous, Carbon, Nitrogen)
traits$TLP <- abs(traits$TLP)

# species
  
species <- Metradica %>% select(Code, Species, Genus, Name)
  
```

## Colinearity

```{r}
library(corrplot)

traits %>% 
  na.omit() %>% # attention, la presence de NA bloque le processus pour regarder la colinearité
  cor(method = "spearman") %>% 
  corrplot::corrplot.mixed()

#autre facon de le faire
df2 <- cor(traits, use = "na.or.complete", method = "spearman")
corrplot::corrplot(df2, method="shade",shade.col=NA, tl.col="black", tl.srt=45)

## add significant level stars
testRes = corrplot::cor.mtest(traits, conf.level = 0.95,  method = "spearman")

corrplot::corrplot(df2, type = 'lower',
         order = "alphabet", 
         p.mat = testRes$p, 
         sig.level = c(.001, .01, .05), #significant level, with default value 0.05. If the p-value in p-mat is bigger than sig.level, then the corresponding correlation coefficient is regarded as insignificant.
         pch.cex = 1.5,
         insig = 'label_sig', pch.col = 'grey20',
         tl.pos="d", #write names of variables in the diagonal
         outline=FALSE,
         col = COL2('RdBu', 10)) #la colonne des couleurs a cote
        
#test independant between two variables to understand how the test is constructed
cor.test(traits$LA, traits$Gmin,
         method = "spearman",
         exact = FALSE) 

```

## Standardize
```{r}
# the way you are using decostand with 'standardize', it is the same as scale option with rda with scale =TRUE. 

# Scale and center variables; standardize: scale x to zero mean and unit variance (defaultMARGIN = 2)
traits.z <- decostand(traits, method = "standardize") 

# Variables are now centered around a mean of 0
round(apply(traits.z, 2, mean), 1)

# and scaled to have a standard deviation of 1
apply(traits.z, 2, sd)
```

## RDA

```{r}
library (vegan)
spe.log <- log1p (spe)  # species data are in percentage scale which is strongly rightskewed, better to transform them
spe.hell <- decostand (spe.log, 'hell')  # we are planning to do tb-RDA, this is Hellinger pre-transformation
tbRDA <- rda (Metradica_log[,9:15] ~ TWI + Name, data = Metradica_log, scale = TRUE)  # calculate tb-RDA with two explanatory variables
tbRDA

ordiplot(tbRDA, scaling = 1, type = "text")
```

How to interpret results:

Call: rda(formula = Metradica_log[, 9:15] ~ Habitat, data = Metradica_log,
scale = TRUE)

              Inertia Proportion Rank
Total          7.0000     1.0000     
Constrained    0.1701     0.0243    1
Unconstrained  6.8299     0.9757    7
Inertia is correlations 

Eigenvalues for constrained axes:
   RDA1 
0.17009 

Eigenvalues for unconstrained axes:
   PC1    PC2    PC3    PC4    PC5    PC6    PC7 
1.7447 1.5250 1.0425 0.8654 0.7711 0.4810 0.4002 

  
- Constrained Proportion: variance of Y (traits) explained by X (Habitat) (2.4 %)
- Unconstrained Proportion: unexplained variance in Y (97 %)

En faisant la meme avec seulement espèce: 44 % de la variance est expliqué.

Avec TWI: 2% 

#NMDS

```{r}

set.seed(123)

nmds <- traits %>% 
  na.omit() %>% # attention, la presence de NA bloque le NMDS
  metaMDS(distance = "bray") %>%
  plot()

#we ask for 2 dimensions, algo takes the points and moves pts around to fit into 2D based on similarity and dissimilarities. It repeats the process to try to find the best fits, findin the smallest stress value aka the amount of distortion when it take the highly dimensional data and we smush it down into 2D. it does the best job at reprensenting variation in the data without using linear combinations

#extract NMDS scores (x and y coordinates)
data.scores = scores(nmds)

#extract NMDS scores (x and y coordinates) for sites from newer versions of vegan package
data.scores = as.data.frame(nmds$sites)

#add columns to data frame 
Data2 <- Data %>% select(Name, Forest, Habitat, Type, HabitatType, TLP, Gmin, LA, SLA, LSWC, MajVLA, K, P, C, N) %>% na.omit()
data.scores$Species = Data2$Name
data.scores$Type = Data2$HabitatType
data.scores$Forest = Data2$Forest
data.scores

head(data.scores)

ggplot(data.scores, aes(x = NMDS1, y = NMDS2)) + 
    geom_point(size = 4, aes(colour =Type))+ 
    theme(axis.text.y = element_text(colour = "black", size = 12, face = "bold"), 
    axis.text.x = element_text(colour = "black", face = "bold", size = 12), 
    legend.text = element_text(size = 12, face ="bold", colour ="black"), 
    legend.position = "right", axis.title.y = element_text(face = "bold", size = 14), 
    axis.title.x = element_text(face = "bold", size = 14, colour = "black"), 
    legend.title = element_text(size = 14, colour = "black", face = "bold"), 
    panel.background = element_blank(), panel.border = element_rect(colour = "black", fill = NA, size = 1.2),
    legend.key=element_blank()) + 
    labs(x = "NMDS1", colour = "HabitatType", y = "NMDS2") 

```

