---
title: "SI_Paper_Metradica"
author: "Marion Boisseaux"
date: "13/09/2022"
output: html_document
---

# Libraries
```{r}
library(tidyverse)
library(ggfortify)
library(factoextra) 
library(ggfortify)
library(kableExtra)
library(V.PhyloMaker)
library(ggtree)
library(readxl)
library(gridExtra)
library(rio)
library(dplyr)
library(tidyr)
library(janitor)
library(forcats)
library(ggplot2)
```

# Species phylogeny

```{r Phylogeny, echo=FALSE, message=FALSE, warning=FALSE}

species <- data.frame(taxon = c(
  "Eperua_falcata", 
  "Iryanthera_hostmannii", 
  "Jacaranda_copaia subsp. copaia",
  "Pterocarpus_officinalis",
  "Symphonia_globulifera",
  "Tachigali_melinonii",
  "Virola_surinamensis", 
  "Bocoa_prouacensis",
#  "Chrysophyllum_prieurii",
  "Conceveiba_guianensis",
  "Eschweilera_coriacea",
  "Hymenopus_heteromorphus",
  "Protium_stevensonii",
  "Virola_michelii",
  "Carapa_surinamensis",
#  "Carapa_guianensis",
  "Laetia_procera",
  "Protium_opacum subsp. rabelianum",
 # "Casearia_javitensis",
  "Dicorynia_guianensis",
  "Gustavia_hexapetala",
  "Iryanthera_sagotiana",
  "Licania_membranacea",
  "Poraqueiba_guianensis"
  #"Vouacapoua_americana"
))%>% separate(taxon, c("Genus", "Species"), sep = "_", remove = F)

species <- dplyr::select(species, taxon , Genus, Species)

paracou <- read_excel("../Metradica_Paracou/Document/Paracou_database20210830.xlsx") %>% 
  dplyr::select(Family, Genus, Species) %>% 
  unique() %>% 
  full_join(species) %>% 
  mutate(species = paste(Genus, Species), genus = Genus, family = Family) %>% 
  dplyr::select(species, genus, family, taxon) %>% 
  mutate(taxon = as.character(taxon))

tree <- phylo.maker(sp.list = paracou, tree = GBOTB.extended, nodes = nodes.info.1, scenarios = "S3")

#remove # when running for the first time.

#save(tree, file = "./Results/phylogeny_subset.Rdata")
#load("./Results/phylogeny_subset.Rdata")

A<- fortify(tree$scenario.3) %>% 
  mutate(species = gsub("_", " ", label)) %>% 
  left_join(paracou) %>% 
  ggtree(aes(col = taxon), layout="circular") + 
  geom_tiplab2(aes(alpha = !is.na(taxon), size = !is.na(taxon))) +
  theme_tree(legend.position='bottom', legend.text = element_text(face = "italic")) +
  scale_alpha_manual("taxon", values = c(0.2, 4)) +
  scale_size_manual("taxon", values = c(1, 4))

#choose saving format
ggsave(file="phylo_subset.svg", plot=A, width=15, height=10)
ggsave(file="phylo_subset.jpg", plot=A, width=15, height=10)
```


# Table sampling 

*Total individuals collected for the paper.*

```{r Subset - Individuals per species collected in the three sampling sites. }

#get authorization 
googlesheets4::gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets.readonly" )

Family <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1XoQH2pg5bcuvFzSdmY4v_lC-D_u9LMye4RTiJU4XRmg/edit#gid=122243583", sheet = "Species_SI") %>% select(Family, Genus, Species)

#Marion's computer path METRADICA/Divers/Species_choice_Indval/Metradica_species_subset_total.csv

#campaign subset data
#data added to drive for co-authors
Data <- read.csv("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/METRADICAproject/Dataset/OUTPUT_cleaning/Subset_imputed/Subset_imputation_exceptSD.csv") 

Paracou <- Data %>% 
  filter(Forest == "Paracou") %>%
  group_by(Name) %>%
  summarise(Paracou = n())

Bafog <- Data %>% 
  filter(Forest == "Bafog") %>%
  group_by(Name) %>%
  summarise(Bafog = n())

Kaw <- Data %>% 
  filter(Forest == "Kaw") %>%
  group_by(Name) %>%
  summarise(Kaw = n())

Paracou <- left_join(Paracou, Bafog)

Totaux_table <- left_join(Paracou, Kaw)

Data <- Data %>% dplyr::select(Genus, Species, Name) %>%unique()

Data <-   left_join(Totaux_table, Data)%>%
  relocate(Genus, .before =Name) %>%
  relocate(Species, .after = Genus)

Totaux_table <- left_join(Data, Family)

Totaux_table <- Totaux_table %>%
  select(-Name) %>%
  relocate(Family, .before="Genus") %>%
  adorn_totals("row")


Totaux_table <- Totaux_table %>%
  replace(is.na(.), 0) %>%
  mutate(Total = rowSums(select(., -Family, -Genus, -Species)))

options(knitr.kable.NA = '') #replace NA by blank spaces in table

Totaux_table %>%
  kbl(caption = "Individuals per species collected on the 3 sites") %>% 
  kable_classic(full_width = F, html_font = "Cambria") %>%
  column_spec(2:3, italic = T) %>%
  row_spec(0, bold= T) %>%
  row_spec(22, background = "#666;", color = "white") %>%
  column_spec(7,  background = "#666;", color = "white" ) %>%
save_kable(file = "../METRADICAproject/Results/Tables_SI/Sampling_subset.png")

```


# Table Indvals

```{r Species chosen for the study according to the Indicator values (Indval) within each habitat in French Guiana. }

#get authorization
googlesheets4::gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets.readonly" )

#indval data 
Indval <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1XoQH2pg5bcuvFzSdmY4v_lC-D_u9LMye4RTiJU4XRmg/edit#gid=122243583", sheet = "Species_SI") %>% select(-Paracou, -Bafog, -Kaw)

Indval <- with(Indval, Indval[order(Type) , ]) #ordering per type

options(knitr.kable.NA = '') #replace NA by blank spaces in table


Indval %>%
  kbl() %>%
  row_spec(0, bold = TRUE) %>% 
  column_spec(1:2, italic = TRUE) %>%
  kable_classic_2(full_width = F) %>% save_kable(file = "../METRADICAproject/Results/Tables_SI/IndVal_subset.png", zoom = 10)

```

# Graph Indvals

Species with high IndVals means that the species prefers the habitat (but not exclusive, hence the word **preference**), but are also a high probability of being sampled in the given habitat.

Our analysis identified 9 generalist taxa, 8 SFF specialist taxa and 7 terra firme specialist taxa.

```{r Indval boxplots per habitat preferences}
#baraloto et al SI
indval_baraloto <- readxl::read_xlsx("C:/Users/marion.boisseaux/Dropbox/Mon PC (Jaboty20)/Documents/METRADICA/Divers/Species_choice_Indval/Indval_Peru_&_FG.xlsx")

indval_baraloto <- indval_baraloto %>% select(...8, ...9, ...10, ...11, ...12, ...13)

indval_FG <- indval_baraloto[-(1:4),-5]

indval_FG <- janitor::row_to_names(indval_FG, 1)

#calculating thresholds for habitat specialists
probs <- c(0.95)
quantiles_SF <- quantile(as.numeric(indval_FG$SF), prob=probs) # Top 5% highest values for SF specialists : indval >= 0.2 
#95% 
#0.2 
quantiles_TF <- quantile(as.numeric(indval_FG$TF), prob=probs) 
#   95% 
# 0.2598 

indval_FG$SF<- as.numeric(indval_FG$SF)
indval_FG$TF<- as.numeric(indval_FG$TF)

#SF specialists
Data_SF<- indval_FG %>%
  select(Species, Abund, SF, TF, `P-value`) %>%
  filter(SF >= 0.2) %>%
  rename(Indval_SF =SF, Indval_TF =TF)

#TF specialists
Data_TF<- indval_FG %>%
  select(Species, Abund,SF, TF, `P-value`) %>%
  filter(TF >= 0.2598)%>%
  rename(Indval_SF =SF, Indval_TF =TF)

#concerning our species
identified_species <- data.frame(Species = c("Eperua_falcata", 
  "Iryanthera_hostmannii", 
  "Jacaranda_copaia",
  "Pterocarpus_officinalis",
  "Symphonia_globulifera",
  "Tachigali_melinonii",
  "Virola_surinamensis", 
  "Bocoa_prouacensis",
  "Conceveiba_guianensis",
  "Eschweilera_coriacea",
  "Hymenopus_heteromorphus",
  "Protium_stevensonii",
  "Virola_michelii", 
  "Carapa_surinamensis", 
  "Laetia_procera",
  "Protium_opacum", 
  "Dicorynia_guianensis",
  "Gustavia_hexapetala",
  "Iryanthera_sagotiana",
  "Licania_membranacea",
  "Poraqueiba_guianensis"
  ))
  

Specialist_SF <- left_join(identified_species, Data_SF) %>% na.omit()

Specialist_TF <- left_join(identified_species, Data_TF) %>% na.omit()

Generalist_fort_indval_deux_habitats <- inner_join(Specialist_SF, Specialist_TF )


Specialist_TF <- Specialist_TF %>% 
  filter(Species != "Conceveiba_guianensis") %>% #con.gui species in both, removed it
  mutate(Type = "TF specialist")
Specialist_SF <- Specialist_SF %>% 
  filter(Species != "Conceveiba_guianensis") %>%#con.gui species in both, removed it
   mutate(Type = "SF specialist")


#indval graphs
indval_SF_plot <- Specialist_SF  %>%
  mutate(Species = fct_reorder(Species, Indval_SF)) %>% 
  ggplot(aes(x = Species, y = Indval_SF, fill = Species)) +
  geom_col() +
  scale_fill_brewer(palette = "YlGnBu", direction = 1) +
  theme_minimal() +
  # theme(palette = "Tol") #color blind palette
  theme(axis.text.x=element_text(angle=50, hjust = 1))+
  theme(legend.position="none")

ggsave(file="indval_SF_plot.svg", plot=indval_SF_plot, width=10, height=8)
ggsave(file="indval_SF_plot.png", plot=indval_SF_plot, width=10, height=8) 

indval_TF_plot<- Specialist_TF  %>%
  mutate(Species = fct_reorder(Species, Indval_TF)) %>% 
  ggplot(aes(x = Species, y = Indval_TF, fill = Species)) +
  geom_col() +
  scale_fill_brewer(palette = "YlOrRd", direction = 1) +
  theme_minimal() +
  # theme(palette = "Tol") #color blind palette
  theme(axis.text.x=element_text(angle=50, hjust = 1))+
  theme(legend.position="none")

ggsave(file="indval_TF_plot.svg", plot=indval_TF_plot, width=10, height=8)
ggsave(file="indval_TF_plot.png", plot=indval_TF_plot, width=10, height=8)

#now for generalists
Generalist <- left_join(identified_species, indval_FG) 

Generalist <- Generalist %>% rename(Indval_SF = SF, Indval_TF = TF)

Generalist <-  Generalist %>%
  na.omit() %>%
  filter(Indval_TF <= 0.2598) %>%
  filter(Indval_SF <= 0.2)

#cannot consider jas.jav.
Generalist <- Generalist %>% 
  filter(Species != "Casearia_javitensis") %>%
  filter(Abund != 5) 


Generalist_all  <-rbind(Generalist, Generalist_fort_indval_deux_habitats)


Generalist_all <- Generalist_all %>% 
  mutate(Diff_Indval = abs(Indval_SF-Indval_TF)) %>%
  mutate(Type = "Generalist")

Generalist_diff_indval<- ggplot(Generalist_all) +
   aes(x = Species, y = Diff_Indval, fill = Species) +
   geom_col() +
   scale_fill_brewer(palette = "RdYlBu", direction = 1) +
   theme_minimal() +#les couleurs en faveur des BF, tacmel proche d'un SF spe donc couleur bleu
  theme(axis.text.x=element_text(angle=50, hjust = 1))+
  theme(legend.position="none")

ggsave(file="indval_generalist_diff_indval_plot.svg", plot=Generalist_diff_indval, width=10, height=8)
ggsave(file="indval_generalist_diff_indval_plot.png", plot=Generalist_diff_indval, width=10, height=8)

```

# Plot table
```{r Plot information }
Plot_table <- googlesheets4::read_sheet("https://docs.google.com/spreadsheets/d/1XoQH2pg5bcuvFzSdmY4v_lC-D_u9LMye4RTiJU4XRmg/edit#gid=0")
googlesheets4::gs4_auth(scopes = "https://www.googleapis.com/auth/spreadsheets.readonly" )

Plot_table <- Plot_table %>% 
  dplyr::select(-PlotName, -Xutm, -Yutm, -Localization)
  
Plot_table %>%
  kbl(caption = "Summary of sampling site information", escape = FALSE, digits = 2) %>%
  row_spec(0, bold = TRUE) %>% 
  kable_classic(full_width = F, html_font = "Cambria") %>%
  save_kable(file = "../Tables_SI/Plot_info_summary.png", zoom = 5)

```

