---
title: "Field_data_cleaning"
author: "Daniela Krebber"
date: "5/18/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

Library <- function(Packages) {
  InstallAndLoad <- function(Package) {
    if (!Package %in% installed.packages()[, 1]) {install.packages(Package, repos="https://cran.rstudio.com/")}
    require(Package, character.only = TRUE)
  }
  invisible(sapply(Packages, InstallAndLoad))
}
# Ajouter les packages nécessaires ici
Library(c("kableExtra", "formatR", "readr", "tidyverse", "lubridate", "here"))

source(here("paths.R")) # Marion you probably don't need this, but I have a .R file in which I specify all my paths for my documents, csv files etc... so that if I change the position of a certain file I just change it in the .R file - I do this with the function here.... so you will need to adapt it to your paths. 
source(here(functionPath, "Functions_DataCleaning.R")) # functions 
```


# Clean FieldData Marion
a) read in file
* make sure that empty cells are read in as NAs
```{r read in data}
ParacouDB <- read.csv(ParacouDBCleanPath, header=T) 

FieldSheet <- read.csv("./../input/2021_06_17_Traits_Paracou_Marion.csv", header=T, na.strings=c("","NA")) # detect empty cells as NAs

```

b) get rid of rows that contain ONLY NAs 
* get number of columns
* take out rows with rowSums of nas == to the number of columns

```{r get rid of empty rows}
FieldSheet <- deleting_EmptyRows(FieldSheet)
```


## Data format Fielddata_Sheet

Make sure the format of the columns are correct

### 1) Rename column names to match Paracou Database and make the data sheet more understandable
* change column names and write function for this so that afterwards we always work with the same information
a) rename column names in FieldSheet to match database Paracou

```{r Rename Column names}

names(FieldSheet)

FieldSheet_Clean  <- FieldSheet %>% 
  rename(TreeFieldNum = FieldNr, 
         SubPlot = Subplot, 
         SpecCode = spName, 
         RWCnr_original = Code, 
         DawkinIndiv = Dawkin_Tree, 
         DawkinBranch = Dawkin_Branch, 
         HeightTree = Height_Tree, 
         HeightBranch = Height_Branch)# %>% 
  #mutate(Sampled = 1)
```


### 2) Check structure and format of the dataframe
Characters that should be characters, integers that should be integers, numerical data should be numeric, dates should be dates and times should be times etc… 
str(FieldSheet)

  * specify which is which here - error message if it isn't

  * id should be a Character 
  * DateField should be a Date object - correct it
  * TimeArrival should be a Time object - correct it
  * WXArrival should be a character
  * Plot should be an integer
  * SubPlot should be an integer
  * idTree should be an integer
  * FieldNr should be an integer
  * SpecCode_DB should be a character
  * Recorder should be a character and should contain the initials of the recorder (Letter Code)
  * DawkinIndiv should be an integer
  * RWCnr_original should be a character (not an integer because we also have cases where RWC number consistis of a letter and an integer)
    + this is especially important for comparisions between RWCbigBag_used and additional RWC bags
  * Resampled should be logical - correct it
  * RWC_additional 1 and 2 should be a character
    + these are columns created for individuals that have been on purpose resampled 
    + for these individuals we keep the original RWC bag number and add a RWC number
  * NrDiscs should be integer
    + normally 4 discs per leaf have been sampled for the RWC disc method
    + this is a column only for the first individuals measured as we were still using the disc technique and later switched entirely to the entire leaf technique
  * DiscDiameter should be an integer
    + tells you the diameter in mm of each disc, should be 8 mm for all samples
  * NrLeaves4Discs should be an integer
    + this column refers to the number of leaves/leaflets that have been used for the discs
    + sometimes leaves and leaflets are too small or the secondary veins are too dense to create more than 1 or 2 discs per leaf/leaflet then additional leaves/leaflets had to be taken to get 4 discs for an individual
  * SampledTraits should be a character
    + NO_Psimd refers to samples for which no Psimd has been measured (as the conditions weren't right)
    + All refers to samples where all traits have been measured
    + Gmin to samples where only gmin has been measured again
    + RWC to samples were RWC has been resampled
    + Ptlp to samples were Ptlp has been resampled
  * Ficelle should be a character
    + 0 means there has been no rope placed on the tree
    + 1 means that a rope has been placed on the tree to facilitate resampling for Psimd
    + 0,easy meants that no rope has been placed on the tree as it is very easy to bigshot the tree
  * TimeCollection should be a time object
    + gives you the time at which the leaves were collected from the tree
  * WXCollection should be a character 
    + We stopped entering the information when it became clear that we are not continuing to try to measure water potential at midday
    + more precise information can be retrieved from the Guyaflux tower measurements and other weather stations around Paracou
  * DawkinBranch should be an integer
    + describes the Dawkin index of the sampled branch
    + should be an integer between of 3 or 4, rarely 2 and 5
  * DawkinTree should be an integer
    + gives the Dawkin index of the Tree that has been sampled 
    + should be between 2 and 5
  * HeightBranch in m should be an integer
  * Height Tree in m should be an integer
    + was not taken at the beginning and a lot missing values due to various reasons
  * PosCrown should be a character
    + describes the position within the crown of the individual tree should only be low (lower 1/3), middle (middle 1/3) and top (top 1/3)
  * LeafLight_exposition should be a character
    + here we try to describe whether the leaf samples themselves self received fullsun light (sunlit leaves), direct sunlight, partial sunlight or are found in half shade or shade
    + depends very much on the date of time and wheather conditions so I feel this addional classification of exposure to light may be rather imprecise
  * Nrleaves2Lab should be a character
    + gives an idea how many leaves were collected and sent to the lab
    + normally we collected over 10 but this was not possible in all cases
    + higher number of leaves collected often results in a better choice of beautiful leaves for the measurements
  * RWCSecVeins2Dense should be logical TRUE and FALSE or 1 and 2
    + this refers to the discs that have been taken for RWC
    + the aim was to take a disc excluding all primary and secondary veins, for some species with too dense secondary veins this was impossible to achieve

## Clean Fielddata_Sheet of the two sampling seasons

### 1) only keep sampled individuals 
* all individuals that were visited were entered even if they were not good for sampling (only complete for the first field season - information exists on sampling maps for the second field season) 
* this was done to prevent revisiting the same individual that is not suitable for sampling later on

### 2) Correct typos and wrongly entered information automatically

a) Create dataframe with which the FieldSheet can be compared e.g. the Paracou Database

  * the dataframe contains each idTree only once - must be unique
  * the dataframe contains only relevant information - Plot, SubPlot, Genus, Species, spName, spName, idTree, TreeFieldNum
```{r ParacouDB unique idTrees}
# create a Paracou Database dataframe only containing unique idTrees
ParacouDB_unique <- ParacouDB %>% group_by(Plot, SubPlot, Genus, Species, spName, idTree, TreeFieldNum) %>% filter(CensusYear==2019) %>% distinct(idTree) # the distinct should not be needed here as I already filtered for the trees from the inventory of 2019 (all Plots have been censused in 2019)
```

b) Create Species Code that matches your species code in the FieldSheet

 * as we did not note the entire binomial species name in the field recording sheet but just a 6 letter species code, I will create a corresponding species code column for the Paracou Database
    + the species Code consists of a 6 letter code - 3 letters for the genus seperated from 3 letters for the species by a "**.**"
    + be aware that binomial species names can lead to the same 3 letter abbreviation e.g. Pou.gui can stand for *Pourouma guianensis* as well as for *Pouteria guianensis*
    + however none of the target species share the same abbreviation - but one Pourouma guinanensis has been sampled due to a missidentification of the individual in the     Paracou database

```{r Create SpecCode for Paracou_DB}
# create species abbreviation code
ParacouDB_unique <- ParacouDB_unique %>% mutate(SpecCode =  paste0(str_sub(Genus, 1, 3), ".", str_sub(Species, 1, 3)))
```


c) Join your sampling sheet with the dataframe in which the correct information on the individual trees exists (here after refered to as *Database*), by a unique identifier that exists in both e.g. idTree

This will reveal the mismatches between the two if any exist

d) Add columns for missmatches between your sampling sheet and the Database with the correct information

There are multiple possibilities for errors:
  * **no_mismatch**: all information corresponds to each other
  * **idNOTinDB**: unique identifier (e.g. idTree, hereafter refered to as *id*) does not exist in the Database
    + clearly the id has been wrongly noted
    + either only the id is wrong --> *easy fix*
    + or in multiple columns wrong information has been noted --> *manual fix*
    + careful only because the id does exist in the Database does not mean that there hasn't been a Typo in the id and it just matches something by chance (however not the correct tree)
    
  * **idTree_missmatch**: all information except for the id do not match between the two dataframes
  * **TreeFieldNum_missmatch**: only information on Tree Field Number does not match
  * **Plot_missmatch**: only information on Plot does not match
  * **SubPlot_missmatch**: only information on Sub Plot does not match
  * **SpecCode_missmatch**: only information on Species Code Number does not match
  * **Manualcheck_missmatch**: several columns do not match and require a manual check
    + to create the manualcheck_missmatch I enter a 1 for each of the individuals that have either received a 1 in *idNOTinDB*, 
    **OR** did not receive a code one in any of the other above mentioned columns 

Example for ids not matching any in the database:

**A dataframe consisting of sampled individuals within the Fielddata_Sheet that do not match any existing idTrees within the ParacouDB:**
```{r Dataframe with mismatch of idTrees between FieldSheet and ParacouDB}
# get a dataframe with all the individuals where idTree does not correspond to any within the database

iddoesNotExist <- FieldSheet_Clean %>% 
  mutate(idExists = ifelse(FieldSheet_Clean$idTree %in% ParacouDB_unique$idTree == T, 1,0)) %>% # creates a new Column with a 0 (not found in database) and 1 (exists in database) code 
  filter(idExists == 0) # filter only the 0s to get a dataframe only containing incorrect ids

print(iddoesNotExist)
# there are 8 clear mistakes of idTrees
```
**There is a idTrees within the FieldSheet that do not match any idTree in the Database - as it is NA**

e) retrieve correct information automatically if possible:
  * **no_mismatch**
    + --> nothing needs to be done
  * **idNOTinDB** if the combination of all other information (which is also unique):
    + --> matches the information in the database --> *extract correct id from Database and state that this is not a manualcheck_missmatch*
    + --> DOES NOT match the information in the database --> *manual check required as more than one column differs from Database*
    
  * **idTree_missmatch**: the combination of all other information (which is also unique):
    + --> matches the information in the database --> *extract correct id from Database*
    + --> DOES NOT match the information in the database --> *manual check required as more than one column differs from Database*
    
  * **TreeFieldNum_missmatch**: 
    + --> *extract correct Tree Field Number from Database*
  * **Plot_missmatch**: only information on Plot does not match
    + --> *extract correct Plot from Database*
  * **SubPlot_missmatch**: only information on Sub Plot does not match
    + --> *extract correct Sub Plot from Database*
  * **SpecCode_missmatch**: only information on Species Code Number does not match
    + --> *extract correct Species Code from Database*
  * **Manualcheck_missmatch**: 
    + --> *needs to be checked manually - Return a dataframe for manual corrections*
    
For each correction a Correction Code e.g. *Code_idTreeCorr* is added and the wrongly noted information is kept in an additional column e.g. *idTree_Wrong*.

```{r Add missmatch of FS and DB to dataframe}

FieldSheet_Clean <- rownames_to_column(FieldSheet_Clean)
#c) Join your sampling sheet with the dataframe in which the correct information on the individual trees exists (here after refered to as *Database*), by a unique identifier that exists in both e.g. idTree

# join Fieldsheet and Paracou_DB by idTree only 
FieldSheet_Clean <- left_join(FieldSheet_Clean, #%>% rename(SpecCode = SpecCode_DB), #rename the SpecCode_DB from witin the sample sheet to SpecCode_FS to avoid confusion
                               ParacouDB_unique %>% ungroup() %>% select(idTree, Plot, SubPlot, TreeFieldNum, SpecCode), # join with the ParacouDB that only contains each idTree once & select relevant columns
                               by="idTree", suffix = c("_FS", "_DB")) # only join by idTree and give information from the DB the suffix .DB to clearly state what comes from where

#d) Add columns for missmatches between your sampling sheet and the Database with the correct information

# create missmatch rows to indicate missmatches between the 2 joined dataframes - alternatively this could be done in two steps by setting the difference between the two dataframes and creating a third containing these differences

FieldSheet_Clean <- FieldSheet_Clean %>% mutate(no_missmatch = ifelse(Plot_FS == Plot_DB &         ## in case there is no missmatch at all
                                                          SubPlot_FS == SubPlot_DB &
                                                          TreeFieldNum_FS == TreeFieldNum_DB &
                                                          SpecCode_FS == SpecCode_DB, 1, NA),
                                     #could combine idNotInDB and idTree_missmatch
                                                idNotInDB = ifelse(is.na(idTree) |
                                                          is.na(Plot_DB) &                  ## in case idTree does not exist in Database or is NA
                                                          is.na(SubPlot_DB) &
                                                          is.na(TreeFieldNum_DB) &
                                                          is.na(SpecCode_DB), 1, 0),

                                                idTree_missmatch = ifelse(idNotInDB == 1 &
                                                          Plot_FS != Plot_DB &                  ## in case only idTree is wrong there is the chance that all other columns don't match
                                                          SubPlot_FS != SubPlot_DB &
                                                          TreeFieldNum_FS != TreeFieldNum_DB &
                                                          SpecCode_FS != SpecCode_DB, 1, NA),
                                
                                TreeFieldNum_missmatch = ifelse(TreeFieldNum_FS != TreeFieldNum_DB & ## in case of missmatch in TreeFieldNum only
                                                          Plot_FS == Plot_DB &
                                                          SubPlot_FS == SubPlot_DB &
                                                          SpecCode_FS == SpecCode_DB | 
                                                            is.na(TreeFieldNum_FS) &
                                                          Plot_FS == Plot_DB &
                                                          SubPlot_FS == SubPlot_DB &
                                                          SpecCode_FS == SpecCode_DB, 1, NA), 
                                
                                Plot_missmatch = ifelse(Plot_FS != Plot_DB &                        ## in case of missmatch in Plot only
                                                        SubPlot_FS == SubPlot_DB &
                                                        TreeFieldNum_FS == TreeFieldNum_DB &
                                                        SpecCode_FS == SpecCode_DB |
                                                          is.na(Plot_FS) &
                                                        SubPlot_FS == SubPlot_DB &
                                                        TreeFieldNum_FS == TreeFieldNum_DB &
                                                        SpecCode_FS == SpecCode_DB, 1, NA),
                                
                                SubPlot_missmatch = ifelse(SubPlot_FS != SubPlot_DB &               ## in case of missmatch in SubPlot only
                                                           Plot_FS == Plot_DB &
                                                           TreeFieldNum_FS == TreeFieldNum_DB &
                                                           SpecCode_FS == SpecCode_DB |
                                                          is.na(SubPlot_FS) &
                                                           Plot_FS == Plot_DB &
                                                           TreeFieldNum_FS == TreeFieldNum_DB &
                                                           SpecCode_FS == SpecCode_DB, 1, NA),
                                
                                SpecCode_missmatch = ifelse(SpecCode_FS != SpecCode_DB &            ## in case of missmatch in SpecCode only
                                                            SubPlot_FS == SubPlot_DB &
                                                            Plot_FS == Plot_DB &
                                                            TreeFieldNum_FS == TreeFieldNum_DB |
                                                          is.na(SpecCode_FS) & 
                                                            SubPlot_FS == SubPlot_DB &
                                                            Plot_FS == Plot_DB &
                                                            TreeFieldNum_FS == TreeFieldNum_DB, 1, NA),
                                
                                Manualcheck_missmatch = ifelse(is.na(no_missmatch) &              ## in case of missmatch in multiple columns - can still be that its just a typo in idTree, but the 
                                                                 is.na(idTree_missmatch) &        ## tree individual that matches with the entered idTree of the Field Sheet and the database shares
                                                                 is.na(TreeFieldNum_missmatch) &  ## additional information column with the tree individual that has bee sampled e.g. Plot or SubPlot
                                                                 is.na(Plot_missmatch) &
                                                                 is.na(SubPlot_missmatch) &
                                                                 is.na(SpecCode_missmatch), 1, 0) ## also for now assumes that if the idTree does not exist in the database it is an error that needs to be manually corrected 
                                )                                                          
#FieldSheet_Clean %>% filter(Manualcheck_missmatch==1) #18 in total


#e) retrieve correct information automatically if possible:

## Now correction 
for (i in 1:nrow(FieldSheet_Clean)) {
  
  
  ### CORRECT IDTREE if manual check is actually not required because all other information except for the idTree match an individual in the database  
  if(!is.na(FieldSheet_Clean[i, "Manualcheck_missmatch"]) && FieldSheet_Clean[i, "Manualcheck_missmatch"] != 0){
     
        # search for correct one in database
        ParacouDB_unique_corrInd <- ParacouDB_unique %>% filter(TreeFieldNum == FieldSheet_Clean[i, "TreeFieldNum_FS"] & 
                                                          Plot == FieldSheet_Clean[i, "Plot_FS"] &
                                                          SubPlot == FieldSheet_Clean[i, "SubPlot_FS"] &
                                                          SpecCode == FieldSheet_Clean[i, "SpecCode_FS"])
        if(nrow(ParacouDB_unique_corrInd == 1)){ # only if a suitable match is found - if required only here because the other correction codes already depend on that                                                    all other information has been found in the database

            # store wrongly entered idTree and overwrite with correct one
            FieldSheet_Clean[i, "idTreeWrong"] <- FieldSheet_Clean[i, "idTree"]
            FieldSheet_Clean[i, "idTree"] <- ParacouDB_unique_corrInd$idTree
            # and correct the code for Manualcheck_missmatch
            FieldSheet_Clean[i, "Manualcheck_missmatch"] <- 0
            FieldSheet_Clean[i, "Code_idTreeCorr"] <- 1 # add correction code
        }
  }
  
  
    ### CORRECT IDTREE if it was identified as a clear idTree mismatch      
   else if(!is.na(FieldSheet_Clean[i,"idTree_missmatch"]) && FieldSheet_Clean[i,"idTree_missmatch"] != 0){

        # search for correct one in database 
        ParacouDB_unique_corrInd <- ParacouDB_unique %>% filter(TreeFieldNum == FieldSheet_Clean[i, "TreeFieldNum_FS"] & 
                                                          Plot == FieldSheet_Clean[i, "Plot_FS"] &
                                                          SubPlot == FieldSheet_Clean[i, "SubPlot_FS"] &
                                                          SpecCode == FieldSheet_Clean[i,"SpecCode_FS"])
        if(nrow(ParacouDB_unique_corrInd == 1)){ # only if a suitable match is found - if required only here because the other correction codes already depend on that                                                    all other information has been found in the database


        # store wrongly entered idTree and overwrite with correct one
        FieldSheet_Clean[i, "idTreeWrong"] <- FieldSheet_Clean[i, "idTree"] # store information on Wrong idTree
        FieldSheet_Clean[i, "idTree"] <- ParacouDB_unique_corrInd$idTree # overwrite idTree with the correct one
        FieldSheet_Clean[i, "Code_idTreeCorr"] <- 1 # add correction code
    
        } 
   }
                                                                                                


    ### COREECT TREEFIELDNUMBER
    else if(!is.na(FieldSheet_Clean[i, "TreeFieldNum_missmatch"]) && FieldSheet_Clean[i, "TreeFieldNum_missmatch"] != 0){
     
          # search for correct one in database 
          ParacouDB_unique_corrInd <- ParacouDB_unique %>% filter(idTree == FieldSheet_Clean[i, "idTree"] & 
                                                          Plot == FieldSheet_Clean[i, "Plot_FS"] &
                                                          SubPlot == FieldSheet_Clean[i, "SubPlot_FS"] &
                                                          SpecCode == FieldSheet_Clean[i, "SpecCode_FS"])
     
          # store wrongly entered TreeFieldNum and overwrite with correct one
          FieldSheet_Clean[i, "TreeFieldNumWrong"] <- FieldSheet_Clean[i, "TreeFieldNum_FS"]
          FieldSheet_Clean[i, "TreeFieldNum_FS"] <- ParacouDB_unique_corrInd$TreeFieldNum
          FieldSheet_Clean[i, "Code_TreeFieldNumCorr"] <- 1 # add correction code
   }

    ### CORRECT PLOT
    else if(!is.na(FieldSheet_Clean[i, "Plot_missmatch"]) && FieldSheet_Clean[i, "Plot_missmatch"] != 0){
      
          # search for correct one in database  
          ParacouDB_unique_corrInd <- ParacouDB_unique %>% filter(idTree == FieldSheet_Clean[i, "idTree"] &
                                                          TreeFieldNum == FieldSheet_Clean[i, "TreeFieldNum_FS"] &
                                                          SubPlot == FieldSheet_Clean[i, "SubPlot_FS"] &
                                                          SpecCode == FieldSheet_Clean[i, "SpecCode_FS"])
    
          # store wrongly entered Plot and overwrite with correct one
          FieldSheet_Clean[i, "PlotWrong"] <- FieldSheet_Clean[i, "Plot_FS"]
          FieldSheet_Clean[i, "Plot_FS"] <- ParacouDB_unique_corrInd$Plot
          FieldSheet_Clean[i, "Code_PlotCorr"] <- 1 # add correction code
     }
  
    ### CORRECT SUBPLOT
    else if(!is.na(FieldSheet_Clean[i, "SubPlot_missmatch"]) && FieldSheet_Clean[i, "SubPlot_missmatch"] != 0){
     
          # search for correct one in database  
          ParacouDB_unique_corrInd <- ParacouDB_unique %>% filter(idTree == FieldSheet_Clean[i, "idTree"] &
                                                          TreeFieldNum == FieldSheet_Clean[i, "TreeFieldNum_FS"] &
                                                          Plot == FieldSheet_Clean[i, "Plot_FS"] &
                                                          SpecCode == FieldSheet_Clean[i, "SpecCode_FS"])

          # store wrongly entered SubPlot and overwrite with correct one
          FieldSheet_Clean[i, "SubPlotWrong"] <- FieldSheet_Clean[i, "SubPlot_FS"]
          FieldSheet_Clean[i, "SubPlot_FS"] <- ParacouDB_unique_corrInd$SubPlot
          FieldSheet_Clean[i, "Code_SubPlotCorr"] <- 1 # add correction code
    }

    ### CORRECT SPECCODE        
    else if(!is.na(FieldSheet_Clean[i, "SpecCode_missmatch"]) && FieldSheet_Clean[i, "SpecCode_missmatch"] != 0){

          # search for correct one in database            
          ParacouDB_unique_corrInd <- ParacouDB_unique %>% filter(idTree == FieldSheet_Clean[i, "idTree"] &
                                                          TreeFieldNum == FieldSheet_Clean[i, "TreeFieldNum_FS"] &
                                                          Plot == FieldSheet_Clean[i, "Plot_FS"] &
                                                          SubPlot == FieldSheet_Clean[i, "SubPlot_FS"])

          # store wrongly entered SpecCode and overwrite with correct one
          FieldSheet_Clean[i, "SpecCodeWrong"] <- FieldSheet_Clean[i, "SpecCode_FS"]
          FieldSheet_Clean[i, "SpecCode_FS"] <- ParacouDB_unique_corrInd$SpecCode
          FieldSheet_Clean[i, "Code_SpecCodeCorr"] <- 1 # add correction code
      }
}



###OUTPUT
#CLEAN DATAFRAME && 
ManualCorrection <- FieldSheet_Clean %>% 
  select(rowname, Plot_FS, 
         SubPlot_FS, 
         idTree, 
         TreeFieldNum_FS, 
         SpecCode_FS, 
         RWCnr_original, 
         Plot_DB, 
         SubPlot_DB, 
         TreeFieldNum_DB, 
         SpecCode_DB, 
         Manualcheck_missmatch) %>% 
  filter(Manualcheck_missmatch == 1) 

ManualCorrection
``` 

2) rowname 227 - idTree and Fieldnumber wrong

```{r}
ParacouDB_unique %>% filter(Plot == 14 , SubPlot == 4, SpecCode == "Dic.gui") # check with field sheet: its FieldNr 11 instead of 13
```

```{r}
ManualCorrection$idTree_Corr[ManualCorrection$rowname==106] <- 144254 # idTree from Database
ManualCorrection$TreeFieldNum_Corr[ManualCorrection$rowname==106] <- 11 # TreeFieldNum from Database
```

What about the empty ones?
```{r}
FieldSheet_Clean %>% filter(RWCnr_original %in% c("25","58","59")) # empty - so ok

```


**Here the rows that what have been corrected manually**
```{r Overview Manual corrections}
ManualCorrection 
```

Do another test if this now matches the database or if information was again wrongly entered
... if not join them together

**Join manual correction with the FieldSheet:**
still missing add manual correction code
```{r Join manual corrections and Fieldsheet}
FieldSheet_Clean <- left_join(FieldSheet_Clean, ManualCorrection)

if(!is.null(FieldSheet_Clean$Manualcheck_missmatch)) {

    for (i in 1:nrow(FieldSheet_Clean)) {
  
        if(FieldSheet_Clean[i, "Manualcheck_missmatch"] == 1) {

            ### CORRECT IDTREE if it was identified as a clear idTree mismatch
            if(!is.null(FieldSheet_Clean$idTree_Corr) && 
            !is.na(FieldSheet_Clean[i, "idTree_Corr"]) && 
             FieldSheet_Clean[i, "idTree_Corr"] != 0) {

                # store wrongly entered idTree and overwrite with correct one
                FieldSheet_Clean[i, "idTreeWrong"] <- FieldSheet_Clean[i, "idTree"] # store information on Wrong idTree
                FieldSheet_Clean[i, "idTree"] <- FieldSheet_Clean[i, "idTree_Corr"] # overwrite idTree with the correct one which was manually entered
            } 
  
            ### CORRECT TREEFIELDNUMBER
            if(!is.null(FieldSheet_Clean$TreeFieldNum_Corr) && 
               !is.na(FieldSheet_Clean[i, "TreeFieldNum_Corr"]) &&
               FieldSheet_Clean[i, "TreeFieldNum_Corr"] != 0){
     
 
                # store wrongly entered TreeFieldNum and overwrite with correct one
                FieldSheet_Clean[i, "TreeFieldNumWrong"] <- FieldSheet_Clean[i, "TreeFieldNum_FS"]
                FieldSheet_Clean[i, "TreeFieldNum_FS"] <- FieldSheet_Clean[i, "TreeFieldNum_Corr"]
            }

            ### CORRECT PLOT
            if(!is.null(FieldSheet_Clean$Plot_Corr) && 
               !is.na(FieldSheet_Clean[i, "Plot_Corr"]) &&
               FieldSheet_Clean[i, "Plot_Corr"] != 0){
      
                # store wrongly entered Plot and overwrite with correct one
                FieldSheet_Clean[i, "PlotWrong"] <- FieldSheet_Clean[i, "Plot_FS"]
                FieldSheet_Clean[i, "Plot_FS"] <- FieldSheet_Clean[i, "Plot_Corr"]
             }
  
            ### CORRECT SUBPLOT
            if(!is.null(FieldSheet_Clean$SubPlot_Corr) && 
               !is.na(FieldSheet_Clean[i, "SubPlot_Corr"]) &&
               FieldSheet_Clean[i, "SubPlot_Corr"] != 0){
     
                # store wrongly entered SubPlot and overwrite with correct one
                FieldSheet_Clean[i, "SubPlotWrong"] <- FieldSheet_Clean[i, "SubPlot_FS"]
                FieldSheet_Clean[i, "SubPlot_FS"] <- FieldSheet_Clean[i, "SubPlot_Corr"]  
             }

            ### CORRECT SPECCODE        
            if(!is.null(FieldSheet_Clean$SpecCode_Correction) && 
               !is.na(FieldSheet_Clean[i, "SpecCode_Correction"]) &&
               FieldSheet_Clean[i, "SpecCode_Correction"] != 0){

                # store wrongly entered SpecCode and overwrite with correct one
                FieldSheet_Clean[i, "SpecCodeWrong"] <- FieldSheet_Clean[i, "SpecCode_FS"]
                FieldSheet_Clean[i, "SpecCode_FS"] <- FieldSheet_Clean[i, "SpecCode_Correction"]      
            } 
        }
    }
}

```



 Little checks
```{r}
#FieldSheet_Clean %>% filter(Code_PlotCorr==1) # yes does not exist because we dont have that case
#FieldSheet_Clean %>% filter(Code_SpecCodeCorr==1) # yes does not exist because we dont have that case 
FieldSheet_Clean %>% filter(Code_idTreeCorr==1) %>% select(idTree, idTreeWrong, Code_idTreeCorr) # yes all correct
FieldSheet_Clean %>% filter(!is.na(idTreeWrong)) %>% select(idTree, idTreeWrong, Code_idTreeCorr)
FieldSheet_Clean %>% filter(Code_idTreeCorr==0 & !is.na(idTreeWrong)) #seems good 

FieldSheet_Clean %>% filter(Code_SubPlotCorr==1) %>% select(idTree, SubPlot_FS, SubPlot_DB, SubPlotWrong, SubPlot_missmatch)
FieldSheet_Clean %>% filter(!is.na(SubPlotWrong==1))%>% select(idTree, SubPlot_FS, SubPlot_DB, SubPlotWrong, SubPlot_missmatch) # yes all correct because one was an NA

```

Recheck if now all the idTrees can be found in the Database. 

```{r recheck for mismatching idTree after correction}
# get a dataframe with all the individuals where idTree does not correspond to any within the database
iddoesNotExist_afterCleaning <- FieldSheet_Clean %>%  
  mutate(idexist = ifelse(FieldSheet_Clean$idTree %in% ParacouDB_unique$idTree == T, 1,0)) %>% # creates a new Column with a 0 (not found in database) and 1 (exists in database) code 
  filter(idexist == 0) # filter only the 0s to get a dataframe only containing incorrect ids

nrow(iddoesNotExist_afterCleaning)
```

Ok looks fine - its now just the 3 empty rows now
```{r}
iddoesNotExist_afterCleaning
```
Dublicates? - NO
```{r}
FieldSheet_Clean %>% group_by(idTree) %>% summarize(nSamples = n_distinct(idTree)) %>% filter(nSamples >1)
```


# Homogenise Tree Information
Position Crown:
 Branch_Position_crown
  <chr>                
1 middle               
2 low                  
3 top                  
4 NA       


```{r}
FieldSheet_Clean %>% ungroup() %>% distinct(Position_Crown)
```

Homogenise information
```{r}
FieldSheet_Clean <- replaceStuff(list_wrong_strings = c("Sup"), 
             replacement = "top", 
             df = FieldSheet_Clean, 
             col_name = "Position_Crown")

FieldSheet_Clean <- replaceStuff(list_wrong_strings = c("Mid"), 
             replacement = "middle", 
             df = FieldSheet_Clean, 
             col_name = "Position_Crown")

FieldSheet_Clean <- replaceStuff(list_wrong_strings = c("Inf"), 
             replacement = "low", 
             df = FieldSheet_Clean, 
             col_name = "Position_Crown")
```

# Add taxonomic information:

TaxonInfo <- ParacouDB_unique %>% ungroup() %>% select(idTree, Genus, Species, spName)

FieldSheet_Clean_BotaCorr <- left_join(FieldSheet_Clean_BotaCorr, TaxonInfo, by = "idTree")

FamilyInfo <- ParacouDB %>% group_by(Genus, Family) %>% distinct(Genus) %>% rename(Genus_CorrBota = Genus, Family_CorrBota = Family)
FieldSheet_Clean_BotaCorr <- left_join(FieldSheet_Clean_BotaCorr, FamilyInfo)

```{r}

TaxonInfo <- ParacouDB %>% ungroup() %>% select(idTree, Genus_CorrBota = Genus, Species_CorrBota=Species, spName_CorrBota=spName, Family_CorrBota=Family) %>% distinct()

FieldSheet_Clean_BotaCorr <- left_join(FieldSheet_Clean, TaxonInfo, by = "idTree")

```

# Select and Rename

```{r}
names(FieldSheet_Clean_BotaCorr)
```


```{r}
FieldSheet_Clean_BotaCorr_OUT <- FieldSheet_Clean_BotaCorr %>% 
  
  select(RWCnr_original, # identifier sample
       #RWC_additional1, 
       
       idTree,         #information on Tree
       #Resampled,
       Plot = Plot_FS, 
       SubPlot = SubPlot_FS, 
       TreeFieldNum = TreeFieldNum_FS,
       SpecCode_CorrBota = SpecCode_FS,
       
       spName_CorrBota, # taxonomic information
       Genus_CorrBota,
       Species_CorrBota,
       Family_CorrBota, 
       
       Tree_Dawkins = DawkinIndiv,  # detailed information on tree
       Tree_Height = HeightTree, 
       
       Branch_Dawkins = DawkinBranch, # detailed information on branch
       Branch_Height = HeightBranch, 
       #Branch_Light_exposition = LeafLight_exposition, 
       Branch_Position_crown = Position_Crown,
       #LeafLight_exposition,
       
       Habitat_preference = pref.Habitat, # additional Info on Species and tree
       Habitat_real = Habitat,
       
       #DateField, # Info on Sampling Day
       #TimeArrival, 
       #Weather_Arrival = WXArrival,
       #Name_Team = NamesTeam, 
       #Name_Recorder = Recorder,
       #Time_Sampling = TimeCollection, 
       #Weather_Sampling = WXCollecion, 
       #NrDiscs, # disc information
       #DiscDiameter, 
       #NrLeaves4Discs, 
       #RWCSecVeins2Dense,
       
       #SampledTraits, # additional information
       #RWCbigBag_used,
       #Ficelle, 
       #Nrleaves2Lab,
       
       #Comment_RWC = commentRWCnr, # Comments
       #Comment_Individual = Comment_individual.collection.exposure,
       
       #no_missmatch, # Information on Mismatches with Database and Correction
       Code_ManualCorr = Manualcheck_missmatch, 
       Code_idTreeCorr,
       #Code_TreeFieldNumCorr,
       Code_SubPlotCorr,
       
       Wrong_idTree = idTreeWrong, # wrongly entered information
       Wrong_TreeFeldNum = TreeFieldNumWrong,
       Wrong_SubPlot = SubPlotWrong,
       SpecCode_DB = SpecCode_FS,
       
       #Code_ErrorBota, # Botanical correction
       #Code_idBotaCheck = Code_id_corr, 
       #Wrong_idBota = Wrong_id,
       #Comment_Botanist
       
       # traits
       Trait_FW_E.g = Fresh_Weight.g.,
       Trait_SW_E.g = Saturated_Weight.g.,
       Trait_Delta_FW_SW_E.g. = Delta_Weight_SW.FW.g.,
       Trait_Delta_en_real = delta_en_._real,
       Trait_Delta_en_clean = delta_en_._clean, 
       Trait_DW_E.g. = Dry_Weight.g.,
       Trait_RWC = RWC, 
       Trait_LSWC = LSWC,
       Trait_Posmo = P_osmo,
       Trait_Ptlp = P_tlp,
       Trait_Pmidday.mean = mean_Pmidday, 
       Trait_Fv.Fm = Fv.Fm, 
       Trait_LA.cm2 = LA..cm.2.,
       Trait_gmin.molm2s1 = gmin..mmol.m.2.s.1.,
       Trait_1st_Order_VD.mm.mm2 = X1st_Order_Vein_Density..mm.mm.2.,
       Trait_2nd_Order_VD.mm.mm2 = X2nd_Order_Vein_Density..mm.mm.2.,
       Trait_3rd_Order_VD.mm.mm2 = X3rd_Order_Vein_Density..mm.mm.2.,
       Trait_Major_VD = Major_Vein_Density..mm.mm.2.   
       )
```


```{r}

#FieldSheet_Clean<- FieldSheet_Clean %>% select(-c("Plot_DB", "SubPlot_DB", "TreeFieldNum_DB", "SpecCode_DB"))
#FieldSheet_Clean<- FieldSheet_Clean %>% rename(Plot = Plot_FS, SubPlot = SubPlot_FS, TreeFieldNum = TreeFieldNum_FS, SpecCode = SpecCode_FS)
FieldSheet_Clean_BotaCorr_OUT <- FieldSheet_Clean_BotaCorr_OUT %>% mutate(RWCnr_original = paste0("M", RWCnr_original))
FieldSheet_Clean_BotaCorr_OUT <- FieldSheet_Clean_BotaCorr_OUT %>% mutate(Name_project = "Metradica")

write.csv(FieldSheet_Clean_BotaCorr_OUT, "./../output/FieldSheet_Clean_OUT_Metradica.csv", row.names = FALSE)
```

 